### 2014-03-15 Paper/paper.tex
First commit for github

\documentclass{article}

\usepackage{amsmath,amsfonts, amssymb,wasysym, latexsym, hyperref, mathdots, enumerate, pstricks,setspace,epsfig,amsthm}
\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
\usetikzlibrary{backgrounds}

\usepackage{todonotes}

\usepackage{graphicx,times}
\usepackage[toc,page]{appendix}
\usepackage{fullpage}
\usepackage[parfill]{parskip}
\usepackage{subfig}
\usepackage{caption}
\usepackage[figuresleft]{rotating}
\usepackage{float}
\usepackage{multibib}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{color}

% New commands------------------------
\newcommand{\NH}{\text{NH}}
\newcommand{\RG}{\text{RG}}
\newcommand{\todoVK}[1]{\todo[color=blue!20]{#1}}

\title{Measuring the Price of Anarchy in Critical Care Unit Interactions}
\author{Vincent Knight
    \and
        Izabela Komenda*
    \and
        Jeff Griffiths}

\begin{document}
\maketitle

\begin{abstract}
Hospital throughput is often studied and optimised in isolation, ignoring the interactions between hospitals.
In this paper Critical Care Unit (CCU) interaction is placed within a game theoretic framework.
The methodology involves the use of a normal form game underpinned by a two dimensional continuous Markov chain.
A theoretical result is given that ensures the existence of a Nash equilibrium.

The effect of target policies is investigated justifying the use of these to align the interests of individual hospitals and social welfare.
In particular, we identify the lowest value of a utilisation target that aligns these.
\end{abstract}

\section{Introduction}

A Critical Care Unit (CCU), also sometimes referred to as an Intensive Therapy Unit or Intensive Therapy Department, is a special ward that is found in most acute hospitals.
It provides intensive care (treatment and monitoring) for people who are critically ill or are in an unstable condition.
CCUs face major challenges.
The first challenge that CCUs have to deal with is shortage of beds.  On average, 8\% of patients are refused admission to a CCU because the Unit is full \cite{Report}. The CCU occupancy rates for some hospitals are reportedly very high \cite{Mitchell1995,Smith1995} and a shortage of beds has been identified throughout the UK.

Patients in CCUs need constant medical support to keep their body functioning.
Moreover, CCU beds are very expensive and a limited resource; therefore efficient CCU bed management is crucial.
Many previous researchers have developed queueing models to help manage bed capacities in hospitals \cite{Cooper1974,Dumas1984,Gallivan2011,Gorunescu2002a,Griffiths2012,Harper2002a}.
Also, a vast amount of literature has been devoted to simulation of CCUs;  \cite{Cahill1999a,Costa2003,Griffiths2004a,Kim1999,Litvak2008,Shahani2008}.

This paper describes part of a project undertaken with managers from the Aneurin Bevan University Health Board (ABUHB), which is an NHS Wales organization in South Wales, that serves 21\% of the total population of Wales \cite{Board}.
Critical care is delivered on two sites, at the Nevill Hall hospital in Abergavenny and at the Royal Gwent hospital in Newport.
For the remainder of this paper, the Nevill Hall hospital will be referred to as NH and the Royal Gwent hospital as RG.

The main proposition of the work requested by the ABHB was to develop a mathematical model of bed occupancies at the CCUs at RG and NH.
After an initial analysis of the data, behavioural aspects became apparent; for example, delaying patients discharge if there was no pressure on CCU beds, or admitting fewer patients if bed occupancy levels were high.
As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy \cite{Komenda2013}.
This state dependent model was applied to both NH and RG separately.
It is however obvious that the actions of one CCU impact on the other CCU, as diversion of patients from one CCU to the other sometimes occurs.
A pictorial representation of the situation is given in Figure \ref{diagramofdiversion}.

\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}
\node (A) at (0,0) [draw] {RG};
\node (B) at (2,0) [draw] {NH};
\draw [->] (-1,0) -- (A);
\draw [->] (3,0) -- (B);
\draw [->] (-1,0) -- ($(A)+(-.5,0)$) -- ($(A)+(-.5,.5)$) -- ($(A)+(.5,.5)$) -- ($(A)+(.5,.1)$) -- ($(B)+(-.4,.1)$);
\draw [->] (3,0) -- ($(B)+(.5,0)$) -- ($(B)+(.5,-.5)$) -- ($(B)+(-.5,-.5)$) -- ($(B)+(-.5,-.1)$) -- ($(A)+(.4,-.1)$);
\draw [->] (3,0) -- (B);
\node at ($(A) + (0,.8)$) {Divert?};
\node at ($(B) + (0,-.8)$) {Divert?};
\end{tikzpicture}
\caption{Diagrammatic representation of CCU interaction through patient diversion.}\label{diagramofdiversion}
\end{center}
\end{figure}

Game theory is the mathematical study of interactive decision making between rational decision makers \cite{Maschler2013}.
A game is a description of strategic interactions that includes the constraints on the actions that the players can take and on the players' interests.

Most research where game theory is applied in healthcare has mainly concentrated on Emergency Departments (EDs) and how to deal with diversions of patients and ambulances.
In \cite{Hagtvedt2009} cooperative strategies for hospitals are considered, in order to reduce occurrences when ambulances are turned away due to the ED being full.
In \cite{Deo2011} a queueing network model of two EDs is proposed to study the network effect of ambulance diversion.
Each ED aims to minimise the expected waiting time of its patients (walk-ins and ambulances) and chooses its diversion threshold based on the number of patients at its location. Decentralised decision making in the network is modelled as a non-cooperative game.

Some other work that has not concentrated on EDs, but has been applied to healthcare includes: \cite{Knight2013}, where results concerning the congestion related implications of decisions made by patients when choosing between healthcare facilities were presented. In \cite{Howard2002} a model of the accept/reject decision for transplant organs is developed.

In the wider intersection of game theory and queueing theory (where this work lies) papers that consider price and/or capacity include: \cite{Allon2007, Cachon2002,  Cachon2007, Kalai1992, Levhari1978}. In these models, the choice of price/or capacity determines the arrival rate for each firm; this is similar to the approach taken in this paper.

The work presented in this paper contributes to the growing body of literature by applying state dependent queueing models in a game theoretical context to CCU interaction.
In particular this consideration allows for the investigation of targets imposed by central control \cite{Bevan2006}.
The findings of this work justify and identify a choice of targets that align the interests of the individual hospitals with social welfare.

The data used for the work presented in this paper was provided by the Intensive Care National Audit and Research Centre (ICNARC) and refers to patients admitted to CCUs in NH and RG, and covers a period of three years, from the 1$^{\text{st}}$ January 2009 till the 31$^{\text{st}}$ December 2011.
The data set contains information about a patient's source of admission, date and time of admission, date and time of discharge, CCU outcome and delay to discharge.
The parameters obtained from the data used in this work are shown in Table \ref{parameter_values_model_1}.

\begin{table}[!htbp]
\begin{center}
\begin{tabular}{|c|l|c|}
\hline
\textbf{Parameter}&\textbf{Parameter description}&\textbf{Parameter value}\\
\hline
$c_{\NH}$&the bed capacity at NH&8\\
\hline
$c_{\RG}$&the bed capacity at RG&16\\
\hline
$\lambda_{\NH}$&the arrival rate at NH (per day)&1.50 \\
\hline
$\lambda_{\RG}$&the arrival rate at RG (per day)&2.24\\
\hline
$\mu_{\NH}$&the service rate at NH (days)&0.262\\
\hline
$\mu_{\RG}$&the service rate at RG (days)&0.198\\
\hline
$t$& bed utilisation target & 0.8\\
\hline
\end{tabular}
\end{center}
\caption{Parameter values used in the model}\label{parameter_values_model_1}
\end{table}

The paper is organised as follows:
\begin{itemize}
    \item Section \ref{queueingandgamemodels} presents the general methodology as well as a theoretical existence condition for Nash equilibrium;
    \item Section \ref{results} presents the findings from two models;
    \item Conclusions and further ideas for progression are given in Section \ref{conclusions}.
\end{itemize}

\section{Queueing and Game Theoretic Models} \label{queueingandgamemodels}

Throughout this paper it is assumed that both CCUs (NH and RG) act selfishly and rationally.
The strategies of each CCU are capacity thresholds at which they declare being in ``diversion''. When in ``diversion'' the arrival rates of patients are modified.
Given the proximity of the two CCUs, one CCU could for example divert their patients to the other.
Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_h^{(r)}$ for $h\in\{\NH, \RG\}$ and $r\in\{a, b, c, d\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $a,b,c \text{ and } d$ are regions with boundaries defined by the capacity thresholds.
It is also assumed that diverted patients will be treated under the length of stay profile of the CCU they are admitted to.
The capacity thresholds are denoted as $K_{h}\in\mathbb{Z}$ for $h\in\{\NH,\RG\}$. Note that $0\leq K_h\leq c_h$.

\begin{figure}[!htbp]
\begin{center}
    \begin{tikzpicture}
        \draw  (0,0) rectangle (4,3);
        \draw [dashed, red, thick] (0,1) -- (4,1);
        \draw [dashed, red, thick] (3,0) -- (3,3);
        \node at (-.5,1) {$K_{\NH}$};
        \node at (3,3.25) {$K_{\RG}$};
        \node at (1.5,2) {$\lambda_{h}^{(a)}$};
        \node at (3.5,2) {$\lambda_{h}^{(b)}$};
        \node at (1.5,.5) {$\lambda_{h}^{(c)}$};
        \node at (3.5,.5) {$\lambda_{h}^{(d)}$};
    \end{tikzpicture}
\caption{General arrival rates for each CCU at each region, where $h\in\{\NH, \RG\}$} \label{arrivalrateregions}
\end{center}
\end{figure}

To formally investigate the impact of decentralised decision making, the interaction between two CCUs is placed within a non-cooperative game framework.
The interaction will be modelled through a two dimensional continuous Markov chain that will now be described.

\subsection{Queueing Model}

The state space for the Markov chain is given by:

\begin{equation}
S=S(c_{\NH}, c_{\RG})= \{(u,v)\in \mathbb{Z}^2\ |\ 0\leq u\leq c_{\NH},\ 0\leq v\leq c_{\RG}\} \label{statespace}
\end{equation}

For given $K_{\NH}, K_{\RG}$ and using the notation of Figure \ref{arrivalrateregions} the generic Markov chain used to model the interactive queueing system in this paper is shown in Figure \ref{mc}.

\begin{figure}[!htbp]
\begin{center}
    \begin{tikzpicture}[scale=.7, every node/.style={scale=0.7}]
        % -----------------------------------------------
        % Boundaries ------------------------------------
        % -----------------------------------------------
        \draw [dashed, line width=1mm, red, opacity=.3] (12,2) -- (12,-20);
        \draw [dashed, line width=1mm, red, opacity=.3] (-2,-12) -- (20,-12);
        %\tikzstyle{state}=[ellipse, draw, fill=blue!10, minimum width=2cm];
        %\tikzstyle{state}=[rectangle, draw, fill=blue!10, minimum width=2cm];
        \tikzstyle{state}=[minimum width=2cm, font=\boldmath];
        %\draw  (0,0) rectangle (4,3);
        %\draw [dashed, red, thick] (0,1) -- (4,1);
        %\draw [dashed, red, thick] (3,0) -- (3,3);
        % -----------------------------------------------
        % First row--------------------------------------
        % -----------------------------------------------
        \node (aa) [state] at (0,0) {$(0,0)$};
        \node (ab) [state] at ($(aa) + (3,0)$) {$(0,1)$};
        \node (ac) [state] at ($(ab) + (3,0)$) {$(0,2)$};
        \node (ellipsisa1) at ($(ac) + (3,0)$) {$\dots$};
        \node(ak) [state] at ($(ellipsisa1) + (3,0)$) {$(0,K_{\RG})$};
        \node (ellipsisa2) at ($(ak) + (3,0)$) {$\dots$};
        \node(az) [state] at ($(ellipsisa2) + (3,0)$) {$(0,c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (aa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ab);
        \draw (aa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ab);

        \draw (ab) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ac);
        \draw (ab) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ac);

        \draw (ac) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisa1);
        \draw (ac) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisa1);

        \draw (ellipsisa1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ak);
        \draw (ellipsisa1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ak);

        \draw (ak) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisa2);
        \draw (ak) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisa2);

        \draw (ellipsisa2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (az);
        \draw (ellipsisa2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (az);
        % -----------------------------------------------
        % Second row--------------------------------------
        % -----------------------------------------------
        \node (ba) [state] at (0,-3) {$(1,0)$};
        \node (bb) [state] at ($(ba) + (3,0)$) {$(1,1)$};
        \node (bc) [state] at ($(bb) + (3,0)$) {$(1,2)$};
        \node (ellipsisb1) at ($(bc) + (3,0)$) {$\dots$};
        \node(bk) [state] at ($(ellipsisb1) + (3,0)$) {$(1,K_{\RG})$};
        \node (ellipsisb2) at ($(bk) + (3,0)$) {$\dots$};
        \node(bz) [state] at ($(ellipsisb2) + (3,0)$) {$(1,c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (ba) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bb);
        \draw (ba) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bb);

        \draw (bb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bc);
        \draw (bb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bc);

        \draw (bc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisb1);
        \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisb1);

        \draw (ellipsisb1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bk);
        \draw (ellipsisb1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bk);

        \draw (bk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisb2);
        \draw (bk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisb2);

        \draw (ellipsisb2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (bz);
        \draw (ellipsisb2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bz);
        % With previous row:
        \draw (aa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ba);
        \draw (aa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ba);

        \draw (ab) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (bb);
        \draw (ab) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bb);

        \draw (ac) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (bc);
        \draw (ac) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bc);

        \draw (ellipsisa1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisb1);
        \draw (ellipsisa1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisb1);

        \draw (ak) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (bk);
        \draw (ak) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bk);

        \draw (ellipsisa2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisb2);
        \draw (ellipsisa2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisb2);

        \draw (az) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (bz);
        \draw (az) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bz);
        % -----------------------------------------------
        % Third row--------------------------------------
        % -----------------------------------------------
        \node (ca) [state] at (0,-6) {$(2,0)$};
        \node (cb) [state] at ($(ca) + (3,0)$) {$(2,1)$};
        \node (cc) [state] at ($(cb) + (3,0)$) {$(2,2)$};
        \node (ellipsisc1) at ($(cc) + (3,0)$) {$\dots$};
        \node(ck) [state] at ($(ellipsisc1) + (3,0)$) {$(2,K_{\RG})$};
        \node (ellipsisc2) at ($(ck) + (3,0)$) {$\dots$};
        \node(cz) [state] at ($(ellipsisc2) + (3,0)$) {$(2,c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (ca) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (cb);
        \draw (ca) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cb);

        \draw (cb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (cc);
        \draw (cb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cc);

        \draw (cc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisc1);
        \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisc1);

        \draw (ellipsisc1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ck);
        \draw (ellipsisc1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ck);

        \draw (ck) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisc2);
        \draw (ck) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisc2);

        \draw (ellipsisc2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (cz);
        \draw (ellipsisc2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cz);
        % With previous row:
        \draw (ba) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ca);
        \draw (ba) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ca);

        \draw (bb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (cb);
        \draw (bb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cb);

        \draw (bc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (cc);
        \draw (bc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cc);

        \draw (ellipsisb1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisc1);
        \draw (ellipsisb1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisc1);

        \draw (bk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ck);
        \draw (bk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ck);

        \draw (ellipsisb2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisc2);
        \draw (ellipsisb2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisc2);

        \draw (bz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (cz);
        \draw (bz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cz);
        % -----------------------------------------------
        % Fourth row--------------------------------------
        % -----------------------------------------------
        \node (da) at (0,-9) {$\vdots$};
        \node (db) at ($(da) + (3,0)$) {$\vdots$};
        \node (dc) at ($(db) + (3,0)$) {$\vdots$};
        \node (ellipsisd1) at ($(dc) + (3,0)$) {$\dots$};
        \node(dk) at ($(ellipsisd1) + (3,0)$) {$\vdots$};
        \node (ellipsisd2) at ($(dk) + (3,0)$) {$\dots$};
        \node(dz) at ($(ellipsisd2) + (3,0)$) {$\vdots$};
        % Transitions -----------------------------------
        % On Row:
        \draw (da) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (db);
        \draw (da) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (db);

        \draw (db) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (dc);
        \draw (db) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (dc);

        \draw (dc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisd1);
        \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisd1);

        \draw (ellipsisd1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (dk);
        \draw (ellipsisd1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (dk);

        \draw (dk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisd2);
        \draw (dk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisd2);

        \draw (ellipsisd2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (dz);
        \draw (ellipsisd2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (dz);
        % With previous row:
        \draw (ca) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (da);
        \draw (ca) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (da);

        \draw (cb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (db);
        \draw (cb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (db);

        \draw (cc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (dc);
        \draw (cc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dc);

        \draw (ellipsisc1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisd1);
        \draw (ellipsisc1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisd1);

        \draw (ck) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (dk);
        \draw (ck) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dk);

        \draw (ellipsisc2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisd2);
        \draw (ellipsisc2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisd2);

        \draw (cz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (dz);
        \draw (cz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dz);
        % -----------------------------------------------
        % Fifth row--------------------------------------
        % -----------------------------------------------
        \node (ea) [state] at (0,-12) {$(K_{\NH},0)$};
        \node (eb) [state] at ($(ea) + (3,0)$) {$(K_{\NH},1)$};
        \node (ec) [state] at ($(eb) + (3,0)$) {$(K_{\NH},2)$};
        \node (ellipsise1) at ($(ec) + (3,0)$) {$\dots$};
        \node(ek) [state] at ($(ellipsise1) + (3,0)$) {$(K_{\NH},K_{\RG})$};
        \node (ellipsise2) at ($(ek) + (3,0)$) {$\dots$};
        \node(ez) [state] at ($(ellipsise2) + (3,0)$) {$(K_{\NH},c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (ea) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (eb);
        \draw (ea) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (eb);

        \draw (eb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ec);
        \draw (eb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ec);

        \draw (ec) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ellipsise1);
        \draw (ec) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsise1);

        \draw (ellipsise1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ek);
        \draw (ellipsise1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ek);

        \draw (ek) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsise2);
        \draw (ek) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsise2);

        \draw (ellipsise2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ez);
        \draw (ellipsise2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ez);
        % With previous row:
        \draw (da) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ea);
        \draw (da) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ea);

        \draw (db) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (eb);
        \draw (db) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (eb);

        \draw (dc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ec);
        \draw (dc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ec);

        \draw (ellipsisd1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsise1);
        \draw (ellipsisd1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsise1);

        \draw (dk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ek);
        \draw (dk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ek);

        \draw (ellipsisd2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsise2);
        \draw (ellipsisd2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsise2);

        \draw (dz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ez);
        \draw (dz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ez);
        % Sixth row--------------------------------------
        \node (fa) at (0,-15) {$\vdots$};
        \node (fb) at ($(fa) + (3,0)$) {$\vdots$};
        \node (fc) at ($(fb) + (3,0)$) {$\vdots$};
        \node (ellipsisf1) at ($(fc) + (3,0)$) {$\dots$};
        \node(fk) at ($(ellipsisf1) + (3,0)$) {$\vdots$};
        \node (ellipsisf2) at ($(fk) + (3,0)$) {$\dots$};
        \node(fz) at ($(ellipsisf2) + (3,0)$) {$\vdots$};
        % Transitions -----------------------------------
        % On Row:
        \draw (fa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fb);
        \draw (fa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fb);

        \draw (fb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fc);
        \draw (fb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fc);

        \draw (fc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ellipsisf1);
        \draw (fc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisf1);

        \draw (ellipsisf1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fk);
        \draw (ellipsisf1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fk);

        \draw (fk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisf2);
        \draw (fk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisf2);

        \draw (ellipsisf2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (fz);
        \draw (ellipsisf2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fz);
        % With previous row:
        \draw (ea) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fa);
        \draw (ea) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fa);

        \draw (eb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fb);
        \draw (eb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fb);

        \draw (ec) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fc);
        \draw (ec) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fc);

        \draw (ellipsise1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (ellipsisf1);
        \draw (ellipsise1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisf1);

        \draw (ek) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (fk);
        \draw (ek) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fk);

        \draw (ellipsise2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (ellipsisf2);
        \draw (ellipsise2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisf2);

        \draw (ez) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (fz);
        \draw (ez) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fz);
        % Final row--------------------------------------
        \node (za) [state] at (0,-18) {$(c_{\NH},0)$};
        \node (zb) [state] at ($(za) + (3,0)$) {$(c_{\NH},1)$};
        \node (zc) [state] at ($(zb) + (3,0)$) {$(c_{\NH},2)$};
        \node (ellipsisz1) at ($(zc) + (3,0)$) {$\dots$};
        \node(zk) [state] at ($(ellipsisz1) + (3,0)$) {$(c_{\NH},K_{\RG})$};
        \node (ellipsisz2) at ($(zk) + (3,0)$) {$\dots$};
        \node(zz) [state] at ($(ellipsisz2) + (3,0)$) {$(c_{\NH},c_{\RG})$};
        % Transitions -----------------------------------
        % On Row:
        \draw (za) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zb);
        \draw (za) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zb);

        \draw (zb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zc);
        \draw (zb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zc);

        \draw (zc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisz1);
        \draw (zc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisz1);

        \draw (ellipsisz1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zk);
        \draw (ellipsisz1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zk);

        \draw (zk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisz2);
        \draw (zk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisz2);

        \draw (ellipsisz2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zz);
        \draw (ellipsisz2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zz);
        % With previous row:
        \draw (fa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (za);
        \draw (fa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (za);

        \draw (fb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (zb);
        \draw (fb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zb);

        \draw (fc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (zc);
        \draw (fc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zc);

        \draw (ellipsisf1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (ellipsisz1);
        \draw (ellipsisf1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisz1);

        \draw (fk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (zk);
        \draw (fk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zk);

        \draw (ellipsisf2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (ellipsisz2);
        \draw (ellipsisf2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisz2);

        \draw (fz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (zz);
        \draw (fz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zz);

    \end{tikzpicture}
\caption{Generic Markov chain underpinning the queueing model of this paper} \label{mc}
\end{center}
\end{figure}

In total there are $(c_{\NH}+1)\times(c_{\RG}+1)$ states and they are indexed lexicographically: $(0,0), (0,1), (0,2)$, etc. In general, state $(u,v)$ is the $s(u,v)th$ state where $s(u,v)=u(c_{\RG}+1)+(v+1)$.

The stochastic transition rate matrix $Q=Q(c_{NH},c_{RG})$ of the continuous-time Markov chain \cite{Stewart2009} has entries $q_{ij}$ which is the rate at which a transition from state $i$ to state $j$ occurs. The transition rates are given by:

\begin{equation}
q_{ij}=\begin{cases} u\mu_{\NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(1,0),\\
 v\mu_{\RG} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,1),\\
 \lambda_{NH}^{(a)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0)  \text{ and  } u_i < K_{\NH}  \text{ and  } v_i < K_{\RG},\\
 \lambda_{RG}^{(a)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1)  \text{ and  } u_i < K_{\NH}  \text{ and  } v_i < K_{\RG},\\
\lambda_{NH}^{(b)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i < K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
\lambda_{RG}^{(b)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i < K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
\lambda_{NH}^{(c)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i < K_{\RG},\\
\lambda_{RG}^{(c)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i < K_{\RG},\\
\lambda_{NH}^{(d)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
\lambda_{RG}^{(d)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
0 & \text{ otherwise}.
\end{cases}
\end{equation}

Utilities will be of interest when this queueing theoretical model will be inserted in the game theoretical model.
Throughput of patients is a natural choice of utility given that most hospitals are financially rewarded per served patient \cite{Pate2009}.
For each threshold pair $(K_{\NH},K_{\RG})$, the utilisation rate $U_h$ and throughput $T_h$ can easily be obtained for each CCU: $h\in\{\text{NH},\text{RG}\}$, using the following formulas:

$$U_{h}={{\sum_{n=0}^{c_h} nP^{(h)}(n)}\over{c_{h}}}$$
$$T_{h}=\mu_h \sum _{n=0}^{c_h} nP^{(h)}(n)$$

where $P^{(h)}=P^{(h)}(K_{\NH},K_{\RG})$ is the steady state probability distribution function (obtained from the corresponding transition matrix $Q=Q(K_{\NH},K_{\RG})$) for $h\in\{\text{NH},\text{RG}\}$.

For $c_{\NH}=8$, $c_{\RG}=16$, $\lambda_{\NH}=(\lambda_{\NH}^{(a)},\lambda_{\NH}^{(b)},\lambda_{\NH}^{(c)},\lambda_{\NH}^{(d)})=(1.5,3.74,0,0)$, $\lambda_{\RG}=(\lambda_{\RG}^{(a)},\lambda_{\RG}^{(b)},\lambda_{\RG}^{(c)},\lambda_{\RG}^{(d)})=(2.24,0,3.74,0)$ and $(K_{\NH},K_{\RG})=(6,12)$, the steady state probabilities for each CCU are given in Figure \ref{steady_state_probs}.

\begin{figure}[!htbp]
$$
\begin{array}{cc}
\includegraphics[width=.5\textwidth]{./Images/NH.pdf}&\includegraphics[width=.5\textwidth]{./Images/RG.pdf}\\
h=NH&h=RG
\end{array}
$$
\caption{Steady state probabilities for $h\in\{\NH,\RG\}$ with $(K_{\NH}, K_{\RG})=(6,12)$} \label{steady_state_probs}
\end{figure}

For the parameters of Figure \ref{steady_state_probs} the utilisation rates are: 59\% at NH and 62\% at RG and a throughput of 1.23 at NH and 1.98 at RG (patients per day).\\

For a different threshold pair of $(K_{\NH},K_{\RG})=(1,12)$ the steady state probabilities are given in Figure \ref{steady_state_probs_1_12}.
The utilisation rates are: 11\% at NH and 67\% at RG and throughput of 0.23 at NH and 2.13 at RG.
We see that the RG is now busier as a result of NH having a lower diversion threshold. A model of this interaction will be given in the next section.

\begin{figure}[!htbp]
$$
\begin{array}{cc}
\includegraphics[width=.5\textwidth]{./Images/NH_1_12.pdf}&\includegraphics[width=.5\textwidth]{./Images/RG_1_12.pdf}\\
h=\NH&h=\RG
\end{array}
$$
\caption{Steady state probabilities for $h\in\{\NH,\RG\}$ with $(K_{\NH}, K_{\RG})=(1,12)$} \label{steady_state_probs_1_12}
\end{figure}

\subsection{Game Theoretic Model}

Based on the discussion above, the game theoretic model is presented as a synchronous optimisation problem shown in Figure \ref{model1}.

\begin{figure}[!htbp]
\hspace{2cm}For all $h\in\{\text{NH}, \text{RG}\}$ minimise:
$$\left(U_{h}-t\right)^2$$
\hspace{2cm}Subject to:
\begin{align}
0\leq & K_h \leq c_{h}\nonumber\\
&K_h \in  \mathbb{Z}\nonumber
\end{align}
\caption{The optimisation problem underlying the game}\label{model1}
\end{figure}

This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close as possible to a certain target.
As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABHB, long term threshold policies are a realistic consideration.

The following result is a sufficient condition for the existence of equilibrium:\\

\textbf{Theorem.}

Let $f_{h}(k):[1,c_{\bar h}]\to[1,c_h]$ be the best response of player $h\in\{\NH, \RG\}$ to the diversion threshold of $\bar h\ne h$ ($\bar h\in\{\NH, \RG\}$).

If $f_{h}(k)$ is a non-decreasing function in $k$ then the game of Figure \ref{model1} has at least one Nash equilibrium.

\begin{proof}

The function $f_h$ is well defined as it maximises a continuous function over a finite discrete set (in case of multiple values that minimize $U_h$, it is assumed that $f_h$ returns the lowest such value).

As such if $f_h$ is non-decreasing then it is in fact a stepwise non-decreasing function.
If we consider $f_{\NH}$ and $f_{\RG}$ plotted on the same axis (so that the domain of $f_{\NH}$ is the $x$-axis and the domain of $f_{\RG}$ is the y-axis) it is obvious to see that the functions must intersect at some point as shown in Figure \ref{exampleforproof}.

\begin{figure}[!htbp]
$$\begin{array}{cc}
\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_NH.pdf}&
\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_RG.pdf}
\end{array}$$
\caption{Plots of $f_{\NH}(K_{\RG})$ and $f_{\RG}(K_{\NH})$}\label{exampleforproof}
\end{figure}

This point of intersection corresponds to a Nash equilibrium of Figure \ref{model1}.

\end{proof}

This Theorem is in itself not that useful as the properties of $f_{h}$ are difficult to ascertain.
Although the methodology alluded to is how the equilibria are found for the work presented here (exhaustive investigation of best response functions).
The following Lemma will however be of more use in Section \ref{results}.

\textbf{Lemma.}

Using the convention of Figure \ref{arrivalrateregions}:

\begin{itemize}

\item If $\lambda_{\NH}^{(a)}\leq \lambda_{\NH}^{(b)}$ and $\lambda_{\NH}^{(c)}\leq \lambda_{\NH}^{(d)}$ then $f_{\NH}(k)$ is a non-decreasing function in $k$.
\item If $\lambda_{\RG}^{(a)}\leq \lambda_{\RG}^{(c)}$ and $\lambda_{\RG}^{(b)}\leq \lambda_{\RG}^{(d)}$ then $f_{\RG}(k)$ is a non-decreasing function in $k$.

\end{itemize}

Before proving the Lemma the following observation is given:

\textbf{Observation.}

The utilisation $U_h=U_h(\lambda)$ is an increasing function in $\lambda$.

\begin{center}
As the traffic intensity at $h$ increases: $h$ gets busier.
\end{center}

\begin{proof}

A proof for the first part of the Lemma is given (the proof for the second part is analogous).

If $\lambda_{\NH}^{(a)}\leq \lambda_{\NH}^{(b)}$ and $\lambda_{\NH}^{(c)}\leq \lambda_{\NH}^{(d)}$, for given $K_{\NH}$: then as $K_{\RG}$ increases, the arrival rate at NH is non-increasing,
Similarly, for given $K_{{\RG}}$, as $K_{\NH}$ increases the arrival rate at RG is non-decreasing.

Using the above and the previous observation this implies:

\begin{itemize}
    \item The function $U_{\NH}=U_{\NH}(K_{\RG})$ is non-increasing;
    \item The function $U_{\NH}=U_{\NH}(K_{\NH})$ is non-decreasing.
\end{itemize}

A graphical proof of the lemma is then shown in Figure \ref{proof}.

\begin{figure}[!hbtp]
\begin{center}
\includegraphics[width=.7\textwidth]{./Images/proof.pdf}
\end{center}
\caption{Graphical proof of the fact that $f_{\NH}(K_{\RG})<f_{\NH}(K_{\RG}+1)$}\label{proof}
\end{figure}

Let $k^*=f_{NH}(K_{\RG})$ for a given $K_{\RG}$.
As $K_{\RG}$ increases, the utilisation $U_{\NH}(k^*)$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $U_{NH}(k^*)=t$ and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
Thus, $f_{\NH}(K_{\RG})\geq k^*$ as required.
\end{proof}

The aim of the work presented is to measure the inefficiency created by the removal of central control between CCUs.

We let $\widetilde T$ denote the sum of throughputs at Nash Equilibria obtained by solving the game of Figure \ref{model1} (in case of multiple equilibria we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{NH}, K_{RG}}\left(T_{NH}+T_{RG}\right)$.

The measure used to quantify inefficiency is the Price of Anarchy (PoA) \cite{Koutsoupias1999,TimRoughgarden}, which is the ratio of the social optimum welfare to the welfare of the worst Nash equilibrium.
That is, the ratio of the largest social welfare, $T^*$ to the smallest social welfare, $\widetilde{T}$, achieved at any Nash equilibrium. Thus:

$$\text{PoA}={{T^*}\over{\widetilde{T}}}$$

Note that the classic definition of PoA has been modified here to allow for a maximisation problem.
Social welfare is here considered to be a maximisation of throughput.
An immediate alignment of interests can be obtained by setting $t=1$.
This however would not be in the interest of the hospital (nor necessarily in the interests of patients) as it would imply aiming to run at 100\% utilisation which would not make for a robust system.
\textbf{A sensible value of $t$ is the lowest value of $t$ that ensures a low PoA}.

\section{Results}\label{results}

The game theoretic model of Figure \ref{model1} is solved using exhaustive consideration of best responses whilst taking advantage of the structure identified by the Lemma of Section \ref{queueingandgamemodels}. For any given pair of threshold strategies the matrix equation $\pi Q=0$ is solved by obtaining a basis for the Kernel of $Q$. For the purpose of this paper this is implemented in \cite{sage}.

\subsection{Model 1: Strict diversion}

This model assumes that if the bed occupancy level at both Units exceeds a predetermined threshold, then the admission to the CCU is cancelled (in reality this implies that patients will be admitted to a general ward within the hospital).
Recalling Figure \ref{arrivalrateregions} this implies:

\begin{minipage}[t]{0.5\textwidth}
\small{$$\lambda_{\NH}^{(r)}=\begin{cases}
\lambda_{\NH}, &\text{if }r=a\\
\lambda_{\NH}+\lambda_{\RG},  &\text{if }r=b\\
0, &\text{if }r\in\{c,d\}\\
\end{cases}$$}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\small{$$\lambda_{\RG}^{(r)}=\begin{cases}
\lambda_{\RG}, &\text{if }r=a\\
\lambda_{\NH}+\lambda_{\RG},  &\text{if }r=c\\
0, &\text{if }r\in\{b,d\}\\
\end{cases}$$}
\end{minipage}

We immediately see that the Lemma of Section \ref{queueingandgamemodels} holds and so a Nash Equilibrium for our model exists.

If either CCU chooses their threshold at zero, patients are not admitted at all, and, consequently both Units are closed.

Therefore, the matrix $Q$ has entries $q_{ij}$ as follows:
\begin{equation}
q_{ij}=\begin{cases} u_i\mu_{NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(1,0),\\
 v_i\mu_{RG} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,1),\\
 \lambda_{\NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0)\text{ and } u_i<K_{\NH} \text{ and } v_i<K_{\RG},\\
 \lambda_{\RG} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and } u_i<K_{\NH} \text{ and } v_i < K_{\RG},\\
\lambda_{\NH}+\lambda_{\RG} & \text{ if  } \left\{\begin{array}{l} (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and } u_i<K_{\NH} \text{ and } v_i \geq K_{\RG} \text{ or}\\ (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and } u_i \geq K_{\NH} \text{ and } v_i < K_{\RG},\\\end{array}\right.\\
0 & \text{ otherwise}.
\end{cases}
\end{equation}

For the parameters of Table \ref{parameter_values_model_1} the best responses are shown in Figure \ref{Fig:best_responses_model1}.
For example, in Figure \ref{Fig:best_responses_model1}a if RG chooses $K_{\RG}=6$, NH has best response $K_{\NH}=8$ .
Similarly, if $K_{\NH}=2$, RG has best response $K_{\RG}=15$.
A Nash equilibrium for our game is a pair of points that intersect.

\begin{figure}[!htbp]
$$
\begin{array}{cc}
\includegraphics[width=.5\textwidth]{./Images/best_responses_model1.pdf}&
\includegraphics[width=.5\textwidth]{./Images/best_responses_model1_t=0_6.pdf}\\
\text{(a: $t=0.8$)}&\text{(b: $t=0.6$)}
\end{array}
$$
\caption{Best responses for each hospital (a: $t=0.8$; b: $t=0.6$). The point of intersection is circled.} \label{Fig:best_responses_model1}
\end{figure}

For this model the Nash equilibrium is at $(8,16)$, which gives $\widetilde T=3.65$ and we obtain $T^*=3.65$.
Importantly, a PoA of 1 is not guaranteed for this problem.
For example in Figure \ref{Fig:best_responses_model1}b similar best response behaviour is shown for $t=0.6$ for which the $\text{PoA}=1.18$ (the optimal throughput is again at $(8,16)$).

Whilst removing central control, a certain influence can be exerted by a choice of $t$.
Figure \ref{Fig:target_demand_model1} shows the effect of $t$ and overall demand (note: the non linear scale).
We modify the demand rate from Table \ref{parameter_values_model_1} by taking $\lambda_h \leftarrow \lambda_h(1+x)$ for $-0.9\leq x\leq2$.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=.5\textwidth]{./Images/lnPoAmodel1targetvdemand.pdf}
\end{center}
\caption{PoA for different target and demand rates}\label{Fig:target_demand_model1}
\end{figure}

We see that an extremely large PoA is obtained for $t<0.2$.
For values of $t>0.5$ the PoA is still high: a PoA of 2 corresponds to 100\% less throughput of patients.
These findings seem to give some backing to the targets implemented throughout the NHS \cite{Bevan2006}.

In particular it can be seen that a value of $t>0.8$ becomes imperative for high demand.
The lowest value of $t$ for which gives PoA$=1$ for the actual demand levels ($x=0$) is in fact $t=0.72$.
It is also noted that as demand increases the effect of uncoordinated behaviour increases (and the recommended target also increases) as shown in Figure \ref{mintargetvdemand}.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=10cm]{./Images/argminPoAmodel1.pdf}
\caption{Lowest value of $t$ ensuring PoA$=1$} \label{mintargetvdemand}
\end{center}
\end{figure}

In this model, there is the potential for both CCUs to divert patients at the same time, and so patients are lost to the entire system. The model of the next section will investigate the effect of not allowing total rejections.

\subsection{Model 2: Soft diversion}

Recalling Figure \ref{arrivalrateregions}, this model assumes:

\begin{minipage}[t]{0.5\textwidth}
\small{$$\lambda_{NH}^{(r)}=\begin{cases}
\lambda_{NH}, &\text{if }r\in\{a,d\}\\
\lambda_{NH}+\lambda_{RG},  &\text{if }r=b\\
0, &\text{if }r=c\\
\end{cases}$$}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\small{$$\lambda_{RG}^{(r)}=\begin{cases}
\lambda_{RG}, &\text{if }r\in\{a,d\}\\
\lambda_{NH}+\lambda_{RG},  &\text{if }r=c\\
0, &\text{if }r=b\\
\end{cases}$$}
\end{minipage}

We immediately see that the Lemma of Section \ref{queueingandgamemodels} holds and so a Nash Equilibrium for our model exists.

This means that if bed occupancy levels at both Units exceed a pre-determined threshold, then diversions do not occur and each CCU has to accommodate their own patients.
In effect we are modelling a certain level of cooperation in this case where CCUs only divert if the other CCU is not busy.

Therefore, the transition matrix $Q$ is obtained from the following transition rates $q_{ij}$:

\begin{equation}
q_{ij}=\begin{cases} u_i\mu_{NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(1,0),\\
 v_i\mu_{RG} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,1),\\
 \lambda_{NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and }\left\{\begin{array}{l} u_i<K_{NH} \text{ and } v_i<K_{RG}  \text{ or } \\        u_i  \geq K_{NH} \text{ and } v_i  \geq K_{RG},\end{array}\right.\\
 \lambda_{RG} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and }\left\{\begin{array}{l}u_i< K_{NH}\text{ and }v_i<K_{RG}\text{ or }\\u_i\geq K_{NH}\text{ and }v_i\geq K_{RG}, \\\end{array}\right.\\\\
\lambda_{NH}+\lambda_{RG} & \text{ if  } \left\{\begin{array}{l} (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and } u_i<K_{NH} \text{ and } v_i \geq K_{RG} \text{ or }\\ (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and } u_i \geq K_{NH} \text{ and } v_i < K_{RG}, \\\end{array}\right.\\
0 & \text{ otherwise}.
\end{cases}
\end{equation}

As before, Figure \ref{Fig:target_demand_model2} presents the PoA for different target values and demand rate changes.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=10cm]{./Images/model2targetvdemand.pdf}
\caption{PoA for different target and demand rates for soft diversion} \label{Fig:target_demand_model2}
\end{center}
\end{figure}

We immediately note that the underlying cooperation that is now being forced on our players (divert only if the other player can accommodate the patients) has reduced the PoA.
Note that PoA$=1.02$ still implies a reduced throughput of 2\% which has very large cost implications for a national health service.
A tipping point is now visible as demand increases, this is similar to the profiles shown in \cite{Knight2013} and can be explained as follows:

\begin{itemize}
    \item When the demand is low, there is no scope for uncoordinated behaviour to be damaging.
    \item When the demand is very high, the system is saturated and once again uncoordinated behaviour has no negative effect in comparison to optimal behaviour.
    \item There is however a region of demand for which there is a high PoA.
\end{itemize}

For example, for $t=0.8$ the PoA starts to rapidly increase for demand changes higher than 0.1, and starts to decrease for a demand change of 0.6; this region will be investigated closely.
Table \ref{table_model2_target_demand} presents results for $t=0.8$ and a demand change from 0.1 to 0.6. For a 50\% increase in demand, without a matching increase in capacity, selfish behaviour of CCUs would incur 6\% less patient throughput.

 \begin{table}[!htbp]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Demand}&\textbf{Nash}&\multirow{2}{*}{\textbf{$\widetilde T$}}&\textbf{Nash NH}&\textbf{Nash RG}&\multirow{2}{*}{\textbf{$T^*$}}&\multirow{2}{*}{\textbf{PoA}}\\
\textbf{change, $x$}&\textbf{equilibrium}&\textbf{ }&\textbf{throughput}&\textbf{throughput}&\textbf{}&\textbf{}\\
\hline
0.1&(8,16)&3.92&1.50&2.42&3.92&1\\
0.2&(8,16)&3.92&1.50&2.42&3.92&1\\
0.3&(6,12)&4.19&1.65&2.54&4.33&1.03\\
0.4&(4,0)&4.22&1.65&2.57&4.48&1.06\\
0.5&(4,0)&4.22&1.65&2.57&4.48&1.06\\
0.6&(0,0)&4.42&1.69&2.72&4.68&1.06\\
\hline
\end{tabular}
\end{center}
\caption{Soft diversion results for $t=0.8$}\label{table_model2_target_demand}
\end{table}

Clearly, as the demand change increases, the Nash equilibrium thresholds decrease.
This is due to the fact that both CCUs are attempting to divert their patients in less busy states as these states become rarer.
If one CCU diverts early, the other will follow suit (both CCUs incrementally reacting to each other.
As a result the Nash equilibrium for $x=0.6$ is at $(0,0)$, meaning that each CCU takes care of their own patients.
As the demand increases even further the Nash equilibria remain at $(0,0)$ and the PoA decreases.

Figure \ref{mintargetvdemandmodel2} shows the lowest values of $t$ which gives a PoA of 1.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=12cm]{./Images/argminPoAmodel2.pdf}
\caption{Lowest value of $t$ ensuring PoA$=1$} \label{mintargetvdemandmodel2}
\end{center}
\end{figure}

\section{Conclusions}\label{conclusions}

In this work a generic game theoretical model has been presented that accounts for the selfish actions of two CCUs.
This game theoretic model is underpinned by a queueing model that takes into account the stochastic nature of queueing systems.
This work extends the application of game theoretic models already present in the literature to healthcare \cite{li2002cooperative, xie2006note}.

A result is proved that allows for the assertion of existence of Nash equilibrium. This result is then applied to two particular models that are influenced by discussions with a local health board:

\begin{itemize}
\item Strict diversion: patients can be lost to the system if both CCUs declare being in diversion.
\item Soft diversion: if both CCUs are in diversion then they cannot divert their own patients.
\end{itemize}

An analysis of the effect of selfish behaviour is given for both of these models in the form of PoA calculations.
The PoA is calculated so as to measure the effect of selfish behaviour on overall patient throughput.
High PoAs are found in the case of strict diversion which is to be expected as soft diversion implies a certain level of cooperation.
Importantly a non negligible effect of selfish behaviour is calculated for certain policy target values.
A recommendation of setting $t=0.72$ is found across both models. This gives some evidence to a particular target value of maximal utilisation in a two CCU ward setting.

This value of $t$ is investigated against increasing demand and is shown to be increasing in overall demand across the system.
Investigating demand is akin to investigating the capacity of the CCUs and as shown in Figure \ref{capacity}: if capacity is not sufficient selfish behaviour can have a very damaging effect on overall patient throughput.

\begin{figure}[!htbp]
$$\begin{array}{cc}
\includegraphics[width=.5\textwidth]{./Images/model1capacity.pdf}&
\includegraphics[width=.5\textwidth]{./Images/model2capacity.pdf}
\\
\text{a: Strict diversion}&\text{b: Soft diversion}\\
\end{array}$$
\caption{The effect of capacity on the PoA}\label{capacity}
\end{figure}

It is vital to acknowledge the limitations of the work presented:

\begin{itemize}
    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{knight2012comparisons, naor1969regulation});
    \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
    \item The restriction to pure strategies is influenced by discussions with ABHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.  However, allowing for mixed strategies could also be of interest.
\end{itemize}

Despite these limitations the work presented here gives a strong analytical evidence as to the use of policies in a decentralised healthcare environmenta local health board could involve the investigation of patient survival instead of throughput as utility.
This would be similar to work such as \cite{erkut2008ambulance, knight2012ambulance}.

The code used in this work was written in Python and can be found here: \url{drvinceknight/measuring...}.
The graphics for this paper were obtained using \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://sage.maths.cf.ac.uk/home/pub/122/}.

\newpage
\bibliographystyle{plain}
\bibliography{library}

\end{document}

### 2014-03-16 Paper/paper.tex
Updated readme with link and including link to github in paper
Update

@@
 \begin{itemize}
-    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{knight2012comparisons, naor1969regulation});
+    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{naor1969regulation, shone2013comparisons});
     \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
@@
 
-The code used in this work was written in Python and can be found here: \url{drvinceknight/measuring...}.
+The code used in this work can be found here: \url{https://github.com/drvinceknight/Measuring_the_price_of_anarchy_in_ccu_interactions}.
 The graphics for this paper were obtained using \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://sage.maths.cf.ac.uk/home/pub/122/}.

### 2014-03-17 Paper/paper.tex
Fixed ABHB to ABUHB

@@
 
-The main proposition of the work requested by the ABHB was to develop a mathematical model of bed occupancies at the CCUs at RG and NH.
+The main proposition of the work requested by the ABUHB was to develop a mathematical model of bed occupancies at the CCUs at RG and NH.
 After an initial analysis of the data, behavioural aspects became apparent; for example, delaying patients discharge if there was no pressure on CCU beds, or admitting fewer patients if bed occupancy levels were high.
@@
 This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close as possible to a certain target.
-As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABHB, long term threshold policies are a realistic consideration.
+As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABUHB, long term threshold policies are a realistic consideration.
 
@@
     \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
-    \item The restriction to pure strategies is influenced by discussions with ABHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.
+    \item The restriction to pure strategies is influenced by discussions with ABUHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.
 However, allowing for mixed strategies could also be of interest.

### 2014-03-21 Paper/paper.tex
Paper now includes table

@@
 \usepackage{makecell}
-\usepackage{tabularx}
+\usepackage{booktabs}
 \usepackage{longtable}
@@
 \begin{center}
-\begin{tabular}{|c|l|c|}
-\hline
-\textbf{Parameter}&\textbf{Parameter description}&\textbf{Parameter value}\\
-\hline
+\begin{tabular}{c|lc}
+\toprule
+Parameter&Parameter description&Parameter value\\
+\midrule
 $c_{\NH}$&the bed capacity at NH&8\\
-\hline
 $c_{\RG}$&the bed capacity at RG&16\\
-\hline
 $\lambda_{\NH}$&the arrival rate at NH (per day)&1.50 \\
-\hline
 $\lambda_{\RG}$&the arrival rate at RG (per day)&2.24\\
-\hline
 $\mu_{\NH}$&the service rate at NH (days)&0.262\\
-\hline
 $\mu_{\RG}$&the service rate at RG (days)&0.198\\
-\hline
 $t$& bed utilisation target & 0.8\\
-\hline
+\bottomrule
 \end{tabular}
@@
 Whilst removing central control, a certain influence can be exerted by a choice of $t$.
-Figure \ref{Fig:target_demand_model1} shows the effect of $t$ and overall demand (note: the non linear scale).
+Figure \ref{Fig:target_demand_model1} (note: the non linear scale) and Table \ref{tabletargetdemandm1} show the effect of $t$ and overall demand.
 We modify the demand rate from Table \ref{parameter_values_model_1} by taking $\lambda_h \leftarrow \lambda_h(1+x)$ for $-0.9\leq x\leq2$.
@@
 \end{figure}
+
+\begin{table}[!htbp]
+\begin{center}
+\begin{tabular}{c|ccccccccc}
+\toprule
+$x$&$t=0.15$&$t=0.27$&$t=0.4$&$t=0.52$&$t=0.64$&$t=0.76$&$t=0.88$&$t=1$\\
+\midrule
+-0.9&1.0&1.0&1.0&1.0&1.0&1.0&1.0&1.0\\
+-0.61&1.64&1.04&1.0&1.0&1.0&1.0&1.0&1.0\\
+-0.33&3.27&1.66&1.22&1.0&1.0&1.0&1.0&1.0\\
+-0.03&4.43&2.55&1.64&1.34&1.06&1.0&1.0&1.0\\
+0.26&5.23&2.99&2.1&1.51&1.28&1.09&1.0&1.0\\
+0.55&7.34&3.21&2.25&1.74&1.34&1.16&1.0&1.0\\
+0.84&7.6&3.81&2.32&1.79&1.46&1.17&1.03&1.0\\
+1.13&7.73&3.88&2.36&1.82&1.48&1.25&1.04&1.0\\
+1.41&7.81&3.91&2.61&1.97&1.58&1.26&1.09&1.0\\
+1.7&7.86&3.94&2.63&1.98&1.58&1.32&1.14&1.0\\
+1.99&7.89&3.95&2.64&1.98&1.59&1.33&1.14&1.0\\
+\bottomrule
+\end{tabular}
+\end{center}
+\caption{Numerical values of PoA for different target and demand rates}\label{tabletargetdemandm1}
+\end{table}
 
@@
 
-As before, Figure \ref{Fig:target_demand_model2} presents the PoA for different target values and demand rate changes.
+As before, Figure \ref{Fig:target_demand_model2} and Table \ref{tabletargetdemandm2} present the PoA for different target values and demand rate changes.
 
@@
 \end{figure}
+
+\begin{table}[!htbp]
+\begin{center}
+\begin{tabular}{c|ccccccccc}
+\toprule
+$x$&$t=0.15$&$t=0.27$&$t=0.4$&$t=0.52$&$t=0.64$&$t=0.76$&$t=0.88$&$t=1$\\
+\midrule
+-0.9&1.0&1.0&1.0&1.0&1.0&1.0&1.0&1.0\\
+-0.61&1.0&1.0&1.0&1.0&1.0&1.0&1.0&1.0\\
+-0.32&1.01&1.01&1.01&1.01&1.0&1.0&1.0&1.0\\
+-0.03&1.05&1.05&1.05&1.05&1.05&1.05&1.0&1.0\\
+0.26&1.06&1.06&1.06&1.06&1.06&1.06&1.06&1.0\\
+0.55&1.06&1.06&1.06&1.06&1.06&1.06&1.06&1.01\\
+0.84&1.05&1.05&1.05&1.05&1.05&1.05&1.05&1.04\\
+1.13&1.05&1.05&1.05&1.05&1.05&1.05&1.05&1.04\\
+1.42&1.04&1.04&1.04&1.04&1.04&1.04&1.04&1.04\\
+1.71&1.03&1.03&1.03&1.03&1.03&1.03&1.03&1.03\\
+1.99&1.03&1.03&1.03&1.03&1.03&1.03&1.03&1.03\\
+\bottomrule
+\end{tabular}
+\end{center}
+\caption{Numerical values of PoA for different target and demand rates}\label{tabletargetdemandm2}
+\end{table}
 
@@
 \begin{center}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\textbf{Demand}&\textbf{Nash}&\multirow{2}{*}{\textbf{$\widetilde T$}}&\textbf{Nash NH}&\textbf{Nash RG}&\multirow{2}{*}{\textbf{$T^*$}}&\multirow{2}{*}{\textbf{PoA}}\\
-\textbf{change, $x$}&\textbf{equilibrium}&\textbf{ }&\textbf{throughput}&\textbf{throughput}&\textbf{}&\textbf{}\\
-\hline
+\begin{tabular}{ccccccc}
+\toprule
+%\textbf{Demand}&\textbf{Nash}&\multirow{2}{*}{\textbf{$\widetilde T$}}&\textbf{Nash NH}&\textbf{Nash RG}&\multirow{2}{*}{\textbf{$T^*$}}&\multirow{2}{*}{\textbf{PoA}}\\
+%\textbf{change, $x$}&\textbf{equilibrium}&\textbf{ }&\textbf{throughput}&\textbf{throughput}&\textbf{}&\textbf{}\\
+$x$&Nash Equilibrium&$\tilde T$&Nash $T_{NH}$& Nash $T_{RG}$& $T^*$& PoA\\
+\midrule
 0.1&(8,16)&3.92&1.50&2.42&3.92&1\\
@@
 0.6&(0,0)&4.42&1.69&2.72&4.68&1.06\\
-\hline
+\bottomrule
 \end{tabular}

### 2014-04-04 Archive/Measuring_the_price_of_anarchy_in_ccu_interactions.tex

--- 2014-03-16 Paper/paper.tex
@@
 \title{Measuring the Price of Anarchy in Critical Care Unit Interactions}
-\author{Vincent Knight
+\author{Izabela Komenda*
     \and
-        Izabela Komenda*
+        Jeff Griffiths
     \and
-        Jeff Griffiths}
+        Vincent Knight}
 
@@
 \begin{array}{cc}
-\includegraphics[width=.5\textwidth]{./Images/NH.pdf}&\includegraphics[width=.5\textwidth]{./Images/RG.pdf}\\
+\includegraphics[width=.5\textwidth]{NH.pdf}&\includegraphics[width=.5\textwidth]{RG.pdf}\\
 h=NH&h=RG
@@
 \begin{array}{cc}
-\includegraphics[width=.5\textwidth]{./Images/NH_1_12.pdf}&\includegraphics[width=.5\textwidth]{./Images/RG_1_12.pdf}\\
+\includegraphics[width=.5\textwidth]{NH_1_12.pdf}&\includegraphics[width=.5\textwidth]{RG_1_12.pdf}\\
 h=\NH&h=\RG
@@
 \begin{figure}[!htbp]
-\hspace{2cm}For all $h\in\{\text{NH}, \text{RG}\}$ minimise:
-$$\left(U_{h}-t\right)^2$$
+\hspace{2cm}For all $h\in\{\text{NH}, \text{RG}\}$ maximize:
+$$U_{h}$$
 \hspace{2cm}Subject to:
@@
 0\leq & K_h \leq c_{h}\nonumber\\
-&K_h \in  \mathbb{Z}\nonumber
+&K_h \in  \mathbb{Z}\nonumber\\
+&U_h\leq t\nonumber
 \end{align}
@@
 
-This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close as possible to a certain target.
+\todoVK{We have a problem here, how do we know that a solution always exists?
+Might need to change problem to not have target as a contraint but instead simply consider distance from constraint.
+The problem with that is that we won't necessarily have the existence theorem anymore...
+I need to figure this out.}
+This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close to, without going past, a certain target.
 As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABHB, long term threshold policies are a realistic consideration.
 
-The following result is a sufficient condition for the existence of equilibrium:\\
+The following result is a sufficient condition for the existence of equilibria:\\
 
@@
 $$\begin{array}{cc}
-\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_NH.pdf}&
-\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_RG.pdf}
+\includegraphics[width=.5\textwidth]{best_responses_ex_for_proof_NH.pdf}&
+\includegraphics[width=.5\textwidth]{best_responses_ex_for_proof_RG.pdf}
 \end{array}$$
@@
 \begin{center}
-\includegraphics[width=.7\textwidth]{./Images/proof.pdf}
+\includegraphics[width=.7\textwidth]{proof.pdf}
 \end{center}
@@
 
-Let $k^*=f_{NH}(K_{\RG})$ for a given $K_{\RG}$.
-As $K_{\RG}$ increases, the utilisation $U_{\NH}(k^*)$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
-As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $U_{NH}(k^*)=t$ and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
-Thus, $f_{\NH}(K_{\RG})\geq k^*$ as required.
+Let $k^*=f(K_{\RG})$ for a given $K_{\RG}$.
+As $K_{\RG}$ increases, the utilisation $U_{\NH}$ for $k^*$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
+Thus, $f_{\NH}(K_{\RG})\geq k^*$: strict inequality depending on whether or not the utilisation for $K_{\NH}>k^*$ is below $t$.
 \end{proof}
@@
 \section{Results}\label{results}
-
-The game theoretic model of Figure \ref{model1} is solved using exhaustive consideration of best responses whilst taking advantage of the structure identified by the Lemma of Section \ref{queueingandgamemodels}.
-For any given pair of threshold strategies the matrix equation $\pi Q=0$ is solved by obtaining a basis for the Kernel of $Q$.
-For the purpose of this paper this is implemented in \cite{sage}.
 
@@
 For the parameters of Table \ref{parameter_values_model_1} the best responses are shown in Figure \ref{Fig:best_responses_model1}.
-For example, in Figure \ref{Fig:best_responses_model1}a if RG chooses $K_{\RG}=6$, NH has best response $K_{\NH}=8$ .
-Similarly, if $K_{\NH}=2$, RG has best response $K_{\RG}=15$.
-A Nash equilibrium for our game is a pair of points that intersect.
+For example, in Figure \ref{Fig:best_responses_model1}a if RG chooses $K_{\RG}=6$, NH has best response $K_{\NH}=7$ .
+Similarly, if NH has best response $K_{\NH}=3$, RG has best response $K_{\RG}=15$.
+A Nash equilibrium for our game is a pair of points that intersect (in this case: $(K_{\NH}, K_{\RG})=(8,16)$ is a Nash equilibrium).
 
@@
 \begin{array}{cc}
-\includegraphics[width=.5\textwidth]{./Images/best_responses_model1.pdf}&
-\includegraphics[width=.5\textwidth]{./Images/best_responses_model1_t=0_6.pdf}\\
+\includegraphics[width=.5\textwidth]{best_responses_model1.pdf}&
+\includegraphics[width=.5\textwidth]{best_responses_model1_t=0_6.pdf}\\
 \text{(a: $t=0.8$)}&\text{(b: $t=0.6$)}
@@
 
-For this model the Nash equilibrium is at $(8,16)$, which gives $\widetilde T=3.65$ and we obtain $T^*=3.65$.
+For this model the Nash equilibrium is at $(8,16)$, which gives $\widetilde T=3.64$ and we obtain $T^*=3.64$.
 Importantly, a PoA of 1 is not guaranteed for this problem.
-For example in Figure \ref{Fig:best_responses_model1}b similar best response behaviour is shown for $t=0.6$ for which the $\text{PoA}=1.18$ (the optimal throughput is again at $(8,16)$).
+For example in Figure \ref{Fig:best_responses_model1}b similar best response behaviour is shown for $t=0.6$ for which the PoA$=1.18$ (the optimal throughput is again at $(8,16)$).
 
 Whilst removing central control, a certain influence can be exerted by a choice of $t$.
-Figure \ref{Fig:target_demand_model1} shows the effect of $t$ and overall demand (note: the non linear scale).
+Figure \ref{Fig:target_demand_model1} shows the effect of $t$ and overall demand. Note, the non linear scale in \ref{Fig:target_demand_model1}a.
 We modify the demand rate from Table \ref{parameter_values_model_1} by taking $\lambda_h \leftarrow \lambda_h(1+x)$ for $-0.9\leq x\leq2$.
@@
 \begin{figure}[!htbp]
-\begin{center}
-\includegraphics[width=.5\textwidth]{./Images/lnPoAmodel1targetvdemand.pdf}
-\end{center}
-\caption{PoA for different target and demand rates}\label{Fig:target_demand_model1}
+$$
+\begin{array}{cc}
+\includegraphics[width=.5\textwidth]{lnPoAmodel1targetvdemand.pdf}
+&
+\includegraphics[width=.5\textwidth]{model1targetvdemandfort-5.pdf}\\
+\text{(a)}&\text{(b)}
+\end{array}
+$$
+\caption{PoA for different target and demand rates (the second plot is a given region of the first)} \label{Fig:target_demand_model1}
 \end{figure}
 
-We see that an extremely large PoA is obtained for $t<0.2$.
-For values of $t>0.5$ the PoA is still high: a PoA of 2 corresponds to 100\% less throughput of patients.
+We see that an extremely large PoA is obtained for $t<0.2$. If we concentrate on a value of $t>0.5$ then the PoA is still extremely high: a PoA of 1.9 corresponds to 90\% less throughput of patients.
 These findings seem to give some backing to the targets implemented throughout the NHS \cite{Bevan2006}.
@@
 \begin{center}
-\includegraphics[width=10cm]{./Images/argminPoAmodel1.pdf}
+\includegraphics[width=10cm]{argminPoAmodel1.pdf}
 \caption{Lowest value of $t$ ensuring PoA$=1$} \label{mintargetvdemand}
@@
 \begin{center}
-\includegraphics[width=10cm]{./Images/model2targetvdemand.pdf}
+\includegraphics[width=10cm]{model2targetvdemand.pdf}
 \caption{PoA for different target and demand rates for soft diversion} \label{Fig:target_demand_model2}
@@
 \hline
-0.1&(8,16)&3.92&1.50&2.42&3.92&1\\
-0.2&(8,16)&3.92&1.50&2.42&3.92&1\\
-0.3&(6,12)&4.19&1.65&2.54&4.33&1.03\\
-0.4&(4,0)&4.22&1.65&2.57&4.48&1.06\\
-0.5&(4,0)&4.22&1.65&2.57&4.48&1.06\\
-0.6&(0,0)&4.42&1.69&2.72&4.68&1.06\\
+0.1&(8,16)&3.91&1.51&2.41&3.91&1\\
+0.2&(8,15)&4.11&1.63&2.48&4.14&1.06\\
+0.3&(5,10)&4.11&1.63&2.48&4.31&1.07\\
+0.4&(4,0)&4.20&1.65&2.55&4.46&1.06\\
+0.5&(3,0)&4.30&1.66&2.64&4.57&1.06\\
+0.6&(0,0)&4.39&1.68&2.71&4.65&1.06\\
 \hline
@@
 \begin{center}
-\includegraphics[width=12cm]{./Images/argminPoAmodel2.pdf}
+\includegraphics[width=12cm]{argminPoAmodel2.pdf}
 \caption{Lowest value of $t$ ensuring PoA$=1$} \label{mintargetvdemandmodel2}
@@
 
-In this work a generic game theoretical model has been presented that accounts for the selfish actions of two CCUs.
+In this work a generic game theoretical model has been presented that accounts for selfish actions of two CCUs.
 This game theoretic model is underpinned by a queueing model that takes into account the stochastic nature of queueing systems.
-This work extends the application of game theoretic models already present in the literature to healthcare \cite{li2002cooperative, xie2006note}.
+This work extends the application of Game Theoretic models already present in the literature to healthcare \cite{li2002cooperative, xie2006note}.
 
-A result is proved that allows for the assertion of existence of Nash equilibrium. This result is then applied to two particular models that are influenced by discussions with a local health board:
+A result is proved that allows for the assertion of existence of Nash equilibrium. This result is then applied to two particular models that are influenced by discussions with ABHB:
 
@@
 $$\begin{array}{cc}
-\includegraphics[width=.5\textwidth]{./Images/model1capacity.pdf}&
-\includegraphics[width=.5\textwidth]{./Images/model2capacity.pdf}
+\includegraphics[width=.5\textwidth]{model1capacity.pdf}&
+\includegraphics[width=.5\textwidth]{model2capacity.pdf}
 \\
-\text{a: Strict diversion}&\text{b: Soft diversion}\\
+\text{a: Strict diversion}&\text{a: Soft diversion}\\
 \end{array}$$
@@
 \begin{itemize}
-    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{naor1969regulation, shone2013comparisons});
+    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{knight2012comparisons, naor1969regulation});
     \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
@@
 
-Despite these limitations the work presented here gives a strong analytical evidence as to the use of policies in a decentralised healthcare environmenta local health board could involve the investigation of patient survival instead of throughput as utility.
+Despite these limitations the work presented here gives a strong analytical evidence as to the use of policies in a decentralised healthcare environment.
+
+Further work could involve the investigation of patient survival instead of throughput as utility.
 This would be similar to work such as \cite{erkut2008ambulance, knight2012ambulance}.
 
-The code used in this work can be found here: \url{https://github.com/drvinceknight/Measuring_the_price_of_anarchy_in_ccu_interactions}.
-The graphics for this paper were obtained using \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://sage.maths.cf.ac.uk/home/pub/122/}.
+The code used in this work was written in Python and can be found here: \url{drvinceknight/measuring...}.
+The graphics for this paper were obtained using \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://sage.maths.cf.ac.uk/home/pub/120/}.
 

### 2014-04-04 Paper/paper.tex
update
fixed equilibium/a

@@
 \title{Measuring the Price of Anarchy in Critical Care Unit Interactions}
-\author{Vincent Knight
+\author{Vincent Knight*
     \and
-        Izabela Komenda*
+        Izabela Komenda
     \and
@@
 
-The following result is a sufficient condition for the existence of equilibrium:\\
+The following result is a sufficient condition for the existence of a equilibrium:\\
 
@@
 
-We let $\widetilde T$ denote the sum of throughputs at Nash Equilibria obtained by solving the game of Figure \ref{model1} (in case of multiple equilibria we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{NH}, K_{RG}}\left(T_{NH}+T_{RG}\right)$.
+We let $\widetilde T$ denote the sum of throughputs at the Nash Equilibrium obtained by solving the game of Figure \ref{model1} (in case of multiple equilibria we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{NH}, K_{RG}}\left(T_{NH}+T_{RG}\right)$.
 
@@
 
+Also, for very low values of demand, cooperation can be obtained with no target.
 \begin{itemize}
@@
 As a result the Nash equilibrium for $x=0.6$ is at $(0,0)$, meaning that each CCU takes care of their own patients.
-As the demand increases even further the Nash equilibria remain at $(0,0)$ and the PoA decreases.
+As the demand increases even further the Nash equilibrium remains at $(0,0)$ and the PoA decreases.
 
 Figure \ref{mintargetvdemandmodel2} shows the lowest values of $t$ which gives a PoA of 1.
+We see that as demand increases this value also increases.
+Also, for very low values of demand, cooperation can be obtained with no target.
+For the actual demand ($x=0$) a target value of $t=0.72$ is once again recommended.
 
@@
 
-A result is proved that allows for the assertion of existence of Nash equilibrium. This result is then applied to two particular models that are influenced by discussions with a local health board:
+A result is proved that allows for the assertion of existence of a Nash equilibrium. This result is then applied to two particular models that are influenced by discussions with a local health board:
 

### 2014-04-05 Archive/CCU_QG_M1.py
removing old stuff

@@ -1,203 +1,0 @@
-#!/usr/bin/env python
-from __future__ import division
-import copy
-import csv
-"""Measuring the Price of Anarchy in Critical Care Unit Interactions
-
-Code to obtain the PoA by exhaustive search of best responses for model 1 of the paper.
-
-usage:
-    python CCU_QG_M1.py [t]
-
-The above will run a basic example with parameters written after `if __name__ == '__main__'` statement in this file.
-If a value of t is passed then the PoA will be calculated with that value of t as a target.
-
-Alternatively (and indeed how this was run for the paper) this file can be used as a library: `import CCU_QG_M1`.
-"""
-
-
-def name_state_i(k,n):
-    """
-    A function used to keep track of states for player 1.
-    """
-    return int((k-1)/(n+1))
-
-def name_state_j(k,n):
-    """
-    A function used to keep track of states for player 2.
-    """
-    return (k-1)%(n+1)
-
-def q(a,b,c,d,k1,k2,mu1,mu2,lmbda1,lmbda2,m,n):
-    """
-    Returns the probability of going from state (a,b) to state (c,d), assuming thresholds k1, k2. This is the transition rates for model 1.
-    """
-
-    if (a-c,b-d)==(1,0):
-        return mu1*a
-    if (a-c,b-d)==(0,1):
-        return mu2*b
-    if (a < k1 and b < k2) and (a-c,b-d)==(-1,0):
-        return lmbda1
-    if (a < k1 and b < k2) and (a-c,b-d)==(0,-1):
-        return lmbda2
-    if ((a-c,b-d)==(-1,0) and a < k1 and b >= k2) or ((a-c,b-d)==(0,-1) and a >= k1 and b < k2):
-        return lmbda1 + lmbda2
-    if (a,b) == (c,d):
-        return -sum([q(a,b,i,j,k1,k2,mu1,mu2,lmbda1,lmbda2,m,n) for i in range(m+1) for j in range(n+1) if (i,j)!=(a,b)])  # Obtain diagonal entries
-    return 0
-
-
-def Transition_Rate_Matrix(m,n,k1,k2,mu1,mu2,lmbda1,lmbda2):
-    """
-    Obtain the transition rate matrix.
-    """
[…]

### 2014-04-05 Archive/CCU_QG_M2.py

@@ -1,221 +1,0 @@
-#!/usr/bin/env python
-from __future__ import division
-import copy
-import csv
-"""Measuring the Price of Anarchy in Critical Care Unit Interactions
-
-Code to obtain the PoA by exhaustive search of best responses for model 2 of the paper.
-
-usage:
-    python CCU_QG_M2.py
-
-The above will run a basic example with parameters written after `if __name__ == '__main__'` statement in this file.
-
-Alternatively (and indeed how this was run for the paper) this file can be used as a library: `import CCU_QG_M1`.
-"""
-
-
-def name_state_i(k,n):
-    """
-    A function used to keep track of states for player 1.
-    """
-    return int((k-1)/(n+1))
-
-def name_state_j(k,n):
-    """
-    A function used to keep track of states for player 2.
-    """
-    return (k-1)%(n+1)
-
-def q(a,b,c,d,k1,k2,mu1,mu2,lmbda1,lmbda2,m,n):
-    """
-    Returns the probability of going from state (a,b) to state (c,d), assuming thresholds k1, k2. This is the transition rates for model 2.
-    """
-    if (a-c,b-d)==(1,0):
-        return mu1*a
-    if (a-c,b-d)==(0,1):
-        return mu2*b
-    if ((a < k1 and b < k2) or (a >= k1 and b >= k2)) and (a-c,b-d)==(-1,0):
-        return lmbda1
-    if ((a < k1 and b < k2) or (a >= k1 and b >= k2)) and (a-c,b-d)==(0,-1):
-        return lmbda2
-    if ((a-c,b-d)==(-1,0) and a < k1 and b >= k2) or ((a-c,b-d)==(0,-1) and a >= k1 and b < k2):
-        return lmbda1 + lmbda2
-    if (a,b) == (c,d):
-        return -sum([q(a,b,i,j,k1,k2,mu1,mu2,lmbda1,lmbda2,m,n) for i in range(m+1) for j in range(n+1) if (i,j)!=(a,b)])  # Obtain diagonal entries
-    return 0
-
-
-def Transition_Rate_Matrix(m,n,k1,k2,mu1,mu2,lmbda1,lmbda2):
-    """
-    Obtain the transition rate matrix.
-    """
[…]

### 2014-04-05 Paper/paper.tex
Some tweaks (E and e)

@@
 The methodology involves the use of a normal form game underpinned by a two dimensional continuous Markov chain.
-A theoretical result is given that ensures the existence of a Nash equilibrium.
+A theoretical result is given that ensures the existence of a Nash Equilibrium.
 
@@
 \begin{itemize}
-    \item Section \ref{queueingandgamemodels} presents the general methodology as well as a theoretical existence condition for Nash equilibrium;
+    \item Section \ref{queueingandgamemodels} presents the general methodology as well as a theoretical existence condition for Nash Equilibrium;
     \item Section \ref{results} presents the findings from two models;
@@
 
-The following result is a sufficient condition for the existence of a equilibrium:\\
+The following result is a sufficient condition for the existence of an equilibrium:\\
 
@@
 
-If $f_{h}(k)$ is a non-decreasing function in $k$ then the game of Figure \ref{model1} has at least one Nash equilibrium.
+If $f_{h}(k)$ is a non-decreasing function in $k$ then the game of Figure \ref{model1} has at least one Nash Equilibrium.
 
@@
 
-This point of intersection corresponds to a Nash equilibrium of Figure \ref{model1}.
+This point of intersection corresponds to a Nash Equilibrium of Figure \ref{model1}.
 
@@
 
-The measure used to quantify inefficiency is the Price of Anarchy (PoA) \cite{Koutsoupias1999,TimRoughgarden}, which is the ratio of the social optimum welfare to the welfare of the worst Nash equilibrium.
-That is, the ratio of the largest social welfare, $T^*$ to the smallest social welfare, $\widetilde{T}$, achieved at any Nash equilibrium. Thus:
+The measure used to quantify inefficiency is the Price of Anarchy (PoA) \cite{Koutsoupias1999,TimRoughgarden}, which is the ratio of the social optimum welfare to the welfare of the worst Nash Equilibrium.
+That is, the ratio of the largest social welfare, $T^*$ to the smallest social welfare, $\widetilde{T}$, achieved at any Nash Equilibrium. Thus:
 
@@
 Similarly, if $K_{\NH}=2$, RG has best response $K_{\RG}=15$.
-A Nash equilibrium for our game is a pair of points that intersect.
+A Nash Equilibrium for our game is a pair of points that intersect.
 
@@
 
-For this model the Nash equilibrium is at $(8,16)$, which gives $\widetilde T=3.65$ and we obtain $T^*=3.65$.
+For this model the Nash Equilibrium is at $(8,16)$, which gives $\widetilde T=3.65$ and we obtain $T^*=3.65$.
 Importantly, a PoA of 1 is not guaranteed for this problem.
@@
 
-Clearly, as the demand change increases, the Nash equilibrium thresholds decrease.
+Clearly, as the demand change increases, the Nash Equilibrium thresholds decrease.
 This is due to the fact that both CCUs are attempting to divert their patients in less busy states as these states become rarer.
 If one CCU diverts early, the other will follow suit (both CCUs incrementally reacting to each other.
-As a result the Nash equilibrium for $x=0.6$ is at $(0,0)$, meaning that each CCU takes care of their own patients.
-As the demand increases even further the Nash equilibrium remains at $(0,0)$ and the PoA decreases.
+As a result the Nash Equilibrium for $x=0.6$ is at $(0,0)$, meaning that each CCU takes care of their own patients.
+As the demand increases even further the Nash Equilibrium remains at $(0,0)$ and the PoA decreases.
 
@@
 
-A result is proved that allows for the assertion of existence of a Nash equilibrium. This result is then applied to two particular models that are influenced by discussions with a local health board:
+A result is proved that allows for the assertion of existence of a Nash Equilibrium. This result is then applied to two particular models that are influenced by discussions with a local health board:
 

### 2014-12-07 Paper/paper.tex
Replacing selfish with the word rational throughout

@@
 Table \ref{table_model2_target_demand} presents results for $t=0.8$ and a demand change from 0.1 to 0.6.
-For a 50\% increase in demand, without a matching increase in capacity, selfish behaviour of CCUs would incur 6\% less patient throughput.
+For a 50\% increase in demand, without a matching increase in capacity, rational behaviour of CCUs would incur 6\% less patient throughput.
 
@@
 
-In this work a generic game theoretical model has been presented that accounts for the selfish actions of two CCUs.
+In this work a generic game theoretical model has been presented that accounts for the rational actions of two CCUs.
 This game theoretic model is underpinned by a queueing model that takes into account the stochastic nature of queueing systems.
@@
 
-An analysis of the effect of selfish behaviour is given for both of these models in the form of PoA calculations.
-The PoA is calculated so as to measure the effect of selfish behaviour on overall patient throughput.
+An analysis of the effect of rational behaviour is given for both of these models in the form of PoA calculations.
+The PoA is calculated so as to measure the effect of rational behaviour on overall patient throughput.
 High PoAs are found in the case of strict diversion which is to be expected as soft diversion implies a certain level of cooperation.
-Importantly a non negligible effect of selfish behaviour is calculated for certain policy target values.
+Importantly a non negligible effect of rational behaviour is calculated for certain policy target values.
 A recommendation of setting $t=0.72$ is found across both models. This gives some evidence to a particular target value of maximal utilisation in a two CCU ward setting.
@@
 This value of $t$ is investigated against increasing demand and is shown to be increasing in overall demand across the system.
-Investigating demand is akin to investigating the capacity of the CCUs and as shown in Figure \ref{capacity}: if capacity is not sufficient selfish behaviour can have a very damaging effect on overall patient throughput.
+Investigating demand is akin to investigating the capacity of the CCUs and as shown in Figure \ref{capacity}: if capacity is not sufficient rational behaviour can have a very damaging effect on overall patient throughput.
 

### 2014-12-08 Paper/paper.tex
Fixing abstract
Adding exit arrows to diagram
Starting to relabel states for demand

@@
 The methodology involves the use of a normal form game underpinned by a two dimensional continuous Markov chain.
-A theoretical result is given that ensures the existence of a Nash Equilibrium.
+A theorem is given that proves that a Nash Equilibrium exists in pure strategies for the games considered.
 
@@
 \node at ($(B) + (0,-.8)$) {Divert?};
+\draw [->] (A) -- ($(A)+(0,-.5)$);
+\draw [->] (B) -- ($(B)+(0,.5)$);
 \end{tikzpicture}
@@
 Given the proximity of the two CCUs, one CCU could for example divert their patients to the other.
-Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_h^{(r)}$ for $h\in\{\NH, \RG\}$ and $r\in\{a, b, c, d\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $a,b,c \text{ and } d$ are regions with boundaries defined by the capacity thresholds.
+Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_h^{(r)}$ for $h\in\{\NH, \RG\}$ and $r\in\{(l,l), (l,h), (h,l), (h,h)\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $a,b,c \text{ and } d$ are regions with boundaries defined by the capacity thresholds.
 It is also assumed that diverted patients will be treated under the length of stay profile of the CCU they are admitted to.

### 2014-12-09 Paper/paper.tex
Fixing the arrows diagram

@@
 \usepackage{setspace}
-\usepackage{multirow}
-\usepackage{multicol}
 \usepackage{color}
@@
         \draw (ab) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ac);
-        \draw (ab) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ac);
+        \draw (ab) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (ac);
 
         \draw (ac) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisa1);
-        \draw (ac) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisa1);
+        \draw (ac) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisa1);
 
         \draw (ellipsisa1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ak);
-        \draw (ellipsisa1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ak);
+        \draw (ellipsisa1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (ak);
 
         \draw (ak) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisa2);
-        \draw (ak) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisa2);
+        \draw (ak) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG}+1)\mu_{\RG}$} (ellipsisa2);
 
         \draw (ellipsisa2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (az);
-        \draw (ellipsisa2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (az);
+        \draw (ellipsisa2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (az);
         % -----------------------------------------------
@@
         \draw (bb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bc);
-        \draw (bb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bc);
+        \draw (bb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (bc);
 
         \draw (bc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisb1);
-        \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisb1);
+        \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisb1);
 
         \draw (ellipsisb1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bk);
-        \draw (ellipsisb1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bk);
+        \draw (ellipsisb1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (bk);
 
         \draw (bk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisb2);
-        \draw (bk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisb2);
+        \draw (bk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisb2);
 
         \draw (ellipsisb2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (bz);
-        \draw (ellipsisb2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bz);
+        \draw (ellipsisb2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (bz);
         % With previous row:
@@
         \draw (cb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (cc);
-        \draw (cb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cc);
+        \draw (cb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (cc);
 
         \draw (cc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisc1);
-        \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisc1);
+        \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisc1);
 
         \draw (ellipsisc1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ck);
-        \draw (ellipsisc1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ck);
+        \draw (ellipsisc1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (ck);
 
         \draw (ck) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisc2);
-        \draw (ck) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisc2);
+        \draw (ck) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisc2);
 
         \draw (ellipsisc2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (cz);
-        \draw (ellipsisc2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cz);
+        \draw (ellipsisc2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (cz);
         % With previous row:
         \draw (ba) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ca);
-        \draw (ba) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ca);
+        \draw (ba) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ca);
 
         \draw (bb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (cb);
-        \draw (bb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cb);
+        \draw (bb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (cb);
 
         \draw (bc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (cc);
-        \draw (bc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cc);
+        \draw (bc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (cc);
 
         \draw (ellipsisb1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisc1);
-        \draw (ellipsisb1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisc1);
+        \draw (ellipsisb1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ellipsisc1);
 
         \draw (bk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ck);
-        \draw (bk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ck);
+        \draw (bk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ck);
 
         \draw (ellipsisb2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisc2);
-        \draw (ellipsisb2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisc2);
+        \draw (ellipsisb2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ellipsisc2);
 
@@
         \draw (db) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (dc);
-        \draw (db) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (dc);
+        \draw (db) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (dc);
 
         \draw (dc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisd1);
-        \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisd1);
+        \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisd1);
 
         \draw (ellipsisd1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (dk);
-        \draw (ellipsisd1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (dk);
+        \draw (ellipsisd1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (dk);
 
         \draw (dk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisd2);
-        \draw (dk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisd2);
+        \draw (dk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisd2);
 
         \draw (ellipsisd2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (dz);
-        \draw (ellipsisd2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (dz);
+        \draw (ellipsisd2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (dz);
         % With previous row:
         \draw (ca) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (da);
-        \draw (ca) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (da);
+        \draw (ca) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (da);
 
         \draw (cb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (db);
-        \draw (cb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (db);
+        \draw (cb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (db);
 
         \draw (cc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (dc);
-        \draw (cc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dc);
+        \draw (cc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (dc);
 
         \draw (ellipsisc1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisd1);
-        \draw (ellipsisc1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisd1);
+        \draw (ellipsisc1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (ellipsisd1);
 
         \draw (ck) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (dk);
-        \draw (ck) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dk);
+        \draw (ck) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (dk);
 
         \draw (ellipsisc2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisd2);
-        \draw (ellipsisc2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisd2);
+        \draw (ellipsisc2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (ellipsisd2);
 
@@
         \draw (eb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ec);
-        \draw (eb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ec);
+        \draw (eb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (ec);
 
         \draw (ec) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ellipsise1);
-        \draw (ec) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsise1);
+        \draw (ec) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsise1);
 
         \draw (ellipsise1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ek);
-        \draw (ellipsise1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ek);
+        \draw (ellipsise1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (ek);
 
         \draw (ek) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsise2);
-        \draw (ek) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsise2);
+        \draw (ek) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsise2);
 
         \draw (ellipsise2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ez);
-        \draw (ellipsise2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ez);
+        \draw (ellipsise2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (ez);
         % With previous row:
         \draw (da) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ea);
-        \draw (da) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ea);
+        \draw (da) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (ea);
 
         \draw (db) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (eb);
-        \draw (db) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (eb);
+        \draw (db) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (eb);
 
         \draw (dc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ec);
-        \draw (dc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ec);
+        \draw (dc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (ec);
 
         \draw (ellipsisd1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsise1);
-        \draw (ellipsisd1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsise1);
+        \draw (ellipsisd1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (ellipsise1);
 
         \draw (dk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ek);
-        \draw (dk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ek);
+        \draw (dk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (ek);
 
         \draw (ellipsisd2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsise2);
-        \draw (ellipsisd2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsise2);
+        \draw (ellipsisd2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (ellipsise2);
 
         \draw (dz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ez);
-        \draw (dz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ez);
+        \draw (dz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (ez);
         % Sixth row--------------------------------------
@@
         \draw (fb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fc);
-        \draw (fb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fc);
+        \draw (fb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (fc);
 
         \draw (fc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ellipsisf1);
-        \draw (fc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisf1);
+        \draw (fc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisf1);
 
         \draw (ellipsisf1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fk);
-        \draw (ellipsisf1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fk);
+        \draw (ellipsisf1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (fk);
 
         \draw (fk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisf2);
-        \draw (fk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisf2);
+        \draw (fk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisf2);
 
         \draw (ellipsisf2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (fz);
-        \draw (ellipsisf2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fz);
+        \draw (ellipsisf2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (fz);
         % With previous row:
         \draw (ea) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fa);
-        \draw (ea) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fa);
+        \draw (ea) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH}+1)\mu_{\NH}$} (fa);
 
-        \draw (eb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fb);
-        \draw (eb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fb);
+        \draw (eb) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(c)}$} (fb);
+        \draw (eb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH} + 1)\mu_{\NH}$} (fb);
 
-        \draw (ec) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fc);
-        \draw (ec) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fc);
+        \draw (ec) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(c)}$} (fc);
+        \draw (ec) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH} + 1)\mu_{\NH}$} (fc);
 
-        \draw (ellipsise1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (ellipsisf1);
-        \draw (ellipsise1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisf1);
+        \draw (ellipsise1) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(c)}$} (ellipsisf1);
+        \draw (ellipsise1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH} + 1)\mu_{\NH}$} (ellipsisf1);
 
-        \draw (ek) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (fk);
-        \draw (ek) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fk);
+        \draw (ek) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(d)}$} (fk);
+        \draw (ek) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH} + 1)\mu_{\NH}$} (fk);
 
-        \draw (ellipsise2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (ellipsisf2);
-        \draw (ellipsise2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisf2);
+        \draw (ellipsise2) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(d)}$} (ellipsisf2);
+        \draw (ellipsise2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH} + 1)\mu_{\NH}$} (ellipsisf2);
 
-        \draw (ez) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (fz);
-        \draw (ez) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fz);
+        \draw (ez) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(d)}$} (fz);
+        \draw (ez) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH}+1)\mu_{\NH}$} (fz);
         % Final row--------------------------------------
@@
         \draw (zb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zc);
-        \draw (zb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zc);
+        \draw (zb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (zc);
 
         \draw (zc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisz1);
-        \draw (zc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisz1);
+        \draw (zc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisz1);
 
         \draw (ellipsisz1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zk);
-        \draw (ellipsisz1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zk);
+        \draw (ellipsisz1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (zk);
 
         \draw (zk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisz2);
-        \draw (zk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisz2);
+        \draw (zk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisz2);
 
         \draw (ellipsisz2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zz);
-        \draw (ellipsisz2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zz);
+        \draw (ellipsisz2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (zz);
         % With previous row:
         \draw (fa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (za);
-        \draw (fa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (za);
+        \draw (fa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (za);
 
         \draw (fb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (zb);
-        \draw (fb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zb);
+        \draw (fb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (zb);
 
         \draw (fc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (zc);
-        \draw (fc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zc);
+        \draw (fc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (zc);
 
         \draw (ellipsisf1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (ellipsisz1);
-        \draw (ellipsisf1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisz1);
+        \draw (ellipsisf1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (ellipsisz1);
 
         \draw (fk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (zk);
-        \draw (fk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zk);
+        \draw (fk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (zk);
 
         \draw (ellipsisf2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (ellipsisz2);
-        \draw (ellipsisf2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisz2);
+        \draw (ellipsisf2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (ellipsisz2);
 
         \draw (fz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (zz);
-        \draw (fz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zz);
+        \draw (fz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (zz);
 

### 2014-12-09 Paper/paper.tex
Fixing a setnence that is broken

@@
 
-Despite these limitations the work presented here gives a strong analytical evidence as to the use of policies in a decentralised healthcare environmenta local health board could involve the investigation of patient survival instead of throughput as utility.
+Despite these limitations the work presented here gives a strong analytical evidence as to the use of policies in a decentralised healthcare environment.
+Further work could involve the investigation of patient survival instead of throughput as utility.
 This would be similar to work such as \cite{erkut2008ambulance, knight2012ambulance}.

### 2014-12-09 Paper/paper.tex
Have regions fixed in intro section

@@
 Given the proximity of the two CCUs, one CCU could for example divert their patients to the other.
-Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_h^{(r)}$ for $h\in\{\NH, \RG\}$ and $r\in\{(l,l), (l,h), (h,l), (h,h)\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $a,b,c \text{ and } d$ are regions with boundaries defined by the capacity thresholds.
+Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_h^{r}$ for $h\in\{\NH, \RG\}$ and $r\in\{(l,l), (l,h), (h,l), (h,h)\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $r$ denotes regions with boundaries defined by the capacity thresholds.
+For example $(l,h)$ denotes a region for which $\NH$ experiences \textit{low} demand and $\RG$ experiences \textit{high} demand.
 It is also assumed that diverted patients will be treated under the length of stay profile of the CCU they are admitted to.
@@
         \node at (3,3.25) {$K_{\RG}$};
-        \node at (1.5,2) {$\lambda_{h}^{(a)}$};
-        \node at (3.5,2) {$\lambda_{h}^{(b)}$};
-        \node at (1.5,.5) {$\lambda_{h}^{(c)}$};
-        \node at (3.5,.5) {$\lambda_{h}^{(d)}$};
+        \node at (1.5,2) {$\lambda_{h}^{(l,l)}$};
+        \node at (3.5,2) {$\lambda_{h}^{(l,h)}$};
+        \node at (1.5,.5) {$\lambda_{h}^{(h,l)}$};
+        \node at (3.5,.5) {$\lambda_{h}^{(h,h)}$};
     \end{tikzpicture}

### 2014-12-09 Paper/paper.tex
Have updated graph for new labelling of regions

@@
         % On Row:
-        \draw (aa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ab);
+        \draw (aa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ab);
         \draw (aa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ab);
 
-        \draw (ab) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ac);
+        \draw (ab) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ac);
         \draw (ab) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (ac);
 
-        \draw (ac) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisa1);
+        \draw (ac) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisa1);
         \draw (ac) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisa1);
 
-        \draw (ellipsisa1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ak);
+        \draw (ellipsisa1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ak);
         \draw (ellipsisa1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (ak);
 
-        \draw (ak) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisa2);
+        \draw (ak) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (ellipsisa2);
         \draw (ak) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG}+1)\mu_{\RG}$} (ellipsisa2);
 
-        \draw (ellipsisa2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (az);
+        \draw (ellipsisa2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (az);
         \draw (ellipsisa2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (az);
@@
         % On Row:
-        \draw (ba) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bb);
+        \draw (ba) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (bb);
         \draw (ba) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bb);
 
-        \draw (bb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bc);
+        \draw (bb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (bc);
         \draw (bb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (bc);
 
-        \draw (bc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisb1);
+        \draw (bc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisb1);
         \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisb1);
 
-        \draw (ellipsisb1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bk);
+        \draw (ellipsisb1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (bk);
         \draw (ellipsisb1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (bk);
 
-        \draw (bk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisb2);
+        \draw (bk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (ellipsisb2);
         \draw (bk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisb2);
 
-        \draw (ellipsisb2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (bz);
+        \draw (ellipsisb2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (bz);
         \draw (ellipsisb2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (bz);
         % With previous row:
-        \draw (aa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ba);
+        \draw (aa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ba);
         \draw (aa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ba);
 
-        \draw (ab) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (bb);
+        \draw (ab) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (bb);
         \draw (ab) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bb);
 
-        \draw (ac) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (bc);
+        \draw (ac) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (bc);
         \draw (ac) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bc);
 
-        \draw (ellipsisa1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisb1);
+        \draw (ellipsisa1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ellipsisb1);
         \draw (ellipsisa1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisb1);
 
-        \draw (ak) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (bk);
+        \draw (ak) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (bk);
         \draw (ak) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bk);
 
-        \draw (ellipsisa2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisb2);
+        \draw (ellipsisa2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (ellipsisb2);
         \draw (ellipsisa2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisb2);
 
-        \draw (az) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (bz);
+        \draw (az) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (bz);
         \draw (az) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bz);
@@
         % On Row:
-        \draw (ca) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (cb);
+        \draw (ca) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (cb);
         \draw (ca) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cb);
 
-        \draw (cb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (cc);
+        \draw (cb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (cc);
         \draw (cb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (cc);
 
-        \draw (cc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisc1);
+        \draw (cc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisc1);
         \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisc1);
 
-        \draw (ellipsisc1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ck);
+        \draw (ellipsisc1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ck);
         \draw (ellipsisc1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (ck);
 
-        \draw (ck) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisc2);
+        \draw (ck) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (ellipsisc2);
         \draw (ck) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisc2);
 
-        \draw (ellipsisc2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (cz);
+        \draw (ellipsisc2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (cz);
         \draw (ellipsisc2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (cz);
         % With previous row:
-        \draw (ba) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ca);
+        \draw (ba) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ca);
         \draw (ba) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ca);
 
-        \draw (bb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (cb);
+        \draw (bb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (cb);
         \draw (bb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (cb);
 
-        \draw (bc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (cc);
+        \draw (bc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (cc);
         \draw (bc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (cc);
 
-        \draw (ellipsisb1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisc1);
+        \draw (ellipsisb1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ellipsisc1);
         \draw (ellipsisb1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ellipsisc1);
 
-        \draw (bk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ck);
+        \draw (bk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (ck);
         \draw (bk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ck);
 
-        \draw (ellipsisb2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisc2);
+        \draw (ellipsisb2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (ellipsisc2);
         \draw (ellipsisb2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$2\mu_{\NH}$} (ellipsisc2);
 
-        \draw (bz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (cz);
+        \draw (bz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (cz);
         \draw (bz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cz);
@@
         % On Row:
-        \draw (da) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (db);
+        \draw (da) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (db);
         \draw (da) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (db);
 
-        \draw (db) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (dc);
+        \draw (db) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (dc);
         \draw (db) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (dc);
 
-        \draw (dc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisd1);
+        \draw (dc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisd1);
         \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisd1);
 
-        \draw (ellipsisd1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (dk);
+        \draw (ellipsisd1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (dk);
         \draw (ellipsisd1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (dk);
 
-        \draw (dk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisd2);
+        \draw (dk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (ellipsisd2);
         \draw (dk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisd2);
 
-        \draw (ellipsisd2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (dz);
+        \draw (ellipsisd2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,h)}$} (dz);
         \draw (ellipsisd2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (dz);
         % With previous row:
-        \draw (ca) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (da);
+        \draw (ca) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (da);
         \draw (ca) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (da);
 
-        \draw (cb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (db);
+        \draw (cb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (db);
         \draw (cb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (db);
 
-        \draw (cc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (dc);
+        \draw (cc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (dc);
         \draw (cc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (dc);
 
-        \draw (ellipsisc1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisd1);
+        \draw (ellipsisc1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ellipsisd1);
         \draw (ellipsisc1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (ellipsisd1);
 
-        \draw (ck) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (dk);
+        \draw (ck) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (dk);
         \draw (ck) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (dk);
 
-        \draw (ellipsisc2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisd2);
+        \draw (ellipsisc2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (ellipsisd2);
         \draw (ellipsisc2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$3\mu_{\NH}$} (ellipsisd2);
 
-        \draw (cz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (dz);
+        \draw (cz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (dz);
         \draw (cz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dz);
@@
         % On Row:
-        \draw (ea) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (eb);
+        \draw (ea) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (eb);
         \draw (ea) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (eb);
 
-        \draw (eb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ec);
+        \draw (eb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (ec);
         \draw (eb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (ec);
 
-        \draw (ec) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ellipsise1);
+        \draw (ec) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (ellipsise1);
         \draw (ec) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsise1);
 
-        \draw (ellipsise1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ek);
+        \draw (ellipsise1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (ek);
         \draw (ellipsise1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (ek);
 
-        \draw (ek) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsise2);
+        \draw (ek) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (ellipsise2);
         \draw (ek) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsise2);
 
-        \draw (ellipsise2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ez);
+        \draw (ellipsise2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (ez);
         \draw (ellipsise2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (ez);
         % With previous row:
-        \draw (da) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ea);
+        \draw (da) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ea);
         \draw (da) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (ea);
 
-        \draw (db) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (eb);
+        \draw (db) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (eb);
         \draw (db) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (eb);
 
-        \draw (dc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ec);
+        \draw (dc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ec);
         \draw (dc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (ec);
 
-        \draw (ellipsisd1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsise1);
+        \draw (ellipsisd1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,l)}$} (ellipsise1);
         \draw (ellipsisd1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (ellipsise1);
 
-        \draw (dk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ek);
+        \draw (dk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (ek);
         \draw (dk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (ek);
 
-        \draw (ellipsisd2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsise2);
+        \draw (ellipsisd2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (ellipsise2);
         \draw (ellipsisd2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (ellipsise2);
 
-        \draw (dz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ez);
+        \draw (dz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(l,h)}$} (ez);
         \draw (dz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$K_{\NH}\mu_{\NH}$} (ez);
@@
         % On Row:
-        \draw (fa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fb);
+        \draw (fa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (fb);
         \draw (fa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fb);
 
-        \draw (fb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fc);
+        \draw (fb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (fc);
         \draw (fb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (fc);
 
-        \draw (fc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ellipsisf1);
+        \draw (fc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (ellipsisf1);
         \draw (fc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisf1);
 
-        \draw (ellipsisf1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fk);
+        \draw (ellipsisf1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (fk);
         \draw (ellipsisf1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (fk);
 
-        \draw (fk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisf2);
+        \draw (fk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (ellipsisf2);
         \draw (fk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisf2);
 
-        \draw (ellipsisf2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (fz);
+        \draw (ellipsisf2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (fz);
         \draw (ellipsisf2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (fz);
         % With previous row:
-        \draw (ea) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fa);
+        \draw (ea) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(h,l)}$} (fa);
         \draw (ea) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH}+1)\mu_{\NH}$} (fa);
 
-        \draw (eb) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(c)}$} (fb);
+        \draw (eb) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(h,l)}$} (fb);
         \draw (eb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH} + 1)\mu_{\NH}$} (fb);
 
-        \draw (ec) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(c)}$} (fc);
+        \draw (ec) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(h,l)}$} (fc);
         \draw (ec) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH} + 1)\mu_{\NH}$} (fc);
 
-        \draw (ellipsise1) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(c)}$} (ellipsisf1);
+        \draw (ellipsise1) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(h,l)}$} (ellipsisf1);
         \draw (ellipsise1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH} + 1)\mu_{\NH}$} (ellipsisf1);
 
-        \draw (ek) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(d)}$} (fk);
+        \draw (ek) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(h,h)}$} (fk);
         \draw (ek) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH} + 1)\mu_{\NH}$} (fk);
 
-        \draw (ellipsise2) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(d)}$} (ellipsisf2);
+        \draw (ellipsise2) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(h,h)}$} (ellipsisf2);
         \draw (ellipsise2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH} + 1)\mu_{\NH}$} (ellipsisf2);
 
-        \draw (ez) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(d)}$} (fz);
+        \draw (ez) edge[out=-125,in=125,->,thick] node [right] {\tiny$\lambda_{\NH}^{(h,h)}$} (fz);
         \draw (ez) edge[out=-55,in=55,<-,thick] node [right] {\tiny$(K_{\NH}+1)\mu_{\NH}$} (fz);
@@
         % On Row:
-        \draw (za) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zb);
+        \draw (za) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (zb);
         \draw (za) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zb);
 
-        \draw (zb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zc);
+        \draw (zb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (zc);
         \draw (zb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$2\mu_{\RG}$} (zc);
 
-        \draw (zc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisz1);
+        \draw (zc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (ellipsisz1);
         \draw (zc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisz1);
 
-        \draw (ellipsisz1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zk);
+        \draw (ellipsisz1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (zk);
         \draw (ellipsisz1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$K_{\RG}\mu_{\RG}$} (zk);
 
-        \draw (zk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisz2);
+        \draw (zk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (ellipsisz2);
         \draw (zk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$(K_{\RG} + 1)\mu_{\RG}$} (ellipsisz2);
 
-        \draw (ellipsisz2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zz);
+        \draw (ellipsisz2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (zz);
         \draw (ellipsisz2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$c_{\RG}\mu_{\RG}$} (zz);
         % With previous row:
-        \draw (fa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (za);
+        \draw (fa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(h,l)}$} (za);
         \draw (fa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (za);
 
-        \draw (fb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (zb);
+        \draw (fb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(h,l)}$} (zb);
         \draw (fb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (zb);
 
-        \draw (fc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (zc);
+        \draw (fc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(h,l)}$} (zc);
         \draw (fc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (zc);
 
-        \draw (ellipsisf1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (ellipsisz1);
+        \draw (ellipsisf1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(h,l)}$} (ellipsisz1);
         \draw (ellipsisf1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (ellipsisz1);
 
-        \draw (fk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (zk);
+        \draw (fk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(h,h)}$} (zk);
         \draw (fk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (zk);
 
-        \draw (ellipsisf2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (ellipsisz2);
+        \draw (ellipsisf2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(h,h)}$} (ellipsisz2);
         \draw (ellipsisf2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (ellipsisz2);
 
-        \draw (fz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (zz);
+        \draw (fz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(h,h)}$} (zz);
         \draw (fz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$c_{\NH}\mu_{\NH}$} (zz);

### 2014-12-09 Paper/paper.tex
I believe I have updated the labels on everything

@@
  v\mu_{\RG} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,1),\\
- \lambda_{NH}^{(a)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0)  \text{ and  } u_i < K_{\NH}  \text{ and  } v_i < K_{\RG},\\
- \lambda_{RG}^{(a)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1)  \text{ and  } u_i < K_{\NH}  \text{ and  } v_i < K_{\RG},\\
-\lambda_{NH}^{(b)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i < K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
-\lambda_{RG}^{(b)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i < K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
-\lambda_{NH}^{(c)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i < K_{\RG},\\
-\lambda_{RG}^{(c)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i < K_{\RG},\\
-\lambda_{NH}^{(d)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
-\lambda_{RG}^{(d)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
+ \lambda_{NH}^{(l,l)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0)  \text{ and  } u_i < K_{\NH}  \text{ and  } v_i < K_{\RG},\\
+ \lambda_{RG}^{(l,l)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1)  \text{ and  } u_i < K_{\NH}  \text{ and  } v_i < K_{\RG},\\
+\lambda_{NH}^{(l,h)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i < K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
+\lambda_{RG}^{(l,h)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i < K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
+\lambda_{NH}^{(h,l)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i < K_{\RG},\\
+\lambda_{RG}^{(h,l)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i < K_{\RG},\\
+\lambda_{NH}^{(h,h)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(-1,0) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
+\lambda_{RG}^{(h,h)} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,-1) \text{ and  } u_i \geq K_{\NH}  \text{ and  } v_i \geq K_{\RG},\\
 0 & \text{ otherwise}.
@@
 
-For $c_{\NH}=8$, $c_{\RG}=16$, $\lambda_{\NH}=(\lambda_{\NH}^{(a)},\lambda_{\NH}^{(b)},\lambda_{\NH}^{(c)},\lambda_{\NH}^{(d)})=(1.5,3.74,0,0)$, $\lambda_{\RG}=(\lambda_{\RG}^{(a)},\lambda_{\RG}^{(b)},\lambda_{\RG}^{(c)},\lambda_{\RG}^{(d)})=(2.24,0,3.74,0)$ and $(K_{\NH},K_{\RG})=(6,12)$, the steady state probabilities for each CCU are given in Figure \ref{steady_state_probs}.
+For $c_{\NH}=8$, $c_{\RG}=16$, $\lambda_{\NH}=(\lambda_{\NH}^{(l,l)},\lambda_{\NH}^{(l,h)},\lambda_{\NH}^{(h,l)},\lambda_{\NH}^{(h,h)})=(1.5,3.74,0,0)$, $\lambda_{\RG}=(\lambda_{\RG}^{(l,l)},\lambda_{\RG}^{(l,h)},\lambda_{\RG}^{(h,l)},\lambda_{\RG}^{(h,h)})=(2.24,0,3.74,0)$ and $(K_{\NH},K_{\RG})=(6,12)$, the steady state probabilities for each CCU are given in Figure \ref{steady_state_probs}.
 
@@
 
-\item If $\lambda_{\NH}^{(a)}\leq \lambda_{\NH}^{(b)}$ and $\lambda_{\NH}^{(c)}\leq \lambda_{\NH}^{(d)}$ then $f_{\NH}(k)$ is a non-decreasing function in $k$.
-\item If $\lambda_{\RG}^{(a)}\leq \lambda_{\RG}^{(c)}$ and $\lambda_{\RG}^{(b)}\leq \lambda_{\RG}^{(d)}$ then $f_{\RG}(k)$ is a non-decreasing function in $k$.
+\item If $\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ and $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)}$ then $f_{\NH}(k)$ is a non-decreasing function in $k$.
+\item If $\lambda_{\RG}^{(l,l)}\leq \lambda_{\RG}^{(h,l)}$ and $\lambda_{\RG}^{(l,h)}\leq \lambda_{\RG}^{(h,h)}$ then $f_{\RG}(k)$ is a non-decreasing function in $k$.
 
@@
 
-If $\lambda_{\NH}^{(a)}\leq \lambda_{\NH}^{(b)}$ and $\lambda_{\NH}^{(c)}\leq \lambda_{\NH}^{(d)}$, for given $K_{\NH}$: then as $K_{\RG}$ increases, the arrival rate at NH is non-increasing,
+If $\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ and $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)}$, for given $K_{\NH}$: then as $K_{\RG}$ increases, the arrival rate at NH is non-increasing,
 Similarly, for given $K_{{\RG}}$, as $K_{\NH}$ increases the arrival rate at RG is non-decreasing.

### 2014-12-09 Paper/paper.tex
Update last sentence of abstract

@@
 
-The effect of target policies is investigated justifying the use of these to align the interests of individual hospitals and social welfare.
+In the UK a variety of utilisation targets are often discussed: aiming to ensure that wards/hospitals operate at a given utilisation value.
+The effect of these target policies is investigated justifying their use to align the interests of individual hospitals and social welfare.
 In particular, we identify the lowest value of a utilisation target that aligns these.

### 2014-12-09 Paper/paper.tex
Clarifying use of pure strategies

@@
 This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close as possible to a certain target.
-As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABUHB, long term threshold policies are a realistic consideration.
+As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, which guarantee the existence of equilibria in mixed strategies.
+Based on discussions with ABUHB, long term threshold policies are a realistic consideration and so a pure strategy space is used.
 

### 2014-12-10 Paper/paper.tex
Have added image with both plots on together
Have removed the indexing of the states - this was not needed

@@
 
-In total there are $(c_{\NH}+1)\times(c_{\RG}+1)$ states and they are indexed lexicographically: $(0,0), (0,1), (0,2)$, etc.
-In general, state $(u,v)$ is the $s(u,v)th$ state where $s(u,v)=u(c_{\RG}+1)+(v+1)$.
+In total there are $(c_{\NH}+1)\times(c_{\RG}+1)$ states and they are indexed lexicographically: $(0,0), (0,1), (0,2), \dots$.
 
@@
 \begin{figure}[!htbp]
-$$\begin{array}{cc}
-\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_NH.pdf}&
-\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_RG.pdf}
-\end{array}$$
+    \begin{center}
+        \includegraphics[width=.7\textwidth]{./Images/best_responses_ex_for_proof.pdf}
+    \end{center}
     \caption{Plots of $f_{\NH}(K_{\RG})$ and $f_{\RG}(K_{\NH})$}\label{exampleforproof}

### 2014-12-15 Paper/paper.tex
Changing equation indexing

@@
 
-The stochastic transition rate matrix $Q=Q(c_{NH},c_{RG})$ of the continuous-time Markov chain \cite{Stewart2009} has entries $q_{ij}$ which is the rate at which a transition from state $i$ to state $j$ occurs.
+The stochastic transition rate matrix $Q=Q(c_{NH},c_{RG})$ of the continuous-time Markov chain \cite{Stewart2009} has entries $q_{ij}=q_{(u_i,v_i),(u_j,v_j)}$ which is the rate at which a transition from state $i$ to state $j$ occurs.
 The transition rates are given by:
@@
 \begin{equation}
-q_{ij}=\begin{cases} u\mu_{\NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(1,0),\\
+q_{(u_i,v_i),(u_j,v_j)}=\begin{cases} u\mu_{\NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(1,0),\\
  v\mu_{\RG} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,1),\\
@@
 \begin{equation}
-q_{ij}=\begin{cases} u_i\mu_{NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(1,0),\\
+q_{(u_i,v_i),(u_j,v_j)}=\begin{cases} u_i\mu_{NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(1,0),\\
  v_i\mu_{RG} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,1),\\
@@
 \midrule
--0.9&1.0&1.0&1.0&1.0&1.0&1.0&1.0&1.0\\
--0.61&1.64&1.04&1.0&1.0&1.0&1.0&1.0&1.0\\
--0.33&3.27&1.66&1.22&1.0&1.0&1.0&1.0&1.0\\
--0.03&4.43&2.55&1.64&1.34&1.06&1.0&1.0&1.0\\
-0.26&5.23&2.99&2.1&1.51&1.28&1.09&1.0&1.0\\
-0.55&7.34&3.21&2.25&1.74&1.34&1.16&1.0&1.0\\
-0.84&7.6&3.81&2.32&1.79&1.46&1.17&1.03&1.0\\
-1.13&7.73&3.88&2.36&1.82&1.48&1.25&1.04&1.0\\
-1.41&7.81&3.91&2.61&1.97&1.58&1.26&1.09&1.0\\
-1.7&7.86&3.94&2.63&1.98&1.58&1.32&1.14&1.0\\
-1.99&7.89&3.95&2.64&1.98&1.59&1.33&1.14&1.0\\
+-0.9  & 1.0  & 1.0  & 1.0  & 1.0  & 1.0  & 1.0  & 1.0  & 1.0\\
+-0.61 & 1.64 & 1.04 & 1.0  & 1.0  & 1.0  & 1.0  & 1.0  & 1.0\\
+-0.33 & 3.27 & 1.66 & 1.22 & 1.0  & 1.0  & 1.0  & 1.0  & 1.0\\
+-0.03 & 4.43 & 2.55 & 1.64 & 1.34 & 1.06 & 1.0  & 1.0  & 1.0\\
+0.26  & 5.23 & 2.99 & 2.1  & 1.51 & 1.28 & 1.09 & 1.0  & 1.0\\
+0.55  & 7.34 & 3.21 & 2.25 & 1.74 & 1.34 & 1.16 & 1.0  & 1.0\\
+0.84  & 7.6  & 3.81 & 2.32 & 1.79 & 1.46 & 1.17 & 1.03 & 1.0\\
+1.13  & 7.73 & 3.88 & 2.36 & 1.82 & 1.48 & 1.25 & 1.04 & 1.0\\
+1.41  & 7.81 & 3.91 & 2.61 & 1.97 & 1.58 & 1.26 & 1.09 & 1.0\\
+1.7   & 7.86 & 3.94 & 2.63 & 1.98 & 1.58 & 1.32 & 1.14 & 1.0\\
+1.99  & 7.89 & 3.95 & 2.64 & 1.98 & 1.59 & 1.33 & 1.14 & 1.0\\
 \bottomrule
@@
 \begin{equation}
-q_{ij}=\begin{cases} u_i\mu_{NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(1,0),\\
+q_{(u_i,v_i), (u_j, v_j)}=\begin{cases} u_i\mu_{NH} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(1,0),\\
  v_i\mu_{RG} & \text{ if  } (u_i,v_i)-(u_j,v_j)=(0,1),\\

### 2014-12-15 Paper/paper.tex
Re wording use of robust

@@
 An immediate alignment of interests can be obtained by setting $t=1$.
-This however would not be in the interest of the hospital (nor necessarily in the interests of patients) as it would imply aiming to run at 100\% utilisation which would not make for a robust system.
+This however would not be in the interest of the hospital (nor necessarily in the interests of patients) as it would imply aiming to run at 100\% utilisation which imply a large quantity of patients being rejected.
 \textbf{A sensible value of $t$ is the lowest value of $t$ that ensures a low PoA}.

### 2014-12-15 Paper/paper.tex
Changing link to code to SMC

@@
 The code used in this work can be found here: \url{https://github.com/drvinceknight/Measuring_the_price_of_anarchy_in_ccu_interactions}.
-The graphics for this paper were obtained using \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://sage.maths.cf.ac.uk/home/pub/122/}.
+The graphics for this paper were obtained using \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://cloud.sagemath.com/projects/c293aefd-1fdf-4b9c-95f4-75bb77035e42/files/MeasuringThePriceOfAnarchyInCCUInteractions.sagews}.
 

### 2014-12-15 Paper/paper.tex
Adding a sentence about the PoA being a theoretical lower bound
Have added a sentence justifying why we choose worst case equilibria

@@
 
-The function $f_h$ is well defined as it maximises a continuous function over a finite discrete set (in case of multiple values that minimize $U_h$, it is assumed that $f_h$ returns the lowest such value).
+The function $f_h$ is well defined as it maximises a continuous function over a finite discrete set.
+In case of multiple values that minimize $U_h$, it is assumed that $f_h$ returns the lowest such value, this is consistent with the PoA being a theoretical upper bound of the effect of uncoordinated behaviour.
 
@@
 The PoA is calculated so as to measure the effect of rational behaviour on overall patient throughput.
+The PoA represents a theoretical lower bound for the potential damages caused by uncoordinated behaviour.
 High PoAs are found in the case of strict diversion which is to be expected as soft diversion implies a certain level of cooperation.

### 2014-12-15 Paper/paper.tex
Have added a sentence justifying why we choose worst case equilibria

@@
 The function $f_h$ is well defined as it maximises a continuous function over a finite discrete set.
-In case of multiple values that minimize $U_h$, it is assumed that $f_h$ returns the lowest such value, this is consistent with the PoA being a theoretical upper bound of the effect of uncoordinated behaviour.
+In case of multiple values that minimize $U_h$, it is assumed that $f_h$ returns the lowest such value, this is consistent with the PoA being a theoretical upper bound of the effect of uncoordinated behaviour \cite{TimRoughgarden}.
 

### 2014-12-15 Paper/paper.tex
Have fixed slight error in proof (still need to refactor proof completely)

@@
 As $K_{\RG}$ increases, the utilisation $U_{\NH}(k^*)$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
-As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $U_{NH}(k^*)=t$ and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
+As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $\left(U_{NH}(k^*)-t\right)^2$ is minimized and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
 Thus, $f_{\NH}(K_{\RG})\geq k^*$ as required.

### 2014-12-16 Paper/paper.tex
Tidying a bit of the intro

@@
 It provides intensive care (treatment and monitoring) for people who are critically ill or are in an unstable condition.
-CCUs face major challenges.
-The first challenge that CCUs have to deal with is shortage of beds.
-On average, 8\% of patients are refused admission to a CCU because the Unit is full \cite{Report}.
+CCUs face major challenges, on average, 8\% of patients are refused admission to a CCU because the Unit is full \cite{Report}.
 The CCU occupancy rates for some hospitals are reportedly very high \cite{Mitchell1995,Smith1995} and a shortage of beds has been identified throughout the UK.
@@
 Patients in CCUs need constant medical support to keep their body functioning.
-Moreover, CCU beds are very expensive and a limited resource; therefore efficient CCU bed management is crucial.
 Many previous researchers have developed queueing models to help manage bed capacities in hospitals \cite{Cooper1974,Dumas1984,Gallivan2011,Gorunescu2002a,Griffiths2012,Harper2002a}.
-Also, a vast amount of literature has been devoted to simulation of CCUs;  \cite{Cahill1999a,Costa2003,Griffiths2004a,Kim1999,Litvak2008,Shahani2008}.
+Also, a vast amount of literature has been devoted to the simulation of CCUs;  \cite{Cahill1999a,Costa2003,Griffiths2004a,Kim1999,Litvak2008,Shahani2008}.
 

### 2014-12-18 Paper/paper.tex
Have added an explenation about state based rates from data
Have added literature

@@
 
-Game theory is the mathematical study of interactive decision making between rational decision makers \cite{Maschler2013}.
-A game is a description of strategic interactions that includes the constraints on the actions that the players can take and on the players' interests.
+The effect of state dependent service rates in healthcare has been well studied in isolated hospitals.
+In \cite{A} an empirical study is undertaken and service rate slow down is identified.
+Furthermore, it is shown that modelling whilst ignoring these state dependent rates leads to errors.
+This effect is further identified in \cite{B,C} where for example the negative effect on patient outcome is revealed.
+In \cite{D,E} this is expanded to consider a variety of admission policies in two CCUs, in particular the effect of rejection (due to too high occupancy) is measured.
+These policies are studied in the setting of a single hospital, and thus, from a game theoretic \cite{Maschler2013} point of view correspond to rational behaviour.
+In practice a simplification of rational strategies is managed by policy makers by setting utilisation targets that ensure that hospitals do not run at a level likely to have a high rejection rate (example of these can be seen \cite{Bevan2006, url1, url2}).
+
+The aim of this paper is to further investigate the effect of rational policies employed by Hospitals.
+In particular, the aim is to place this in a game theoretic setting so as to identify whether or not target policies result in uncoordinated behaviour that is damaging for patients.
 
@@
 \end{table}
+
+Note that the inter-arrival and service rates are not state dependent.
+These will serve as a base level for the state dependent rates used throughout the game theoretic models.
 

### 2014-12-18 Paper/paper.tex
Adding the fact that LoS follows patient
Adding bibtex files

@@
 The effect of state dependent service rates in healthcare has been well studied in isolated hospitals.
-In \cite{A} an empirical study is undertaken and service rate slow down is identified.
+In \cite{batt2012doctors} an empirical study is undertaken and service rate slow down is identified.
 Furthermore, it is shown that modelling whilst ignoring these state dependent rates leads to errors.
-This effect is further identified in \cite{B,C} where for example the negative effect on patient outcome is revealed.
-In \cite{D,E} this is expanded to consider a variety of admission policies in two CCUs, in particular the effect of rejection (due to too high occupancy) is measured.
+This effect is further identified in \cite{chan2014use, kc2012econometric} where for example the negative effect on patient outcome is revealed.
+In \cite{kim2013icu, shmueli2003optimizing} this is expanded to consider a variety of admission policies in two CCUs, in particular the effect of rejection (due to too high occupancy) is measured.
 These policies are studied in the setting of a single hospital, and thus, from a game theoretic \cite{Maschler2013} point of view correspond to rational behaviour.
-In practice a simplification of rational strategies is managed by policy makers by setting utilisation targets that ensure that hospitals do not run at a level likely to have a high rejection rate (example of these can be seen \cite{Bevan2006, url1, url2}).
+In practice a simplification of rational strategies is managed by policy makers by setting utilisation targets that ensure that hospitals do not run at a level likely to have a high rejection rate (example of these can be seen in \cite{Bevan2006, NHS2013}).
 
@@
 However, allowing for mixed strategies could also be of interest.
+    \item Patient length of stay is assumed to be dependent on the CCU at which they receive service.
+A further extension of the work would be to use the service rate from original CCU (prior to diversion).
+This would require a Markov chain with a higher dimensional state space.
 \end{itemize}

### 2014-12-20 Paper/paper.tex
Starting to work on writing the theorem

--- 2014-12-18 Paper/paper.tex
@@
 
-\item If $\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ and $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)}$ then $f_{\NH}(k)$ is a non-decreasing function in $k$.
-\item If $\lambda_{\RG}^{(l,l)}\leq \lambda_{\RG}^{(h,l)}$ and $\lambda_{\RG}^{(l,h)}\leq \lambda_{\RG}^{(h,h)}$ then $f_{\RG}(k)$ is a non-decreasing function in $k$.
+\item If $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)},\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ then $f_{\NH}(k)$ is a non-decreasing function in $k$.
+\item If $\lambda_{\RG}^{(l,h)}\leq \lambda_{\RG}^{(h,h)},\lambda_{\RG}^{(l,l)}\leq \lambda_{\RG}^{(h,l)}$ then $f_{\RG}(k)$ is a non-decreasing function in $k$.
 

### 2014-12-21 Paper/paper.tex
Getting rid of todo list
Have image for effect of KRG

@@
 \usetikzlibrary{backgrounds}
-
-\usepackage{todonotes}
 
@@
 \newcommand{\RG}{\text{RG}}
-\newcommand{\todoVK}[1]{\todo[color=blue!20]{#1}}
 
@@
 
-If $\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ and $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)}$, for given $K_{\NH}$: then as $K_{\RG}$ increases, the arrival rate at NH is non-increasing,
-Similarly, for given $K_{{\RG}}$, as $K_{\NH}$ increases the arrival rate at RG is non-decreasing.
-
-Using the above and the previous observation this implies:
-
-\begin{itemize}
-    \item The function $U_{\NH}=U_{\NH}(K_{\RG})$ is non-increasing;
-    \item The function $U_{\NH}=U_{\NH}(K_{\NH})$ is non-decreasing.
-\end{itemize}
-
-A graphical proof of the lemma is then shown in Figure \ref{proof}.
+Let \(\bar \lambda_{\NH} = \bar \lambda_{\NH}(K_{\RG})\) be the effective arrival rate at NH.
+If \(\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)},\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}\) then this implies that \(\bar \lambda_{\NH}(K_{\RG}) \geq \bar \lambda_{\NH}(K_{\RG} + 1)\) as shown in Figure \ref{fig:effect_of_KRG_on_arrival_rate}.
 
@@
     \begin{center}
-\includegraphics[width=.7\textwidth]{./Images/proof.pdf}
-\end{center}
-\caption{Graphical proof of the fact that $f_{\NH}(K_{\RG})<f_{\NH}(K_{\RG}+1)$}\label{proof}
-\end{figure}
-
-Let $k^*=f_{NH}(K_{\RG})$ for a given $K_{\RG}$.
-As $K_{\RG}$ increases, the utilisation $U_{\NH}(k^*)$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
-As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $\left(U_{NH}(k^*)-t\right)^2$ is minimized and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
-Thus, $f_{\NH}(K_{\RG})\geq k^*$ as required.
+        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
+            \foreach \x in {0,8}
+            {\coordinate (origin) at (\x,0);
+                % Coordinate system
+                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\(\bar\lambda_{K_{\RG}}\)};
+                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {Occupancy at RG};
+                % lambda
+                \draw ($(origin) + (0,2)$) -- ($(origin) + (2,2)$) -- ($(origin) + (2,4)$) -- ($(origin) + (5,4)$);
+                \node at ($(origin) + (1,2.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
+                \node at ($(origin) + (3.5,4.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
+                % Effect of KRG
+                \draw [dashed] ($(origin) + (0,2)$) -- ($(origin) + (4,2)$) -- ($(origin) + (4,4)$);
+                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,2)$);
+                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,2)$);
+                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
+                \node at ($(origin) + (2,0)$) [below] {\(K_{\RG}\)};
+                \node at ($(origin) + (4,0)$) [below] {\(K_{\RG}+1\)};
+            };
+        \end{tikzpicture}
+    \end{center}
+    \caption{The effect of \(K_{\RG}\) on \(\bar \lambda\).}\label{fig:effect_of_KRG_on_arrival_rate}
+\end{figure}
+
+Based on the previous observation this in turn implies:
+
+\begin{equation}
+    U_{\NH}(K_{\RG}) = U_{\NH}(\bar \lambda_{\RG}(K_{\RG}) \geq U_{\NH}(\bar \lambda_{\RG}(K_{\RG}+1)) = U_{\NH}(K_{\RG}+1)
+    \label{equ:UNH_as_a_function_of_KRG}
+\end{equation}
+
+In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}), we have:
+
+\begin{equation}
+    U_{\NH}(K_{\NH}) = U_{\NH}(\bar \lambda_{\NH}(K_{\NH}) \leq U_{\NH}(\bar \lambda_{\NH}(K_{\NH}+1)) = U_{\NH}(K_{\NH}+1)
+    \label{equ:UNH_as_a_function_of_KNH}
+\end{equation}
+
+\begin{figure}[!hbtp]
+    \begin{center}
+        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
+            \foreach \x in {0,8}
+            {\coordinate (origin) at (\x,0);
+                % Coordinate system
+                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\(\bar\lambda_{K_{\NH}}\)};
+                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {Occupancy at NH};
+                % lambda
+                \draw ($(origin) + (0,4)$) -- ($(origin) + (2,4)$) -- ($(origin) + (2,2)$) -- ($(origin) + (5,2)$);
+                \node at ($(origin) + (1,3.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
+                \node at ($(origin) + (3.5,1.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
+                % Effect of KNH
+                \draw [dashed] ($(origin) + (0,4)$) -- ($(origin) + (4,4)$) -- ($(origin) + (4,2)$);
+                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,4)$);
+                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,4)$);
+                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
+                \node at ($(origin) + (2,0)$) [below] {\(K_{\NH}\)};
+                \node at ($(origin) + (4,0)$) [below] {\(K_{\NH}+1\)};
+            };
+        \end{tikzpicture}
+    \end{center}
+    \caption{The effect of \(K_{\NH}\) on \(\bar \lambda\).}\label{fig:effect_of_KNH_on_arrival_rate}
+\end{figure}
+
+%If $\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ and $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)}$, for given $K_{\NH}$: then as $K_{\RG}$ increases, the arrival rate at NH is non-increasing,
+%Similarly, for given $K_{{\RG}}$, as $K_{\NH}$ increases the arrival rate at RG is non-decreasing.
+
+%Using the above and the previous observation this implies:
+
+%\begin{itemize}
+    %\item The function $U_{\NH}=U_{\NH}(K_{\RG})$ is non-increasing;
+    %\item The function $U_{\NH}=U_{\NH}(K_{\NH})$ is non-decreasing.
+%\end{itemize}
+
+%A graphical proof of the lemma is then shown in Figure \ref{proof}.
+
+%\begin{figure}[!hbtp]
+%\begin{center}
+%\includegraphics[width=.7\textwidth]{./Images/proof.pdf}
+%\end{center}
+%\caption{Graphical proof of the fact that $f_{\NH}(K_{\RG})<f_{\NH}(K_{\RG}+1)$}\label{proof}
+%\end{figure}
+
+%Let $k^*=f_{NH}(K_{\RG})$ for a given $K_{\RG}$.
+%As $K_{\RG}$ increases, the utilisation $U_{\NH}(k^*)$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
+%As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $\left(U_{NH}(k^*)-t\right)^2$ is minimized and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
+%Thus, $f_{\NH}(K_{\RG})\geq k^*$ as required.
 \end{proof}

### 2014-12-21 Paper/paper.tex
Have diagram of inequalities

@@
 
-In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}), we have:
+In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}), this gives:
 
@@
         \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
-            \foreach \x in {0,8}
+            \foreach \x in {0,9}
             {\coordinate (origin) at (\x,0);
@@
 
+Using (\ref{equ:UNH_as_a_function_of_KRG}) and (\ref{equ:UNH_as_a_function_of_KNH}) the general inequalities associated with \(U_{\NH}(K_{\NH}, K_{\RG})\) are summarised in Figure \ref{fig:variation_of_UNH}.
+
+\begin{figure}[!hbtp]
+    \begin{center}
+        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
+            % Coordinate system
+            \draw [very thick, ->] (0,0) -- (0,6) node[anchor=south east] {\(K_{\RG}\)};
+            \draw [very thick, ->] (0,0) -- (7,0) node[anchor=north west] {\(K_{\NH}\)};
+
+            % Points
+            \foreach \x in {1,2,3,4,5,6}
+                {
+                \foreach \y in {1,2,3,4,5}
+                    {
+                        \node at (\x, \y) {\textbullet};
+                    };
+                };
+
+            % Negative region
+            \draw[rounded corners, dashed, thick] (.5,5.5) --
+              ++(5, 0) -- ++(0,-1) -- ++(-1, 0)  -- ++(0,-1) -- ++(-1,0) --
+              ++(0, -2) -- ++(-2,0) -- ++(-1, 0) -- cycle;
+            \draw [<-, thick] (3.25,4.75) -- (4.75,6) node[anchor= south west] {\(U_{\NH}\leq t\)};
+
+            % Vertical inequalities
+            \foreach \x in {1,2,3,4,5,6}
+                {
+                \foreach \y in {1.5,2.5,3.5,4.5}
+                    {
+                        \node at (\x, \y) [blue!100, rotate=90] {\textbf{\(\geq\)}};
+                    };
+                };
+
+            % Horizontal inequalities
+            \foreach \x in {1.5,2.5,3.5,4.5,5.5}
+                {
+                \foreach \y in {1,2,3,4,5}
+                    {
+                        \node at (\x, \y) [red!100] {\textbf{\(\leq\)}};
+                    };
+                };
+        \end{tikzpicture}
+    \end{center}
+    \caption{Values \(U_{\NH}\).}\label{fig:variation_of_UNH}
+\end{figure}
+
+As \(\U_{\NH}\) increases from the lowest value (top left in Figure  \ref{fig:variation_of_UNH}) to the highest (bottom right in Figure \ref{fig:variation_of_UNH}) the value of \(U_{\NH}-t\) will change sign (from negative to positive).
+
 %If $\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ and $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)}$, for given $K_{\NH}$: then as $K_{\RG}$ increases, the arrival rate at NH is non-increasing,

### 2014-12-21 Paper/paper.tex
Have re written the proof - needs to be checked

@@
 \newcommand{\RG}{\text{RG}}
+\DeclareMathOperator*{\argmin}{arg\!min}
+\DeclareMathOperator*{\argmax}{arg\!max}
 
@@
 
-As \(\U_{\NH}\) increases from the lowest value (top left in Figure  \ref{fig:variation_of_UNH}) to the highest (bottom right in Figure \ref{fig:variation_of_UNH}) the value of \(U_{\NH}-t\) will change sign (from negative to positive).
-
-%If $\lambda_{\NH}^{(l,l)}\leq \lambda_{\NH}^{(l,h)}$ and $\lambda_{\NH}^{(h,l)}\leq \lambda_{\NH}^{(h,h)}$, for given $K_{\NH}$: then as $K_{\RG}$ increases, the arrival rate at NH is non-increasing,
-%Similarly, for given $K_{{\RG}}$, as $K_{\NH}$ increases the arrival rate at RG is non-decreasing.
-
-%Using the above and the previous observation this implies:
-
-%\begin{itemize}
-    %\item The function $U_{\NH}=U_{\NH}(K_{\RG})$ is non-increasing;
-    %\item The function $U_{\NH}=U_{\NH}(K_{\NH})$ is non-decreasing.
-%\end{itemize}
-
-%A graphical proof of the lemma is then shown in Figure \ref{proof}.
-
-%\begin{figure}[!hbtp]
-%\begin{center}
-%\includegraphics[width=.7\textwidth]{./Images/proof.pdf}
-%\end{center}
-%\caption{Graphical proof of the fact that $f_{\NH}(K_{\RG})<f_{\NH}(K_{\RG}+1)$}\label{proof}
-%\end{figure}
-
-%Let $k^*=f_{NH}(K_{\RG})$ for a given $K_{\RG}$.
-%As $K_{\RG}$ increases, the utilisation $U_{\NH}(k^*)$ will be non-increasing, but it will also be non-increasing for all $k<k^*$.
-%As $K_{RG}$ increases $\left(U_{NH}(k^*)-t\right)^2$ decreases until $\left(U_{NH}(k^*)-t\right)^2$ is minimized and then increases, however $\left(U_{NH}(k^*+1)-t\right)^2$ will continue to decrease.
-%Thus, $f_{\NH}(K_{\RG})\geq k^*$ as required.
+As \(U_{\NH}\) increases from the lowest value (top left in Figure  \ref{fig:variation_of_UNH}) to the highest (bottom right in Figure \ref{fig:variation_of_UNH}) the value of \(U_{\NH}-t\) will change sign (from negative to positive).
+Let \(f^+(K_{\RG})=\argmin_{\{0\leq k \leq C_{\NH}|U_{\NH}(k, K_{\RG})\geq t\}}(U_{\NH}(k, K_{\RG}))\) and \(f^-(K_{\RG})=\argmax_{\{0\leq k \leq C_{\NH}|U_{\NH}(k, K_{\RG})\leq t\}}(U_{\NH}(k, K_{\RG}))\).
+So that \(f^{\pm}({K_{\RG}})\) is the value of \(K_{\NH}\) that gives the value of \(U_{\NH}(K_{\NH}, K_{\RG})\) that is closest to \(t\) such that:
+
+\begin{equation}
+U_{\NH}(f^-(K_{\RG}),K_{\RG})\leq t \leq U_{\NH}(f^+(K_{\RG}),K_{\RG})
+\end{equation}
+
+This immediately (from Figure \ref{fig:variation_of_UNH}) gives:
+
+\begin{equation}
+f^{\pm}(K_{\RG}) \leq f^{\pm}(K_{\RG} + 1)
+\end{equation}
+
+Let:
+
+\begin{equation}
+S(K_{\RG}) = \{f^{+}(K_{\RG})\}\cup\{f^{-}(K_{\RG})\}
+\end{equation}
+
+Thus, \(f(K_{\RG})\in S(K_{\RG})\).
+Note that from (\ref{equ:UNH_as_a_function_of_KNH}) have \(\max S(K_{\RG})=f^{+}(K_{\RG})\) and \(\min S(K_{\RG})=f^{+}(K_{\RG})\).
+In essence \(S(K_{\RG})\) corresponds to the set of two values of \(K_{\NH}\) that give a utilisation just below and just above \(t\).
+
+There are two possibilities that will now be considered:
+
+\begin{enumerate}
+    \item \(S(K_{\RG})\ne S(K_{\RG})\)
+    \item \(S(K_{\RG})= S(K_{\RG})\)
+\end{enumerate}
+
+If \(S(K_{\RG})\ne S(K_{\RG})\) this implies that \(f^{+}(K_{\RG})\leq f^{-}(K_{\RG})\) which gives:
+
+\begin{equation}
+    f(K_{\RG}) \leq f^{+}(K_{\RG}) \leq f^{-}(K_{\RG}+1) \leq f(K_{\RG}+1)
+\end{equation}
+
+which is the required result.
+
+To finish the proof consider \(S(K_{\RG})= S(K_{\RG})\) and assume:
+
+\begin{equation}
+    f(K_{RG})=f^{+}(K_{\RG}) \text{ but } f(K_{RG}+1)=f^{-}(K_{\RG}+1)
+\end{equation}
+
+which contradicts the required result.
+
+For simplicity of notation let:
+
+\[a^{\pm}=(f^{\pm}(K_{\RG}), K{\RG})\text{ and }b^{\pm}=(f^{\pm}(K_{\RG}+1), K{\RG}+1)\]
+
+Recalling equations (\ref{equ:UNH_as_a_function_of_KRG}-\ref{equ:UNH_as_a_function_of_KNH}) and Figure \ref{fig:variation_of_UNH} have:
+
+\begin{align}
+U_{\NH}(b^-)&\leq U_{\NH}(a^-)\\
+U_{\NH}(b^+)&\leq U_{\NH}(a^+)
+\end{align}
+
+which implies:
+
+\begin{equation}
+U_{\NH}(b^-) +  U_{\NH}(b^+) \leq U_{\NH}(a^-) + U_{\NH}(a^-)
+\label{equ:true_inequality_for_a_and_b}
+\end{equation}
+
+As \(f(K_{\RG})=f^{+}(K_{\RG})\) (this is the assumption made):
+
+\begin{equation}
+|U_{\NH}(a^+)-t|<|U_{\NH}(a^-)-t|
+\end{equation}
+
+this implies:
+
+\begin{equation}
+U_{\NH}(a^+)+U_{\NH}(a^-)<2t
+\label{equ:contradiction_part_1}
+\end{equation}
+
+Similarly as \(f(K_{\RG}+1)=f^{-}(K_{\RG}+1)\) (this is the assumption made):
+
+\begin{equation}
+|U_{\NH}(b^+)-t|>|U_{\NH}(b^-)-t|
+\end{equation}
+
+this implies:
+
+\begin{equation}
+U_{\NH}(b^+)+U_{\NH}(b^-)>2t
+\label{equ:contradiction_part_2}
+\end{equation}
+
+Combining (\ref{equ:contradiction_part_1}) and (\ref{equ:contradiction_part_2}) contradicts (\ref{equ:true_inequality_for_a_and_b}) implying that the original assumption was incorrect thus proving the required result.
 \end{proof}

### 2014-12-22 Paper/paper.tex
Have updated proof and tweaked intro

@@
 
+The effect of state dependent service rates in healthcare has been well studied in isolated hospitals.
+In \cite{batt2012doctors} an empirical study is undertaken and service rate slow down is identified.
+Furthermore, it is shown that modelling whilst ignoring these state dependent rates leads to errors.
+This effect is further identified in \cite{chan2014use, kc2012econometric} where for example the negative effect on patient outcome is revealed.
+In \cite{kim2013icu, shmueli2003optimizing} this is expanded to consider a variety of admission policies in two CCUs, in particular the effect of rejection (due to too high occupancy) is measured.
+These policies are studied in the setting of a single hospital, and thus, from a game theoretic \cite{Maschler2013} point of view correspond to rational behaviour.
+In practice a simplification of rational strategies is managed by policy makers by setting utilisation targets that ensure that hospitals do not run at a level likely to have a high rejection rate (example of these can be seen in \cite{Bevan2006, NHS2013}).
+
+The aim of this paper is to further investigate the effect of rational policies employed by Hospitals.
+In particular, the goal is to place this in a game theoretic setting so as to identify whether or not target policies result in uncoordinated behaviour that is damaging for patients.
+
 A Critical Care Unit (CCU), also sometimes referred to as an Intensive Therapy Unit or Intensive Therapy Department, is a special ward that is found in most acute hospitals.
@@
 
-Patients in CCUs need constant medical support to keep their body functioning.
 Many previous researchers have developed queueing models to help manage bed capacities in hospitals \cite{Cooper1974,Dumas1984,Gallivan2011,Gorunescu2002a,Griffiths2012,Harper2002a}.
@@
 After an initial analysis of the data, behavioural aspects became apparent; for example, delaying patients discharge if there was no pressure on CCU beds, or admitting fewer patients if bed occupancy levels were high.
-As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy \cite{Komenda2013}.
+As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy \cite{williams2015mathematical}.
 This state dependent model was applied to both NH and RG separately.
@@
 \end{figure}
-
-The effect of state dependent service rates in healthcare has been well studied in isolated hospitals.
-In \cite{batt2012doctors} an empirical study is undertaken and service rate slow down is identified.
-Furthermore, it is shown that modelling whilst ignoring these state dependent rates leads to errors.
-This effect is further identified in \cite{chan2014use, kc2012econometric} where for example the negative effect on patient outcome is revealed.
-In \cite{kim2013icu, shmueli2003optimizing} this is expanded to consider a variety of admission policies in two CCUs, in particular the effect of rejection (due to too high occupancy) is measured.
-These policies are studied in the setting of a single hospital, and thus, from a game theoretic \cite{Maschler2013} point of view correspond to rational behaviour.
-In practice a simplification of rational strategies is managed by policy makers by setting utilisation targets that ensure that hospitals do not run at a level likely to have a high rejection rate (example of these can be seen in \cite{Bevan2006, NHS2013}).
-
-The aim of this paper is to further investigate the effect of rational policies employed by Hospitals.
-In particular, the aim is to place this in a game theoretic setting so as to identify whether or not target policies result in uncoordinated behaviour that is damaging for patients.
 
@@
 
-Based on the previous observation this in turn implies:
-
-\begin{equation}
-    U_{\NH}(K_{\RG}) = U_{\NH}(\bar \lambda_{\RG}(K_{\RG}) \geq U_{\NH}(\bar \lambda_{\RG}(K_{\RG}+1)) = U_{\NH}(K_{\RG}+1)
+Based on the previous observation this in turn implies: \(U_{\NH}(K_{\RG}) = U_{\NH}(\bar \lambda_{\RG}(K_{\RG}) \geq U_{\NH}(\bar \lambda_{\RG}(K_{\RG}+1)) = U_{\NH}(K_{\RG}+1)\) giving:
+
+\begin{equation}
+    U_{\NH}(K_{\RG}) \geq U_{\NH}(K_{\RG}+1)
     \label{equ:UNH_as_a_function_of_KRG}
@@
 
-In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}), this gives:
-
-\begin{equation}
-    U_{\NH}(K_{\NH}) = U_{\NH}(\bar \lambda_{\NH}(K_{\NH}) \leq U_{\NH}(\bar \lambda_{\NH}(K_{\NH}+1)) = U_{\NH}(K_{\NH}+1)
+In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}), this gives: \(U_{\NH}(K_{\NH}) = U_{\NH}(\bar \lambda_{\NH}(K_{\NH}) \leq U_{\NH}(\bar \lambda_{\NH}(K_{\NH}+1)) = U_{\NH}(K_{\NH}+1)\) giving:
+
+\begin{equation}
+    U_{\NH}(K_{\NH}) \leq U_{\NH}(K_{\NH}+1)
     \label{equ:UNH_as_a_function_of_KNH}
@@
     \end{center}
-    \caption{Values \(U_{\NH}\).}\label{fig:variation_of_UNH}
+    \caption{Values of \(U_{\NH}\) and the corresponding inequalities for varying cutoff thresholds.}\label{fig:variation_of_UNH}
 \end{figure}
@@
 As \(U_{\NH}\) increases from the lowest value (top left in Figure  \ref{fig:variation_of_UNH}) to the highest (bottom right in Figure \ref{fig:variation_of_UNH}) the value of \(U_{\NH}-t\) will change sign (from negative to positive).
-Let \(f^+(K_{\RG})=\argmin_{\{0\leq k \leq C_{\NH}|U_{\NH}(k, K_{\RG})\geq t\}}(U_{\NH}(k, K_{\RG}))\) and \(f^-(K_{\RG})=\argmax_{\{0\leq k \leq C_{\NH}|U_{\NH}(k, K_{\RG})\leq t\}}(U_{\NH}(k, K_{\RG}))\).
-So that \(f^{\pm}({K_{\RG}})\) is the value of \(K_{\NH}\) that gives the value of \(U_{\NH}(K_{\NH}, K_{\RG})\) that is closest to \(t\) such that:
+Let:
+
+\begin{equation}
+f^+(K_{\RG})=\argmin_{\{0\leq k \leq C_{\NH}|U_{\NH}(k, K_{\RG})\geq t\}}(U_{\NH}(k, K_{\RG}))
+\end{equation}
+ and
+
+\begin{equation}
+f^-(K_{\RG})=\argmax_{\{0\leq k \leq C_{\NH}|U_{\NH}(k, K_{\RG})\leq t\}}(U_{\NH}(k, K_{\RG}))
+\end{equation}
+
+Thus, \(f^{\pm}({K_{\RG}})\) is the value of \(K_{\NH}\) that gives the value of \(U_{\NH}(K_{\NH}, K_{\RG})\) that is closest to \(t\) such that:
 
@@
 \begin{equation}
-S(K_{\RG}) = \{f^{+}(K_{\RG})\}\cup\{f^{-}(K_{\RG})\}
+S(K_{\RG}) = \{f^{-}(K_{\RG})\}\cup\{f^{+}(K_{\RG})\}
 \end{equation}
@@
 Thus, \(f(K_{\RG})\in S(K_{\RG})\).
-Note that from (\ref{equ:UNH_as_a_function_of_KNH}) have \(\max S(K_{\RG})=f^{+}(K_{\RG})\) and \(\min S(K_{\RG})=f^{+}(K_{\RG})\).
+Note that from (\ref{equ:UNH_as_a_function_of_KNH}) \(\max (S(K_{\RG}))=f^{+}(K_{\RG})\) and \(\min S(K_{\RG})=f^{+}(K_{\RG})\).
 In essence \(S(K_{\RG})\) corresponds to the set of two values of \(K_{\NH}\) that give a utilisation just below and just above \(t\).
@@
 \begin{enumerate}
-    \item \(S(K_{\RG})\ne S(K_{\RG})\)
-    \item \(S(K_{\RG})= S(K_{\RG})\)
+    \item \(S(K_{\RG})\ne S(K_{\RG}+1)\)
+    \item \(S(K_{\RG})= S(K_{\RG}+1)\)
 \end{enumerate}
 
-If \(S(K_{\RG})\ne S(K_{\RG})\) this implies that \(f^{+}(K_{\RG})\leq f^{-}(K_{\RG})\) which gives:
+If \(S(K_{\RG})\ne S(K_{\RG})\) this implies that \(f^{+}(K_{\RG})\leq f^{-}(K_{\RG}+1)\) which gives:
 
@@
 
-To finish the proof consider \(S(K_{\RG})= S(K_{\RG})\) and assume:
-
-\begin{equation}
-    f(K_{RG})=f^{+}(K_{\RG}) \text{ but } f(K_{RG}+1)=f^{-}(K_{\RG}+1)
-\end{equation}
-
-which contradicts the required result.
+To finish the proof consider \(S(K_{\RG})=S(K_{\RG})\) which is equivalent to \(f^{\pm}(K_{\RG})=f^{\pm}(K_{\RG}+1)\) and assume:
+
+\begin{equation}
+    f(K_{\RG})=f^{+}(K_{\RG}) \text{ but } f(K_{\RG}+1)=f^{-}(K_{\RG}+1)
+\end{equation}
+
+which, because it has been assumed that \(f^{-}(K_{\RG}+1)=f^{-}(K_{\RG})\), contradicts the required result (as this would imply that \(f(K_{\RG})< f(K_{\RG}+1)\).
 
@@
 
-\[a^{\pm}=(f^{\pm}(K_{\RG}), K{\RG})\text{ and }b^{\pm}=(f^{\pm}(K_{\RG}+1), K{\RG}+1)\]
+\[a^{\pm}=(f^{\pm}(K_{\RG}), K_{\RG})\text{ and }b^{\pm}=(f^{\pm}(K_{\RG}+1), K_{\RG}+1))=(f^{\pm}(K_{\RG}), K_{\RG}+1))\]
 
@@
 
-this implies:
+which implies:
 

### 2015-07-22 AuthorInformationFile/author_information.tex
Submitting to JORS.

\documentclass{article}
\usepackage{fullpage}
\usepackage{parskip}

\title{Measuring the Price of Anarchy in Critical Care Unit Interactions\\
Author Information}
\author{Vincent Knight*
    \and
        Izabela Komenda
    \and
        Jeff Griffiths}

\begin{document}

\maketitle

\textbf{Author affiliations:}

\begin{itemize}
    \item Vincent Knight: Cardiff University, School of Mathematics
    \item Izabela Komdena: ABUHB Health Board, ABCi
    \item Jeff Griffiths: Cardiff University, School of Mathematics
\end{itemize}

\textbf{Corresponding author:}

Dr Vincent Knight\\
Cardiff School of Mathematics\\
Senghennydd Road,\\
Cardiff\\
CF24 4AG\\
(+44) 29 2087 5548\\
www.vknight.org\\
+Vincent Knight\\
@drvinceknight\\
Skype: drvinceknight

\textbf{Statement of contribution:}

This paper contributes to the operational research literature in two main ways:

\begin{itemize}
    \item  Application of Game Theory to a healthcare system with a view to
        understanding choice of performance targets.
    \item Theoretical results as to the existence of Nash equilibria in pure
        strategies for the specific game considered.
\end{itemize}

The contribution is novel by placing an analytical stochastic model of critical
care unit interaction in a game theoretic context. The utilities of the game are
outputs of the stochastic model. Further to this the game is solved using a
simple search thanks to a theoretic result proving the existence of a pure Nash
equilibrium.

Various numerical results are offered which help describe the best design of
incentives so that each critical care unit acts in a coordinated way.

\end{document}

### 2016-03-15 Reviews/response.tex
Adding reviews.

\documentclass{article}

\usepackage{fullpage}
\usepackage{parskip}

\title{Responses to Reviews for Measuring the Price of Anarchy in Critical Care Unit Interactions}
\author{Vincent Knight*
    \and
        Izabela Komenda
    \and
        Jeff Griffiths}

\begin{document}

\maketitle

Below we respond to each reviewer in detail.

\subsection{Reviewer 1}

\begin{quote}
    \begin{textit}{
Write the clarifications of notations \(\lambda_{h}^{(l,h)},\lambda_{h}^{(l,l)}\). One \(h \in (NH,RG)\) other \(h\) denotes RG experiences high demand.
    }\end{textit}
\end{quote}

\begin{quote}
    \begin{textit}{
Give explanation for figure 3.
    }\end{textit}
\end{quote}

\begin{quote}
    \begin{textit}{
Write clearly major contribution of the paper corresponding to the existing
literature.
    }\end{textit}
\end{quote}

\begin{quote}
    \begin{textit}{
State clearly the objectives of the model.
    }\end{textit}
\end{quote}

\subsection{Reviewer 2}

\begin{quote}
    \begin{textit}{
    On page 5, the model is referred to as a Figure 6. This confuses and leaves a question on whether it is a figure or equations. I am unsure whether figure 6 is missing or authors are referring to the model on page 6.
    }\end{textit}
\end{quote}

\begin{quote}
    \begin{textit}{
The paper is unreadable. The unknowns used, some, are undefined, for example on page 3, h, ch, etc are not defined and it is very difficult to find definitions of those defined. I suggest that the authors provide a list of the parameters used somewhere in the paper where it is easy to refer.
    }\end{textit}
\end{quote}

\begin{quote}
    \begin{textit}{
    On page 12, authors states that ``It is also noted that as demand increases the effect of uncoordinated behaviour increases (and the recommended target also increases) as shown in Figure 13'', is there any possible explanation to this finding.
    }\end{textit}
\end{quote}

\begin{quote}
    \begin{textit}{
    Are the Queuing and Game theoretic models never been implemented to solve such problems? There is a need to review literature that has information on application of the used models to hospital problems or related problems.
    }\end{textit}
\end{quote}

\begin{quote}
    \begin{textit}{
The authors need to give a justification on the reason why they are implementing the models.
    }\end{textit}
\end{quote}

\subsection{Reviewer 3}

\begin{quote}
    \begin{textit}
        {I recommend that the authors write a more complete and coherent
        Discussion and/or Conclusion which places their work in the context of
        the critcal care system.  It should relate model limitations to the
        critical care system. The current way that limitations are discussed
        is too technical. A brief discussion of stakeholder feedback would
        also be useful.}
    \end{textit}
\end{quote}

\begin{quote}
    \begin{textit}
        {
        At the beginning of Section 3.1, the authors claim that if neither CCU
        is able to admit patients, then admission to the CCU is cancelled and
        the patient is admitted to a general ward. In my experience modelling
        CCUs, it is highly unlikely that a critical patient would ever be
        admitted to a general ward.  CCU beds are almost always equipped with
        ventilators and ward beds never. I believe that more likely courses of
        action are:
        \begin{itemize}
         \item Sending the patient to another hospital's CCU.  This would be a CCU
           outside of the model.
         \item ``Bumping" a patient currently in the CCU to a ward bed, to free up
           a bed. This would normally be a patient who was nearly ready to be
           transferred to the ward anyway.
         \item Accommodating the patient in the hospital's post-anesthesia care
           unit (PACU), which sometimes functions as an overflow for the CCU.
        \end{itemize}
        I recommend that the authors consult with their stakeholders and
        correct this comment in their paper, if necessary.  This wouldn't have
        any impact on their model, but it is important to use the correct
        language.
        }
    \end{textit}
\end{quote}

\begin{quote}
    \begin{textit}
        {
        The axis labels on many of the graphs are in a very small font. The
        font size should be increased.
        }
    \end{textit}
\end{quote}

\begin{quote}
    \begin{textit}
        {
        The optimisation problem is shown as a figure (Figure 6). I suggest
        that this be separated from the text with a header such as
        ``Optimisation Problem" (much like a theorem).  Calling it a figure
        seems like a misnomer, and for me, actually made it harder to find.
        }
    \end{textit}
\end{quote}

\begin{quote}
    \begin{textit}
        {
        In Figure 7, the caption should state which points are \(f_NH\) and
        which are \(F_RG\).
        }
    \end{textit}
\end{quote}

\begin{quote}
    \begin{textit}
        {
I was puzzled as to whether the target, t, appeared in the definition
of \(T^*\). As I understand it, \(T^*\) is independent of \(t\). Is this true?
Also, for which values of \(K_NH\) and \(K_RG\) is the maximum achieved? Is my
intuition correct that it is achieved at \(K_NH = c_NH\) and \(K_RG = c_RG\)?
        }
    \end{textit}
\end{quote}

\begin{quote}
    \begin{textit}
        {
The authors make extensive use of bullets in the text. While bullets
can be useful to draw attention to key points, they can lead to lazy
writing. In my view, converting some of the bullet lists would improve
the clarity of the exposition.
        }
    \end{textit}
\end{quote}
\end{document}

### 2016-03-15 Reviews/response.tex
Writing todo list.

@@
 
+\begin{itemize}
+    \item Change one of the hs.
+\end{itemize}
+
 \begin{quote}
@@
 \end{quote}
+
+\begin{itemize}
+    \item Add a sentence.
+\end{itemize}
 
@@
 
+\begin{itemize}
+    \item Point out that this is there. Ask if there would be a better way of doing it?
+\end{itemize}
+
 \begin{quote}
@@
 \end{quote}
+
+\begin{itemize}
+    \item Not sure I understand, mention that have clarified the model for each player.
+\end{itemize}
 
@@
 
+\begin{itemize}
+    \item Mention that this has changed.
+\end{itemize}
+
 \begin{quote}
@@
 
+\begin{itemize}
+    \item Highlight that this is all in the paper.
+\end{itemize}
+
 \begin{quote}
@@
 \end{quote}
+
+\begin{itemize}
+    \item Suggest some explanations.
+\end{itemize}
 
@@
 
+\begin{itemize}
+    \item This is in the paper.
+\end{itemize}
+
 \begin{quote}
@@
 \end{quote}
+
+\begin{itemize}
+    \item Point to wider discussion invited by reviewer 3.
+\end{itemize}
 
@@
 \end{quote}
+
+\begin{itemize}
+    \item Add to discussion, point out that previous limitations were technical and now discuss ccu limitations. Mainly following from points suggested by reviewer 3.
+\end{itemize}
 
@@
 
+\begin{itemize}
+    \item List all of above as options but use first as most related to model.
+\end{itemize}
+
 \begin{quote}
@@
 \end{quote}
+
+\begin{itemize}
+    \item Make bigger.
+\end{itemize}
 
@@
 
+\begin{itemize}
+    \item Change this.
+\end{itemize}
+
 \begin{quote}
@@
 
+\begin{itemize}
+    \item State this in captions.
+\end{itemize}
+
 \begin{quote}
@@
 of \(T^*\). As I understand it, \(T^*\) is independent of \(t\). Is this true?
-Also, for which values of \(K_NH\) and \(K_RG\) is the maximum achieved? Is my
-intuition correct that it is achieved at \(K_NH = c_NH\) and \(K_RG = c_RG\)?
+Also, for which values of \(K_{NH}\) and \(K_{RG}\) is the maximum achieved? Is my
+intuition correct that it is achieved at \(K_{NH} = c_{NH}\) and \(K_{RG} = c_{RG}\)?
         }
@@
 \end{quote}
+
+\begin{itemize}
+    \item Clarify this, I believe that it's not always the case that \(K_{NH}=c_{NH}\).
+\end{itemize}
 
@@
 \end{quote}
+
+\begin{itemize}
+    \item Remove bullet points.
+\end{itemize}
 \end{document}

### 2016-03-15 Paper/paper.tex
Correct link to code
Making fonts larger on all axis labels.

@@
                 % Coordinate system
-                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\(\bar\lambda_{K_{\RG}}\)};
-                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {Occupancy at RG};
+                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\Large \(\bar\lambda_{K_{\RG}}\)};
+                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {\Large Occupancy at RG};
                 % lambda
@@
                 % Coordinate system
-                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\(\bar\lambda_{K_{\NH}}\)};
-                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {Occupancy at NH};
+                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\Large \(\bar\lambda_{K_{\NH}}\)};
+                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {\Large Occupancy at NH};
                 % lambda
@@
             % Coordinate system
-            \draw [very thick, ->] (0,0) -- (0,6) node[anchor=south east] {\(K_{\RG}\)};
-            \draw [very thick, ->] (0,0) -- (7,0) node[anchor=north west] {\(K_{\NH}\)};
+            \draw [very thick, ->] (0,0) -- (0,6) node[anchor=south east] {\Large\(K_{\RG}\)};
+            \draw [very thick, ->] (0,0) -- (7,0) node[anchor=north west] {\Large\(K_{\NH}\)};
 
@@
 
-The code used in this work can be found here: \url{https://github.com/drvinceknight/Measuring_the_price_of_anarchy_in_ccu_interactions}.
+The code used in this work can be found here: \url{https://gist.github.com/anonymous/81effc06eea70a9e4e2f}.
 The graphics for this paper were obtained using \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://cloud.sagemath.com/projects/c293aefd-1fdf-4b9c-95f4-75bb77035e42/files/MeasuringThePriceOfAnarchyInCCUInteractions.sagews}.

### 2016-03-15 Reviews/response.tex
Making fonts larger on all axis labels.
Changing the opt to section + add legen to fig.

@@
 
-\begin{itemize}
-    \item Make bigger.
-\end{itemize}
+All axis labels have now got a bigger font. We appreciate this comment: if any
+other aspects of the graphics could be improved we would be happy to make the
+suggested changes.
 
@@
 
+This has been changed:
+
 \begin{itemize}
-    \item Change this.
+    \item The figure has been changed to a section with a header as suggested.
+    \item A label (3) has been added for easier reference throughout the text.
 \end{itemize}
@@
 
-\begin{itemize}
-    \item State this in captions.
-\end{itemize}
+This is a good point, we have clarified this by noting `crosses' and `diamonds' in plain text in the caption.
 

### 2016-03-15 Paper/paper.tex
Changing the opt to section + add legen to fig.

@@
 
-Based on the discussion above, the game theoretic model is presented as a synchronous optimisation problem shown in Figure \ref{model1}.
-
-\begin{figure}[!htbp]
+Based on the discussion above, the game theoretic model is presented as a
+synchronous optimisation problem shown in the following optimisation problem.
+
+\textbf{Optimisation problem.}
+
 \hspace{2cm}For all $h\in\{\text{NH}, \text{RG}\}$ minimise:
@@
 \begin{align}
-0\leq & K_h \leq c_{h}\nonumber\\
+0\leq & K_h \leq c_{h}\label{model1}\\
 &K_h \in  \mathbb{Z}\nonumber
 \end{align}
-\caption{The optimisation problem underlying the game}\label{model1}
-\end{figure}
 
@@
 
-If $f_{h}(k)$ is a non-decreasing function in $k$ then the game of Figure \ref{model1} has at least one Nash Equilibrium.
+If $f_{h}(k)$ is a non-decreasing function in $k$ then the game of
+(\ref{model1}) has at least one Nash Equilibrium.
 
@@
     \end{center}
-    \caption{Plots of $f_{\NH}(K_{\RG})$ and $f_{\RG}(K_{\NH})$}\label{exampleforproof}
-\end{figure}
-
-This point of intersection corresponds to a Nash Equilibrium of Figure \ref{model1}.
+    \caption{Plots of $f_{\NH}(K_{\RG})$ (crosses) and $f_{\RG}(K_{\NH})$ (diamonds)}\label{exampleforproof}
+\end{figure}
+
+This point of intersection corresponds to a Nash Equilibrium of (\ref{model1}).
 
@@
 
-We let $\widetilde T$ denote the sum of throughputs at the Nash Equilibrium obtained by solving the game of Figure \ref{model1} (in case of multiple equilibria we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{NH}, K_{RG}}\left(T_{NH}+T_{RG}\right)$.
+We let $\widetilde T$ denote the sum of throughputs at the Nash Equilibrium obtained by solving the game of (\ref{model1}) (in case of multiple equilibria we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{NH}, K_{RG}}\left(T_{NH}+T_{RG}\right)$.
 
@@
 
-The game theoretic model of Figure \ref{model1} is solved using exhaustive consideration of best responses whilst taking advantage of the structure identified by the Lemma of Section \ref{queueingandgamemodels}.
+The game theoretic model of (\ref{model1}) is solved using exhaustive consideration of best responses whilst taking advantage of the structure identified by the Lemma of Section \ref{queueingandgamemodels}.
 For any given pair of threshold strategies the matrix equation $\pi Q=0$ is solved by obtaining a basis for the Kernel of $Q$.

### 2016-03-15 Reviews/response.tex
Adding discussion about optimal T^*.

@@
 \usepackage{parskip}
+\usepackage{booktabs}
+\usepackage{minted}
+\usepackage{amsmath}
+
+\newcommand{\NH}{\text{NH}}
+\newcommand{\RG}{\text{RG}}
 
@@
 
+This is an excellent question. The reviewer understand correctly: \(T^*\) is
+not dependent of \(t\).
+
+Identifying the point at which throughput is maximised is however not
+immediate. When we began working on this paper we had the same intuition as the
+reviewer (that throughput would always be maximised when using the highest
+possible threshold), however this is not the case.
+
+Indeed, for example for the second model, when using a system with parameters:
+
 \begin{itemize}
-    \item Clarify this, I believe that it's not always the case that \(K_{NH}=c_{NH}\).
+    \item \(c_{\text{RG}}=2, c_{\text{NH}}=3\)
+    \item \(\mu_{\text{RG}}=0.22, \mu_{\text{NH}}=1.66\)
+    \item \(\lambda_{\text{RG}}=3, \mu_{\text{NH}}=1\)
 \end{itemize}
+
+The throughputs for each cutoff pair are shown in the table below:
+
+\begin{center}
+    \begin{tabular}{cc}
+        \toprule
+        Throughput & Cut off pairs\\
+        \midrule
+        1.704098 &(2, 0)\\
+        1.843005 &(1, 0)\\
+        1.857689 &(0, 0)\\
+        3.27514 &(2, 1)\\
+        3.472371 &(1, 1)\\
+        3.51033 &(0, 1)\\
+        4.291777 &(2, 2)\\
+        4.488501 &(1, 2)\\
+        4.549065 &(0, 2)\\
+        4.767654 &(2, 3)\\
+        4.877357 &(1, 3)\\
+        4.916791 &(0, 3)\\
+        4.928235 &(2, 4)\\
+        4.961882 &(1, 4)\\
+        4.969698 &(0, 4)\\
+        \bottomrule
+    \end{tabular}
+\end{center}
+
+We see that the optimal throughput is obtained when RG is in effect `closed'
+and NH is never in a diverted state. This is due to the fact that the service
+rate for RG is very low and NH is not subject to high levels of demand.
+Through our investigations other examples occur that evidence this: the main idea that seems to pervade is that running a system at full capacity is not necessariy optimal.
+
+If it is of interest the Sagemath code (making use of the models distributed
+with the previously made available code) to obtain the above table is:
+
+\begin{minted}[frame=lines]{python}
+capacity_list = [2, 3]
+serviceratelist = [0.22, 1.66]
+demandratelist = [3, 1]
+model = Model2(capacity_list, serviceratelist, demandratelist)
+model.sweepcutoffs()
+tps = {model.data[pair].throughput1 + model.data[pair].throughput2: pair for pair in model.data}
+for tp in sorted(tps.keys()):
+    print round(tp,6), tps[tp]
+\end{minted}
+
+A brief discussion of this has been added to the paper which now reads:
+
+... This optimal throughput \(T^*\) is
+independent of \(t\).
+
+Note that intuitively it could be thought that \(T^*\) is obtained when
+\(K_{\NH}=c_{\NH}\) and \(K_{\RG}=c_{\RG}\) however this is not always the case
+(numerical experiments have been carried out to verify this).
 

### 2016-03-15 Paper/paper.tex
Adding discussion about optimal T^*.

@@
 
-We let $\widetilde T$ denote the sum of throughputs at the Nash Equilibrium obtained by solving the game of (\ref{model1}) (in case of multiple equilibria we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{NH}, K_{RG}}\left(T_{NH}+T_{RG}\right)$.
+We let $\widetilde T$ denote the sum of throughputs at the Nash Equilibrium
+obtained by solving the game of (\ref{model1}) (in case of multiple equilibria
+we take $\widetilde T$ to be the lowest throughput) and let $T^*=\max_{K_{\NH},
+K_{\RG}}\left(T_{\NH}+T_{\RG}\right)$. This optimal throughput \(T^*\) is
+independent of \(t\).
+
+Note that intuitively it could be thought that \(T^*\) is obtained when
+\(K_{\NH}=c_{\NH}\) and \(K_{\RG}=c_{\RG}\) however this is not always the case
+(very numerical experiments have been carried out to verify this).
 

### 2016-03-15 Paper/paper.tex
Changing h to H for hospitals.

@@
 Given the proximity of the two CCUs, one CCU could for example divert their patients to the other.
-Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_h^{r}$ for $h\in\{\NH, \RG\}$ and $r\in\{(l,l), (l,h), (h,l), (h,h)\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $r$ denotes regions with boundaries defined by the capacity thresholds.
+Figure \ref{arrivalrateregions} shows a diagrammatic representation of this where $\lambda_H^{r}$ for $H\in\{\NH, \RG\}$ and $r\in\{(l,l), (l,h), (h,l), (h,h)\}$ simply denote arrival rates that will be defined for both models considered in Section \ref{results}, where $r$ denotes regions with boundaries defined by the capacity thresholds.
 For example $(l,h)$ denotes a region for which $\NH$ experiences \textit{low} demand and $\RG$ experiences \textit{high} demand.
 It is also assumed that diverted patients will be treated under the length of stay profile of the CCU they are admitted to.
-The capacity thresholds are denoted as $K_{h}\in\mathbb{Z}$ for $h\in\{\NH,\RG\}$. Note that $0\leq K_h\leq c_h$.
+The capacity thresholds are denoted as $K_{H}\in\mathbb{Z}$ for $H\in\{\NH,\RG\}$. Note that $0\leq K_N\leq c_H$.
 
@@
         \node at (3,3.25) {$K_{\RG}$};
-        \node at (1.5,2) {$\lambda_{h}^{(l,l)}$};
-        \node at (3.5,2) {$\lambda_{h}^{(l,h)}$};
-        \node at (1.5,.5) {$\lambda_{h}^{(h,l)}$};
-        \node at (3.5,.5) {$\lambda_{h}^{(h,h)}$};
+        \node at (1.5,2) {$\lambda_{H}^{(l,l)}$};
+        \node at (3.5,2) {$\lambda_{H}^{(l,h)}$};
+        \node at (1.5,.5) {$\lambda_{H}^{(h,l)}$};
+        \node at (3.5,.5) {$\lambda_{H}^{(h,h)}$};
     \end{tikzpicture}
-\caption{General arrival rates for each CCU at each region, where $h\in\{\NH, \RG\}$} \label{arrivalrateregions}
+\caption{General arrival rates for each CCU at each region, where $H\in\{\NH, \RG\}$} \label{arrivalrateregions}
 \end{center}
@@
 Throughput of patients is a natural choice of utility given that most hospitals are financially rewarded per served patient \cite{Pate2009}.
-For each threshold pair $(K_{\NH},K_{\RG})$, the utilisation rate $U_h$ and throughput $T_h$ can easily be obtained for each CCU: $h\in\{\text{NH},\text{RG}\}$, using the following formulas:
-
-$$U_{h}={{\sum_{n=0}^{c_h} nP^{(h)}(n)}\over{c_{h}}}$$
-$$T_{h}=\mu_h \sum _{n=0}^{c_h} nP^{(h)}(n)$$
-
-where $P^{(h)}=P^{(h)}(K_{\NH},K_{\RG})$ is the steady state probability distribution function (obtained from the corresponding transition matrix $Q=Q(K_{\NH},K_{\RG})$) for $h\in\{\text{NH},\text{RG}\}$.
+For each threshold pair $(K_{\NH},K_{\RG})$, the utilisation rate $U_H$ and throughput $T_H$ can easily be obtained for each CCU: $H\in\{\text{NH},\text{RG}\}$, using the following formulas:
+
+$$U_{H}={{\sum_{n=0}^{c_H} nP^{(H)}(n)}\over{c_{H}}}$$
+$$T_{H}=\mu_H \sum _{n=0}^{c_H} nP^{(H)}(n)$$
+
+where $P^{(H)}=P^{(H)}(K_{\NH},K_{\RG})$ is the steady state probability distribution function (obtained from the corresponding transition matrix $Q=Q(K_{\NH},K_{\RG})$) for $H\in\{\text{NH},\text{RG}\}$.
 
@@
 \includegraphics[width=.5\textwidth]{./Images/NH.pdf}&\includegraphics[width=.5\textwidth]{./Images/RG.pdf}\\
-h=NH&h=RG
+H=\NH&H=\RG
 \end{array}
 $$
-\caption{Steady state probabilities for $h\in\{\NH,\RG\}$ with $(K_{\NH}, K_{\RG})=(6,12)$} \label{steady_state_probs}
+\caption{Steady state probabilities for $H\in\{\NH,\RG\}$ with $(K_{\NH}, K_{\RG})=(6,12)$} \label{steady_state_probs}
 \end{figure}
@@
 \includegraphics[width=.5\textwidth]{./Images/NH_1_12.pdf}&\includegraphics[width=.5\textwidth]{./Images/RG_1_12.pdf}\\
-h=\NH&h=\RG
+H=\NH&H=\RG
 \end{array}
 $$
-\caption{Steady state probabilities for $h\in\{\NH,\RG\}$ with $(K_{\NH}, K_{\RG})=(1,12)$} \label{steady_state_probs_1_12}
+\caption{Steady state probabilities for $H\in\{\NH,\RG\}$ with $(K_{\NH}, K_{\RG})=(1,12)$} \label{steady_state_probs_1_12}
 \end{figure}
@@
 
-\hspace{2cm}For all $h\in\{\text{NH}, \text{RG}\}$ minimise:
-$$\left(U_{h}-t\right)^2$$
+\hspace{2cm}For all $H\in\{\text{NH}, \text{RG}\}$ minimise:
+$$\left(U_{H}-t\right)^2$$
 \hspace{2cm}Subject to:
 \begin{align}
-0\leq & K_h \leq c_{h}\label{model1}\\
-&K_h \in  \mathbb{Z}\nonumber
+0\leq & K_H \leq c_{H}\label{model1}\\
+&K_H \in  \mathbb{Z}\nonumber
 \end{align}
@@
 
-Let $f_{h}(k):[1,c_{\bar h}]\to[1,c_h]$ be the best response of player $h\in\{\NH, \RG\}$ to the diversion threshold of $\bar h\ne h$ ($\bar h\in\{\NH, \RG\}$).
-
-If $f_{h}(k)$ is a non-decreasing function in $k$ then the game of
+Let $f_{H}(k):[1,c_{\bar H}]\to[1,c_H]$ be the best response of player $H\in\{\NH, \RG\}$ to the diversion threshold of $\bar h\ne h$ ($\bar H\in\{\NH, \RG\}$).
+
+If $f_{H}(k)$ is a non-decreasing function in $k$ then the game of
 (\ref{model1}) has at least one Nash Equilibrium.
@@
 
-The function $f_h$ is well defined as it maximises a continuous function over a finite discrete set.
-In case of multiple values that minimize $U_h$, it is assumed that $f_h$ returns the lowest such value, this is consistent with the PoA being a theoretical upper bound of the effect of uncoordinated behaviour \cite{TimRoughgarden}.
-
-As such if $f_h$ is non-decreasing then it is in fact a stepwise non-decreasing function.
+The function $f_H$ is well defined as it maximises a continuous function over a finite discrete set.
+In case of multiple values that minimize $U_H$, it is assumed that $f_H$ returns the lowest such value, this is consistent with the PoA being a theoretical upper bound of the effect of uncoordinated behaviour \cite{TimRoughgarden}.
+
+As such if $f_H$ is non-decreasing then it is in fact a stepwise non-decreasing function.
 If we consider $f_{\NH}$ and $f_{\RG}$ plotted on the same axis (so that the domain of $f_{\NH}$ is the $x$-axis and the domain of $f_{\RG}$ is the y-axis) it is obvious to see that the functions must intersect at some point as shown in Figure \ref{exampleforproof}.
@@
 
-This Theorem is in itself not that useful as the properties of $f_{h}$ are difficult to ascertain.
+This Theorem is in itself not that useful as the properties of $f_{H}$ are difficult to ascertain.
 Although the methodology alluded to is how the equilibria are found for the work presented here (exhaustive investigation of best response functions).
@@
 
-The utilisation $U_h=U_h(\lambda)$ is an increasing function in $\lambda$.
-
-\begin{center}
-As the traffic intensity at $h$ increases: $h$ gets busier.
+The utilisation $U_H=U_H(\lambda)$ is an increasing function in $\lambda$.
+
+\begin{center}
+As the traffic intensity at $H$ increases: $H$ gets busier.
 \end{center}
@@
 \(K_{\NH}=c_{\NH}\) and \(K_{\RG}=c_{\RG}\) however this is not always the case
-(very numerical experiments have been carried out to verify this).
+(numerical experiments have been carried out to verify this).
 
@@
 Figure \ref{Fig:target_demand_model1} (note: the non linear scale) and Table \ref{tabletargetdemandm1} show the effect of $t$ and overall demand.
-We modify the demand rate from Table \ref{parameter_values_model_1} by taking $\lambda_h \leftarrow \lambda_h(1+x)$ for $-0.9\leq x\leq2$.
+We modify the demand rate from Table \ref{parameter_values_model_1} by taking $\lambda_H \leftarrow \lambda_H(1+x)$ for $-0.9\leq x\leq2$.
 

### 2016-03-15 Reviews/response.tex
Changing h to H for hospitals.
minor (pointers to figures and removing bulet points)

@@
 
-\begin{itemize}
-    \item Change one of the hs.
-\end{itemize}
+Thank you to the reviewer for noticing this detail.
+We have changed all occurrences of \(h\) denoting an element of \(\NH, \RG\) to
+be \(H\). This clarifies the paper.
 
@@
 
-\begin{itemize}
-    \item Add a sentence.
-\end{itemize}
+Another pointer in the text to the Figure has been added (``The transition rates are given by (2) and are illustrated diagrammatically in Figure 3").
+This Figure is meant to illustrate diagrammatically the state space and transitions.
 
@@
 
-\begin{itemize}
-    \item Point out that this is there. Ask if there would be a better way of doing it?
-\end{itemize}
-
 \begin{quote}
@@
 
-\begin{itemize}
-    \item Not sure I understand, mention that have clarified the model for each player.
-\end{itemize}
+The following paragraph is in the introduction of the paper: if the reviewer does not find it sufficient we would gladly clarify it further.
+At present we feel that it very clearly places the contribution of the paper (as highlighted by the 3rd reviewer) and also highlights what the main finding/objective of the model is.
+
+``
+The work presented in this paper contributes to the growing body of literature by applying state dependent queueing models in a game theoretical context to CCU interaction.
+In particular this consideration allows for the investigation of targets imposed by central control [4].
+The findings of this work justify and identify a choice of targets that align the interests of the individual hospitals with social welfare.
+''
 
@@
 
-\begin{itemize}
-    \item Mention that this has changed.
-\end{itemize}
+This has now been fixed: the optimisation problem that defines the game is now
+in a section with title: `Optimisation problem' and is referred to by a
+labelling equation number. This was suggested by another reviewer and we feel
+improves the paper.
 
@@
 
-\begin{itemize}
-    \item Highlight that this is all in the paper.
-\end{itemize}
+We were disappointed by this comment. To suggest that the paper is unreadable
+is an exaggeration. Perhaps the reviewer did not have time to read page
+2 which contained a table that clearly listed the variables they mention?
+
+If we have misunderstood and that table is not sufficient we would gladly list
+the variables with their definitions in a format more pleasing to the referee.
+Although we note that the other two reviewers, one of which has clearly read
+the paper carefully did not find the paper unreadable.
 
@@
 
-\begin{itemize}
-    \item Suggest some explanations.
-\end{itemize}
+At present it is merely an observation from the emergent behaviour of the model however a sentence has been added:
+
+``
+It is also noted that as demand increases the effect of uncoordinated behaviour increases (and the recommended target also increases) as shown in Figure 12.
+This is potentially due to the fact that as demand increases there is the scope for larger discrepancy between optimal and sub optimal behaviours.
+''
 
@@
 
-\begin{itemize}
-    \item This is in the paper.
-\end{itemize}
-
 \begin{quote}
@@
 
-\begin{itemize}
-    \item Point to wider discussion invited by reviewer 3.
-\end{itemize}
+It seems that the reviewer did indeed not read page 2 of the manuscript.
+As highlighted by the 3rd reviewer a literature review is present.
+This literature review highlights that there is not much work at the intersection of game theory, queueing theory and healthcare.
+
+Furthermore the contributions and goals of the model are very clearly stated on page 2 and again highlighted in the conclusion section.
+If the reviewer could clarify there expectations if this is not sufficient we would gladly highlight the contributions of the paper (as recognized by the referees that have read it) further.
+
+``
+The work presented in this paper contributes to the growing body of literature by applying state dependent queueing models in a game theoretical context to CCU interaction.
+In particular this consideration allows for the investigation of targets imposed by central control [4].
+The findings of this work justify and identify a choice of targets that align the interests of the individual hospitals with social welfare.
+''
 
@@
         {
-        In Figure 7, the caption should state which points are \(f_NH\) and
-        which are \(F_RG\).
+            In Figure 7, the caption should state which points are \(f_{NH}\) and
+            which are \(F_{RG}\).
         }
@@
 
+``
 ... This optimal throughput \(T^*\) is
@@
 (numerical experiments have been carried out to verify this).
+''
 
@@
 
-\begin{itemize}
-    \item Remove bullet points.
-\end{itemize}
+3 of the 5 bullet point lists have been changed to be paragraphs. We felt that
+this left a nice balance but if the reviewer feels strongly about this, we
+would be happy to change the remaining bullet point lists.
 \end{document}

### 2016-03-15 Paper/paper.tex
minor (pointers to figures and removing bulet points)

@@
 
-The paper is organised as follows:
-\begin{itemize}
-    \item Section \ref{queueingandgamemodels} presents the general methodology as well as a theoretical existence condition for Nash Equilibrium;
-    \item Section \ref{results} presents the findings from two models;
-    \item Conclusions and further ideas for progression are given in Section \ref{conclusions}.
-\end{itemize}
+The paper is organised as follows: Section \ref{queueingandgamemodels} presents
+the general methodology as well as a theoretical existence condition for Nash
+Equilibrium. Section \ref{results} presents the findings from two models.
+Finally, conclusions and further ideas for progression are given in Section
+\ref{conclusions}.
 
@@
 
-The state space for the Markov chain is given by:
+The state space for the Markov chain is given by (\ref{statespace}).
 
@@
 The stochastic transition rate matrix $Q=Q(c_{NH},c_{RG})$ of the continuous-time Markov chain \cite{Stewart2009} has entries $q_{ij}=q_{(u_i,v_i),(u_j,v_j)}$ which is the rate at which a transition from state $i$ to state $j$ occurs.
-The transition rates are given by:
+The transition rates are given by (\ref{transitions}) and are illustrated diagrammatically in Figure \ref{mc}.
 
@@
 \end{cases}
+\label{transitions}
 \end{equation}
@@
 In particular it can be seen that a value of $t>0.8$ becomes imperative for high demand.
-The lowest value of $t$ for which gives PoA$=1$ for the actual demand levels ($x=0$) is in fact $t=0.72$.
+The lowest value of $t$ which gives PoA$=1$ for the actual demand levels ($x=0$) is in fact $t=0.72$.
 It is also noted that as demand increases the effect of uncoordinated behaviour increases (and the recommended target also increases) as shown in Figure \ref{mintargetvdemand}.
+This is potentially due to the fact that as demand increases there is the scope for larger discrepancy between optimal and sub optimal behaviours.
 
@@
 
-Also, for very low values of demand, cooperation can be obtained with no target.
-\begin{itemize}
-    \item When the demand is low, there is no scope for uncoordinated behaviour to be damaging.
-    \item When the demand is very high, the system is saturated and once again uncoordinated behaviour has no negative effect in comparison to optimal behaviour.
-    \item There is however a region of demand for which there is a high PoA.
-\end{itemize}
+Also, for very low values of demand, cooperation can be obtained with no
+target.  When the demand is low, there is no scope for uncoordinated behaviour
+to be damaging.  When the demand is very high, the system is saturated and once
+again uncoordinated behaviour has no negative effect in comparison to optimal
+behaviour.  There is however a region of demand for which there is a high PoA.
 
@@
 
-A result is proved that allows for the assertion of existence of a Nash Equilibrium. This result is then applied to two particular models that are influenced by discussions with a local health board:
-
-\begin{itemize}
-\item Strict diversion: patients can be lost to the system if both CCUs declare being in diversion.
-\item Soft diversion: if both CCUs are in diversion then they cannot divert their own patients.
-\end{itemize}
+A result is proved that allows for the assertion of existence of a Nash
+Equilibrium. This result is then applied to two particular models that are
+influenced by discussions with a local health board. \textbf{Strict diversion}:
+patients can be lost to the system if both CCUs declare being in diversion.
+\textbf{Soft diversion}: if both CCUs are in diversion then they cannot divert
+their own patients.
 

### 2016-03-30 Reviews/response.tex
First draft of review complete.

@@
 
-It seems that the reviewer did indeed not read page 2 of the manuscript.
-As highlighted by the 3rd reviewer a literature review is present.
-This literature review highlights that there is not much work at the intersection of game theory, queueing theory and healthcare.
+It seems that the reviewer did indeed not read page 2 of the manuscript. As
+highlighted by the 3rd reviewer a literature review is present. This literature
+review highlights that there is not much work at the intersection of game
+theory, queueing theory and healthcare.
 
-Furthermore the contributions and goals of the model are very clearly stated on page 2 and again highlighted in the conclusion section.
-If the reviewer could clarify there expectations if this is not sufficient we would gladly highlight the contributions of the paper (as recognized by the referees that have read it) further.
+Furthermore the contributions and goals of the model are very clearly stated on
+page 2 and again highlighted in the conclusion section. If the reviewer could
+clarify there expectations if this is not sufficient we would gladly highlight
+the contributions of the paper (as recognized by the referees that have read it)
+further.
 
 ``
-The work presented in this paper contributes to the growing body of literature by applying state dependent queueing models in a game theoretical context to CCU interaction.
-In particular this consideration allows for the investigation of targets imposed by central control [4].
-The findings of this work justify and identify a choice of targets that align the interests of the individual hospitals with social welfare.
+The work presented in this paper contributes to the growing body of literature
+by applying state dependent queueing models in a game theoretical context to CCU
+interaction.  In particular this consideration allows for the investigation of
+targets imposed by central control [4].  The findings of this work justify and
+identify a choice of targets that align the interests of the individual
+hospitals with social welfare.
 ''
@@
 
-\begin{itemize}
-    \item Add to discussion, point out that previous limitations were technical and now discuss ccu limitations. Mainly following from points suggested by reviewer 3.
-\end{itemize}
+This has been addressed, each technical bullet point is now complemented by a
+sentence putting the limitation in the context of critical care. Furthermore a
+discussion has been added that describes the feedback and further emphasises the
+contribution of the work:
+
+``
+Despite these mathematical limitations the work presented here gives a strong
+analytical evidence as to the use of policies in a decentralised healthcare
+environment.
+
+As discussed above, reducing the decision making of critical care managers to
+rational reactions to capacity targets is not without limitations. However, this
+quantitative model of behaviour was described as insightful and informative
+ABUHB. In practice, stakeholders describe a rule of 80\% capacity. Whilst this
+is not only at times impossible it is also not evidence based and in particular
+does not take in to account interactions between CCUs. This is a common theme in
+practice and the literature which this manuscript aims to address.
+''
 
@@
 \end{quote}
+
+This is a very good point, after discussion with our stakeholders we confirm all
+the suggestions made by the reviewer and have modified the text:
+
+``
+This model assumes that if the bed occupancy level at both Units exceeds a
+predetermined threshold, then the admission to the CCU is cancelled. This
+cancellation could correspond, to sending the patient to a completely different
+CCU (outside of the model), moving one of the current patients (ready to be
+dismieed) in the CCU to another ward and/or using the post-anethesisa care unit
+as a temporary overflow measure. This models corresponds to the first of those
+possibilities: the patient is lost (from the point of view of this model).
+''
 

### 2016-03-30 Paper/paper.tex
First draft of review complete.

@@
 
-This model assumes that if the bed occupancy level at both Units exceeds a predetermined threshold, then the admission to the CCU is cancelled (in reality this implies that patients will be admitted to a general ward within the hospital).
+This model assumes that if the bed occupancy level at both Units exceeds a
+predetermined threshold, then the admission to the CCU is cancelled. This
+cancellation could correspond, to sending the patient to a completely different
+CCU (outside of the model), moving one of the current patients (ready to be
+dismieed) in the CCU to another ward and/or using the post-anethesisa care unit
+as a temporary overflow measure. This models corresponds to the first of those
+possibilities: the patient is lost (from the point of view of this model).
+
 Recalling Figure \ref{arrivalrateregions} this implies:
@@
 \begin{itemize}
-    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{naor1969regulation, shone2013comparisons});
-    \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
-    \item The restriction to pure strategies is influenced by discussions with ABUHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.
-However, allowing for mixed strategies could also be of interest.
-    \item Patient length of stay is assumed to be dependent on the CCU at which they receive service.
-A further extension of the work would be to use the service rate from original CCU (prior to diversion).
-This would require a Markov chain with a higher dimensional state space.
+    \item The assumptions as to the strategy space of our players is
+        restrictive: a single threshold policy might not be optimal (although it
+        is present in various pieces of literature on optimal control of
+        queueing systems: \cite{naor1969regulation, shone2013comparisons}).
+        Indeed, in reality critical care managers could have far more complex
+        boundaries for their heuristic decision making;
+    \item This model only assumes the presence of two players however in reality
+        the system has a variety of stakeholders. Multi player systems could be
+        worth considering. This would reflect health boards/hospitals in a
+        concentrated area so that interactions are not just between two
+        hospitals but between many.
+    \item The restriction to pure strategies is influenced by discussions with
+        ABUHB and also does not detract from the results presented thanks to the
+        Theorem and Lemma of Section \ref{queueingandgamemodels}.  However,
+        allowing for mixed strategies could also be of interest, corresponding
+        to decision making that is not constant over time. Managers could
+        alternate between a variety of behaviours: at time accepting patient
+        despite being busy and at other times not;
+    \item Patient length of stay is assumed to be dependent on the CCU at which
+        they receive service. A further extension of the work would be to use
+        the service rate from original CCU (prior to diversion). This would
+        require a Markov chain with a higher dimensional state space. In
+        practice this corresponds to patient morbidity corresponding to the
+        original CCU.
 \end{itemize}
 
-Despite these limitations the work presented here gives a strong analytical evidence as to the use of policies in a decentralised healthcare environment.
-Further work could involve the investigation of patient survival instead of throughput as utility.
-This would be similar to work such as \cite{erkut2008ambulance, knight2012ambulance}.
+Despite these mathematical limitations the work presented here gives a strong
+analytical evidence as to the use of policies in a decentralised healthcare
+environment.
+
+As discussed above, reducing the decision making of critical care managers to
+rational reactions to capacity targets is not without limitations. However, this
+quantitative model of behaviour was described as insightful and informative by
+ABUHB. In practice, stakeholders describe a rule of 80\% capacity. Whilst this
+is not only at times impossible it is also not evidence based and in particular
+does not take in to account interactions between CCUs. This is a common theme in
+practice and the literature which this manuscript aims to address.
+
+Finally, congestion and throughput is not the only concern of a healthcare
+system. Further work could involve the investigation of patient survival instead
+of throughput as utility.  This would be similar to work such as
+\cite{erkut2008ambulance, knight2012ambulance}.
 

### 2016-04-10 Reviews/response.tex
Update response following comments by JG and IS
Also fixing paper where relevant.

@@
 
-We were disappointed by this comment. To suggest that the paper is unreadable
-is an exaggeration. Perhaps the reviewer did not have time to read page
-2 which contained a table that clearly listed the variables they mention?
+We were disappointed by this comment. Page 2 contains a table that clearly
+lists the variables.
 
-If we have misunderstood and that table is not sufficient we would gladly list
+If we have misunderstood and that table is not sufficient, we would gladly list
 the variables with their definitions in a format more pleasing to the referee.
-Although we note that the other two reviewers, one of which has clearly read
-the paper carefully did not find the paper unreadable.
 
@@
 
-It seems that the reviewer did indeed not read page 2 of the manuscript. As
-highlighted by the 3rd reviewer a literature review is present. This literature
-review highlights that there is not much work at the intersection of game
-theory, queueing theory and healthcare.
+As highlighted by the 3rd reviewer a literature review is present. This
+literature review highlights that there is not much work at the intersection of
+game theory, queueing theory and healthcare.
 
-Furthermore the contributions and goals of the model are very clearly stated on
-page 2 and again highlighted in the conclusion section. If the reviewer could
-clarify there expectations if this is not sufficient we would gladly highlight
-the contributions of the paper (as recognized by the referees that have read it)
-further.
+Furthermore the contributions and goals of the model are clearly stated on page
+2 and again highlighted in the conclusion section. If the reviewer could
+clarify expectations if this is not sufficient, we would gladly highlight the
+contributions of the paper further.
 
@@
 rational reactions to capacity targets is not without limitations. However, this
-quantitative model of behaviour was described as insightful and informative
-ABUHB. In practice, stakeholders describe a rule of 80\% capacity. Whilst this
+quantitative model of behaviour was described as insightful and informative by
+ABUHB. In practice, stakeholders describe a target of 80\% capacity. Whilst this
 is not only at times impossible it is also not evidence based and in particular
@@
 ``
-This model assumes that if the bed occupancy level at both Units exceeds a
+This model assumes that if the bed occupancy level at both CCUs exceeds a
 predetermined threshold, then the admission to the CCU is cancelled. This
-cancellation could correspond, to sending the patient to a completely different
-CCU (outside of the model), moving one of the current patients (ready to be
-dismieed) in the CCU to another ward and/or using the post-anethesisa care unit
+cancellation could correspond to sending the patient to a completely different
+CCU (outside of the model), moving one of the current CCU patients (ready to be
+discharged) to another ward and/or using the post-anesthesia care unit
 as a temporary overflow measure. This models corresponds to the first of those
@@
 
-All axis labels have now got a bigger font. We appreciate this comment: if any
+All axis labels have now a bigger font. We appreciate this comment: if any
 other aspects of the graphics could be improved we would be happy to make the
@@
     \item \(\mu_{\text{RG}}=0.22, \mu_{\text{NH}}=1.66\)
-    \item \(\lambda_{\text{RG}}=3, \mu_{\text{NH}}=1\)
+    \item \(\lambda_{\text{RG}}=3, \lambda_{\text{NH}}=1\)
 \end{itemize}
@@
 Note that intuitively it could be thought that \(T^*\) is obtained when
-\(K_{\NH}=c_{\NH}\) and \(K_{\RG}=c_{\RG}\) however this is not always the case
+\(K_{\NH}=c_{\NH}\) and \(K_{\RG}=c_{\RG}\); however this is not always the case
 (numerical experiments have been carried out to verify this).

### 2016-04-10 Paper/paper.tex
Update response following comments by JG and IS
Also fixing paper where relevant.

@@
 
-This model assumes that if the bed occupancy level at both Units exceeds a
+This model assumes that if the bed occupancy level at both CCUs exceeds a
 predetermined threshold, then the admission to the CCU is cancelled. This
-cancellation could correspond, to sending the patient to a completely different
-CCU (outside of the model), moving one of the current patients (ready to be
-dismieed) in the CCU to another ward and/or using the post-anethesisa care unit
+cancellation could correspond to sending the patient to a completely different
+CCU (outside of the model), moving one of the current CCU patients (ready to be
+discharged) to another ward and/or using the post-anesthesia care unit
 as a temporary overflow measure. This models corresponds to the first of those
@@
 quantitative model of behaviour was described as insightful and informative by
-ABUHB. In practice, stakeholders describe a rule of 80\% capacity. Whilst this
+ABUHB. In practice, stakeholders describe a target of 80\% capacity. Whilst this
 is not only at times impossible it is also not evidence based and in particular

### 2016-04-10 Paper/paper.tex
Revisions to paper.

@@
 \begin{abstract}
-Hospital throughput is often studied and optimised in isolation, ignoring the interactions between hospitals.
-In this paper Critical Care Unit (CCU) interaction is placed within a game theoretic framework.
-The methodology involves the use of a normal form game underpinned by a two dimensional continuous Markov chain.
-A theorem is given that proves that a Nash Equilibrium exists in pure strategies for the games considered.
-
-In the UK a variety of utilisation targets are often discussed: aiming to ensure that wards/hospitals operate at a given utilisation value.
-The effect of these target policies is investigated justifying their use to align the interests of individual hospitals and social welfare.
-In particular, we identify the lowest value of a utilisation target that aligns these.
+Hospital throughput is often studied and optimised in isolation, ignoring the
+interactions between hospitals.  In this paper Critical Care Unit (CCU)
+interaction is placed within a game theoretic framework.  The methodology
+involves the use of a normal form game underpinned by a two dimensional
+continuous Markov chain.  A theorem is given that proves that a Nash Equilibrium
+exists in pure strategies for the games considered.
+
+In the United Kingdom a variety of utilisation targets are often discussed:
+aiming to ensure that wards/hospitals operate at a given utilisation value.  The
+effect of these target policies is investigated justifying their use to align
+the interests of individual hospitals and social welfare.  In particular, we
+identify the lowest value of a utilisation target that aligns these.
 \end{abstract}
@@
 CCUs face major challenges, on average, 8\% of patients are refused admission to a CCU because the Unit is full \cite{Report}.
-The CCU occupancy rates for some hospitals are reportedly very high \cite{Mitchell1995,Smith1995} and a shortage of beds has been identified throughout the UK.
+The CCU occupancy rates for some hospitals are reportedly very high
+\cite{Mitchell1995,Smith1995} and a shortage of beds has been identified
+throughout the United Kingdom.
 
@@
 It is also assumed that diverted patients will be treated under the length of stay profile of the CCU they are admitted to.
-The capacity thresholds are denoted as $K_{H}\in\mathbb{Z}$ for $H\in\{\NH,\RG\}$. Note that $0\leq K_N\leq c_H$.
+The capacity thresholds are denoted as $K_{H}\in\mathbb{Z}$ for
+$H\in\{\NH,\RG\}$. Note that $0\leq K_H\leq c_H$.
 
@@
         % -----------------------------------------------
-        \draw [dashed, line width=1mm, red, opacity=.3] (12,2) -- (12,-20);
-        \draw [dashed, line width=1mm, red, opacity=.3] (-2,-12) -- (20,-12);
+        \draw [dashed, red, line width=1mm, opacity=.3] (12,2) -- (12,-20);
+        \draw [dashed, red, line width=1mm, opacity=.3] (-2,-12) -- (20,-12);
         %\tikzstyle{state}=[ellipse, draw, fill=blue!10, minimum width=2cm];
@@
         \draw (bc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisb1);
-        \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisb1);
+        \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisb1);
 
@@
         \draw (cc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisc1);
-        \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisc1);
+        \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisc1);
 
@@
         \draw (dc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(l,l)}$} (ellipsisd1);
-        \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisd1);
+        \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisd1);
 
@@
         \draw (ec) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (ellipsise1);
-        \draw (ec) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsise1);
+        \draw (ec) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsise1);
 
@@
         \draw (fc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,l)}$} (ellipsisf1);
-        \draw (fc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisf1);
+        \draw (fc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisf1);
 
@@
         \draw (zc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(h,h)}$} (ellipsisz1);
-        \draw (zc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$333\mu_{\RG}$} (ellipsisz1);
+        \draw (zc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$3\mu_{\RG}$} (ellipsisz1);
 
@@
 \begin{align}
-0\leq & K_H \leq c_{H}\label{model1}\\
+0\leq &\; K_H \leq c_{H}\label{model1}\\
 &K_H \in  \mathbb{Z}\nonumber
@@
 
-Let $f_{H}(k):[1,c_{\bar H}]\to[1,c_H]$ be the best response of player $H\in\{\NH, \RG\}$ to the diversion threshold of $\bar h\ne h$ ($\bar H\in\{\NH, \RG\}$).
+Let $f_{H}(k):[1,c_{\bar H}]\to[1,c_H]$ be the best response of player $H\in\{\NH, \RG\}$ to the diversion threshold of $\bar H\ne H$ ($\bar H\in\{\NH, \RG\}$).
 
@@
 
-The function $f_H$ is well defined as it maximises a continuous function over a finite discrete set.
-In case of multiple values that minimize $U_H$, it is assumed that $f_H$ returns the lowest such value, this is consistent with the PoA being a theoretical upper bound of the effect of uncoordinated behaviour \cite{TimRoughgarden}.
-
-As such if $f_H$ is non-decreasing then it is in fact a stepwise non-decreasing function.
-If we consider $f_{\NH}$ and $f_{\RG}$ plotted on the same axis (so that the domain of $f_{\NH}$ is the $x$-axis and the domain of $f_{\RG}$ is the y-axis) it is obvious to see that the functions must intersect at some point as shown in Figure \ref{exampleforproof}.
+The function $f_H$ is well defined as it maximises a continuous function over a
+finite discrete set.  In case of multiple values that minimize $U_H$, it is
+assumed that $f_H$ returns the lowest such value, this is consistent with the
+Price of Anarchy (PoA) being a theoretical upper bound of the effect of
+uncoordinated behaviour \cite{TimRoughgarden}.
+
+As such if $f_H$ is non-decreasing then it is in fact a stepwise non-decreasing
+function.  If we consider $f_{\NH}$ and $f_{\RG}$ plotted on the same axis (so
+that the domain of $f_{\NH}$ is the $x$-axis and the domain of $f_{\RG}$ is the
+y-axis) it is obvious to see that the functions must intersect at some point as
+shown in Figure \ref{exampleforproof}.
 
@@
         \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
-            \foreach \x in {0,9}
-            {\coordinate (origin) at (\x,0);
+            \coordinate (origin) at (0,0);
+                % Coordinate system
+                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\Large \(\bar\lambda_{K_{\RG}}\)};
+                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {\Large Occupancy at RG};
+                % lambda
+                \draw ($(origin) + (0,2)$) -- ($(origin) + (2,2)$) -- ($(origin) + (2,4)$) -- ($(origin) + (5,4)$);
+                \node at ($(origin) + (1,2.5)$) {\(\lambda_{\NH}^{(h,l)}\)};
+                \node at ($(origin) + (3.5,4.5)$) {\(\lambda_{\NH}^{(h,h)}\)};
+                % Effect of KRG
+                \draw [dashed] ($(origin) + (0,2)$) -- ($(origin) + (4,2)$) -- ($(origin) + (4,4)$);
+                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,2)$);
+                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,2)$);
+                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
+                \node at ($(origin) + (2,0)$) [below] {\(K_{\RG}\)};
+                \node at ($(origin) + (4,0)$) [below] {\(K_{\RG}+1\)};
+
+            \coordinate (origin) at (9,0);
                 % Coordinate system
@@
                 \node at ($(origin) + (4,0)$) [below] {\(K_{\RG}+1\)};
-            };
         \end{tikzpicture}
@@
 
-In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}), this gives: \(U_{\NH}(K_{\NH}) = U_{\NH}(\bar \lambda_{\NH}(K_{\NH}) \leq U_{\NH}(\bar \lambda_{\NH}(K_{\NH}+1)) = U_{\NH}(K_{\NH}+1)\) giving:
+In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}),
+this gives: \(U_{\NH}(K_{\NH}) = U_{\NH}(\bar \lambda_{\NH}(K_{\NH})) \leq
+U_{\NH}(\bar \lambda_{\NH}(K_{\NH}+1)) = U_{\NH}(K_{\NH}+1)\) giving:
 
@@
         \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
-            \foreach \x in {0,9}
-            {\coordinate (origin) at (\x,0);
+            \coordinate (origin) at (0,0);
+                % Coordinate system
+                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\Large \(\bar\lambda_{K_{\NH}}\)};
+                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {\Large Occupancy at NH};
+                % lambda
+                \draw ($(origin) + (0,4)$) -- ($(origin) + (2,4)$) -- ($(origin) + (2,2)$) -- ($(origin) + (5,2)$);
+                \node at ($(origin) + (1,3.5)$) {\(\lambda_{\NH}^{(h,l)}\)};
+                \node at ($(origin) + (3.5,1.5)$) {\(\lambda_{\NH}^{(h,h)}\)};
+                % Effect of KNH
+                \draw [dashed] ($(origin) + (0,4)$) -- ($(origin) + (4,4)$) -- ($(origin) + (4,2)$);
+                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,4)$);
+                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,4)$);
+                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
+                \node at ($(origin) + (2,0)$) [below] {\(K_{\NH}\)};
+                \node at ($(origin) + (4,0)$) [below] {\(K_{\NH}+1\)};
+
+            \coordinate (origin) at (9,0);
                 % Coordinate system
@@
                 \node at ($(origin) + (4,0)$) [below] {\(K_{\NH}+1\)};
-            };
         \end{tikzpicture}
@@
 \small{$$\lambda_{\NH}^{(r)}=\begin{cases}
-\lambda_{\NH}, &\text{if }r=a\\
-\lambda_{\NH}+\lambda_{\RG},  &\text{if }r=b\\
-0, &\text{if }r\in\{c,d\}\\
+\lambda_{\NH}, &\text{if }r=(l,l)\\
+\lambda_{\NH}+\lambda_{\RG},  &\text{if }r=(l,h)\\
+0, &\text{if }r\in\{(h,l),(h,h)\}\\
 \end{cases}$$}
@@
 \small{$$\lambda_{\RG}^{(r)}=\begin{cases}
-\lambda_{\RG}, &\text{if }r=a\\
-\lambda_{\NH}+\lambda_{\RG},  &\text{if }r=c\\
-0, &\text{if }r\in\{b,d\}\\
+\lambda_{\RG}, &\text{if }r=(l,l)\\
+\lambda_{\NH}+\lambda_{\RG},  &\text{if }r=(h,l)\\
+0, &\text{if }r\in\{(l,h),(h,h)\}\\
 \end{cases}$$}
@@
 \small{$$\lambda_{NH}^{(r)}=\begin{cases}
-\lambda_{NH}, &\text{if }r\in\{a,d\}\\
-\lambda_{NH}+\lambda_{RG},  &\text{if }r=b\\
-0, &\text{if }r=c\\
+\lambda_{NH}, &\text{if }r\in\{(l,l),(h,h)\}\\
+\lambda_{NH}+\lambda_{RG},  &\text{if }r=(l,h)\\
+0, &\text{if }r=(h,l)\\
 \end{cases}$$}
@@
 \small{$$\lambda_{RG}^{(r)}=\begin{cases}
-\lambda_{RG}, &\text{if }r\in\{a,d\}\\
-\lambda_{NH}+\lambda_{RG},  &\text{if }r=c\\
-0, &\text{if }r=b\\
+\lambda_{RG}, &\text{if }r\in\{(l,l), (h,h)\}\\
+\lambda_{NH}+\lambda_{RG},  &\text{if }r=(h,l)\\
+0, &\text{if }r=(l,h)\\
 \end{cases}$$}

### 2016-07-04 Paper/paper.tex
Modifications to paper.

@@
 
+\usepackage{natbib}
+\bibliographystyle{agsm}
+
 % New commands------------------------
@@
 In \cite{kim2013icu, shmueli2003optimizing} this is expanded to consider a variety of admission policies in two CCUs, in particular the effect of rejection (due to too high occupancy) is measured.
-These policies are studied in the setting of a single hospital, and thus, from a game theoretic \cite{Maschler2013} point of view correspond to rational behaviour.
+These policies are studied in the setting of a single hospital, and thus, from a game theoretic point of view correspond to rational behaviour (a good game theory reference text is \cite{Maschler2013}).
 In practice a simplification of rational strategies is managed by policy makers by setting utilisation targets that ensure that hospitals do not run at a level likely to have a high rejection rate (example of these can be seen in \cite{Bevan2006, NHS2013}).
@@
 It provides intensive care (treatment and monitoring) for people who are critically ill or are in an unstable condition.
-CCUs face major challenges, on average, 8\% of patients are refused admission to a CCU because the Unit is full \cite{Report}.
+CCUs face major challenges, on average, 8\% of patients are refused admission to a CCU because the Unit is full (\cite{Report}).
 The CCU occupancy rates for some hospitals are reportedly very high
-\cite{Mitchell1995,Smith1995} and a shortage of beds has been identified
+(\cite{Mitchell1995,Smith1995}) and a shortage of beds has been identified
 throughout the United Kingdom.
 
-Many previous researchers have developed queueing models to help manage bed capacities in hospitals \cite{Cooper1974,Dumas1984,Gallivan2011,Gorunescu2002a,Griffiths2012,Harper2002a}.
+Many previous researchers have developed queueing models to help manage bed capacities in hospitals: \cite{Cooper1974,Dumas1984,Gallivan2011,Gorunescu2002a,Griffiths2012,Harper2002a}.
 Also, a vast amount of literature has been devoted to the simulation of CCUs;  \cite{Cahill1999a,Costa2003,Griffiths2004a,Kim1999,Litvak2008,Shahani2008}.
 
-This paper describes part of a project undertaken with managers from the Aneurin Bevan University Health Board (ABUHB), which is an NHS Wales organization in South Wales, that serves 21\% of the total population of Wales \cite{Board}.
+This paper describes part of a project undertaken with managers from the Aneurin Bevan University Health Board (ABUHB), which is an NHS Wales organization in South Wales, that serves 21\% of the total population of Wales (\cite{Boarda}).
 Critical care is delivered on two sites, at the Nevill Hall hospital in Abergavenny and at the Royal Gwent hospital in Newport.
@@
 After an initial analysis of the data, behavioural aspects became apparent; for example, delaying patients discharge if there was no pressure on CCU beds, or admitting fewer patients if bed occupancy levels were high.
-As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy \cite{williams2015mathematical}.
+As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy (\cite{williams2015mathematical}).
 This state dependent model was applied to both NH and RG separately.
@@
 The work presented in this paper contributes to the growing body of literature by applying state dependent queueing models in a game theoretical context to CCU interaction.
-In particular this consideration allows for the investigation of targets imposed by central control \cite{Bevan2006}.
+In particular this consideration allows for the investigation of targets imposed by central control (\cite{Bevan2006}).
 The findings of this work justify and identify a choice of targets that align the interests of the individual hospitals with social welfare.
@@
 \begin{center}
-    \begin{tikzpicture}[scale=.7, every node/.style={scale=0.7}]
+    \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
         % -----------------------------------------------
@@
 
-The stochastic transition rate matrix $Q=Q(c_{NH},c_{RG})$ of the continuous-time Markov chain \cite{Stewart2009} has entries $q_{ij}=q_{(u_i,v_i),(u_j,v_j)}$ which is the rate at which a transition from state $i$ to state $j$ occurs.
+The stochastic transition rate matrix $Q=Q(c_{NH},c_{RG})$ of the continuous-time Markov chain (\cite{Stewart2009}) has entries $q_{ij}=q_{(u_i,v_i),(u_j,v_j)}$ which is the rate at which a transition from state $i$ to state $j$ occurs.
 The transition rates are given by (\ref{transitions}) and are illustrated diagrammatically in Figure \ref{mc}.
@@
 Utilities will be of interest when this queueing theoretical model will be inserted in the game theoretical model.
-Throughput of patients is a natural choice of utility given that most hospitals are financially rewarded per served patient \cite{Pate2009}.
+Throughput of patients is a natural choice of utility given that most hospitals are financially rewarded per served patient (\cite{Pate2009}).
 For each threshold pair $(K_{\NH},K_{\RG})$, the utilisation rate $U_H$ and throughput $T_H$ can easily be obtained for each CCU: $H\in\{\text{NH},\text{RG}\}$, using the following formulas:
@@
 $$
-\caption{Steady state probabilities for $H\in\{\NH,\RG\}$ with $(K_{\NH}, K_{\RG})=(6,12)$} \label{steady_state_probs}
+\caption{Steady state probabilities for each hospital ($H\in\{\NH,\RG\}$) with different threshold pairs ($(K_{\NH}, K_{\RG})=(6,12)$)} \label{steady_state_probs}
 \end{figure}
@@
 $$
-\caption{Steady state probabilities for $H\in\{\NH,\RG\}$ with $(K_{\NH}, K_{\RG})=(1,12)$} \label{steady_state_probs_1_12}
+\caption{Steady state probabilities for each hospital ($H\in\{\NH,\RG\}$) with different threshold pairs ($(K_{\NH}, K_{\RG})=(1,12)$)} \label{steady_state_probs_1_12}
 \end{figure}
@@
 This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close as possible to a certain target.
-As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, which guarantee the existence of equilibria in mixed strategies.
+As such a Nash Equilibrium is not guaranteed by traditional game theoretical results (\cite{Nash1950}), which guarantee the existence of equilibria in mixed strategies.
 Based on discussions with ABUHB, long term threshold policies are a realistic consideration and so a pure strategy space is used.
@@
 Price of Anarchy (PoA) being a theoretical upper bound of the effect of
-uncoordinated behaviour \cite{TimRoughgarden}.
+uncoordinated behaviour (\cite{TimRoughgarden}).
 
@@
     \end{center}
-    \caption{Plots of $f_{\NH}(K_{\RG})$ (crosses) and $f_{\RG}(K_{\NH})$ (diamonds)}\label{exampleforproof}
+    \caption{Plots of best response functions: $f_{\NH}(K_{\RG})$ (crosses) and $f_{\RG}(K_{\NH})$ (diamonds)}\label{exampleforproof}
 \end{figure}
@@
                 \node at ($(origin) + (4,0)$) [below] {\(K_{\RG}+1\)};
-
-            \coordinate (origin) at (9,0);
-                % Coordinate system
-                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\Large \(\bar\lambda_{K_{\RG}}\)};
-                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {\Large Occupancy at RG};
-                % lambda
-                \draw ($(origin) + (0,2)$) -- ($(origin) + (2,2)$) -- ($(origin) + (2,4)$) -- ($(origin) + (5,4)$);
-                \node at ($(origin) + (1,2.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
-                \node at ($(origin) + (3.5,4.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
-                % Effect of KRG
-                \draw [dashed] ($(origin) + (0,2)$) -- ($(origin) + (4,2)$) -- ($(origin) + (4,4)$);
-                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,2)$);
-                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,2)$);
-                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
-                \node at ($(origin) + (2,0)$) [below] {\(K_{\RG}\)};
-                \node at ($(origin) + (4,0)$) [below] {\(K_{\RG}+1\)};
         \end{tikzpicture}
     \end{center}
-    \caption{The effect of \(K_{\RG}\) on \(\bar \lambda\).}\label{fig:effect_of_KRG_on_arrival_rate}
+    \caption{The effect of the threshold (\(K_{\RG}\)) on the effective arrival rate (\(\bar \lambda\)).
+The same behaviour is exhibited for \(\lambda_{\NH}^{(l,l)}\) and \(\lambda_{\NH}^{(l, h)}\).}\label{fig:effect_of_KRG_on_arrival_rate}
 \end{figure}
@@
                 \node at ($(origin) + (4,0)$) [below] {\(K_{\NH}+1\)};
-
-            \coordinate (origin) at (9,0);
-                % Coordinate system
-                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\Large \(\bar\lambda_{K_{\NH}}\)};
-                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {\Large Occupancy at NH};
-                % lambda
-                \draw ($(origin) + (0,4)$) -- ($(origin) + (2,4)$) -- ($(origin) + (2,2)$) -- ($(origin) + (5,2)$);
-                \node at ($(origin) + (1,3.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
-                \node at ($(origin) + (3.5,1.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
-                % Effect of KNH
-                \draw [dashed] ($(origin) + (0,4)$) -- ($(origin) + (4,4)$) -- ($(origin) + (4,2)$);
-                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,4)$);
-                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,4)$);
-                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
-                \node at ($(origin) + (2,0)$) [below] {\(K_{\NH}\)};
-                \node at ($(origin) + (4,0)$) [below] {\(K_{\NH}+1\)};
         \end{tikzpicture}
     \end{center}
-    \caption{The effect of \(K_{\NH}\) on \(\bar \lambda\).}\label{fig:effect_of_KNH_on_arrival_rate}
+    \caption{The effect of the threshold (\(K_{\NH}\)) on the effective arrival rate (\(\bar \lambda\)).
+The same behaviour is exhibited for \(\lambda_{\NH}^{(l,l)}\) and \(\lambda_{\NH}^{(l, h)}\).}\label{fig:effect_of_KNH_on_arrival_rate}
 \end{figure}
@@
     \end{center}
-    \caption{Values of \(U_{\NH}\) and the corresponding inequalities for varying cutoff thresholds.}\label{fig:variation_of_UNH}
+    \caption{Values of utilisation (\(U_{\NH}\)) and the corresponding inequalities for varying cutoff thresholds.}\label{fig:variation_of_UNH}
 \end{figure}
@@
 
-Recalling equations (\ref{equ:UNH_as_a_function_of_KRG}-\ref{equ:UNH_as_a_function_of_KNH}) and Figure \ref{fig:variation_of_UNH} have:
+Recalling equations
+(\ref{equ:UNH_as_a_function_of_KRG}-\ref{equ:UNH_as_a_function_of_KNH}) and
+Figure~\ref{fig:variation_of_UNH} gives:
 
@@
 
-The measure used to quantify inefficiency is the Price of Anarchy (PoA) \cite{Koutsoupias1999,TimRoughgarden}, which is the ratio of the social optimum welfare to the welfare of the worst Nash Equilibrium.
+The measure used to quantify inefficiency is the Price of Anarchy (PoA) (\cite{Koutsoupias1999,TimRoughgarden}), which is the ratio of the social optimum welfare to the welfare of the worst Nash Equilibrium.
 That is, the ratio of the largest social welfare, $T^*$ to the smallest social welfare, $\widetilde{T}$, achieved at any Nash Equilibrium. Thus:
@@
 
-The game theoretic model of (\ref{model1}) is solved using exhaustive consideration of best responses whilst taking advantage of the structure identified by the Lemma of Section \ref{queueingandgamemodels}.
-For any given pair of threshold strategies the matrix equation $\pi Q=0$ is solved by obtaining a basis for the Kernel of $Q$.
-For the purpose of this paper this is implemented in \cite{sage}.
+The game theoretic model of (\ref{model1}) is solved using exhaustive
+consideration of best responses whilst taking advantage of the structure
+identified by the Lemma of Section~\ref{queueingandgamemodels}. For any given
+pair of threshold strategies the matrix equation $\pi Q=0$ is solved by
+obtaining a basis for the kernel of $Q$. For the purpose of this paper this is
+implemented in Sagemath (\cite{sage}).
 
@@
 discharged) to another ward and/or using the post-anesthesia care unit
-as a temporary overflow measure. This models corresponds to the first of those
-possibilities: the patient is lost (from the point of view of this model).
+as a temporary overflow measure. This models corresponds to the first
+possibility: the patient is lost (from the point of view of this model).
 
@@
 For values of $t>0.5$ the PoA is still high: a PoA of 2 corresponds to 100\% less throughput of patients.
-These findings seem to give some backing to the targets implemented throughout the NHS \cite{Bevan2006}.
+These findings seem to give some backing to the targets implemented throughout the NHS (\cite{Bevan2006}).
 
@@
 This game theoretic model is underpinned by a queueing model that takes into account the stochastic nature of queueing systems.
-This work extends the application of game theoretic models already present in the literature to healthcare \cite{li2002cooperative, xie2006note}.
+This work extends the application of game theoretic models already present in the literature to healthcare (\cite{li2002cooperative, xie2006note}).
 
@@
     \item This model only assumes the presence of two players however in reality
-        the system has a variety of stakeholders. Multi player systems could be
+        the system has a variety of stakeholders. Multiplayer systems could be
         worth considering. This would reflect health boards/hospitals in a
@@
 The code used in this work can be found here: \url{https://gist.github.com/anonymous/81effc06eea70a9e4e2f}.
-The graphics for this paper were obtained using \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://cloud.sagemath.com/projects/c293aefd-1fdf-4b9c-95f4-75bb77035e42/files/MeasuringThePriceOfAnarchyInCCUInteractions.sagews}.
+The graphics for this paper were obtained using software described in \cite{Hunter:2007, sage} a worksheet with the data and code used for the plots can be found here: \url{https://cloud.sagemath.com/projects/c293aefd-1fdf-4b9c-95f4-75bb77035e42/files/MeasuringThePriceOfAnarchyInCCUInteractions.sagews}.
 
 \newpage
-\bibliographystyle{plain}
 \bibliography{library}

### 2016-07-04 Reviews/response-1.tex
Adding response.

\documentclass{article}

\usepackage{fullpage}
\usepackage{parskip}
\usepackage{booktabs}
\usepackage{minted}
\usepackage{amsmath}

\newcommand{\NH}{\text{NH}}
\newcommand{\RG}{\text{RG}}

\title{Responses to second review for Measuring the Price of Anarchy in Critical Care Unit Interactions}
\author{Vincent Knight*
    \and
        Izabela Komenda
    \and
        Jeff Griffiths}

\begin{document}

\maketitle

We are grateful for positive comments and address each in turn below.

\subsection{Reviewer 1}

\begin{quote}
    \begin{textit}{
            The current version of the paper is accepted for publication as all
            the quarries are justified properly in the revised paper. Thanks a
            lot.
    }\end{textit}
\end{quote}

No action taken. We are grateful to the reviewer for their time and expertise.

\subsection{Reviewer 2}

\begin{quote}
    \begin{textit}{
It becomes more confusing especially to note the relation between H and h. Why not define KH, h, H ,l etc in this table? This will be easy for the reader to refer to this table easily rather than having to move up and down to get some definitions. When I got to the end of the document, the discussions, I had already forgotten some definitions of some unknowns and I had to spent almost a minute looking for their definitions in the document. That is my point. I suggest that the authors define all the unknowns in a single table. It makes the paper more readable than its current form.
    }\end{textit}
\end{quote}

As highlighted in our previous response we do not feel that this is a request
that would improve the paper. The general parameters for the problem itself are
listed, the description of the solution approach then defines all relevant
parameters (this is not unusual).

\subsection{Reviewer 3}

\begin{quote}
    \begin{textit}{
1. p. 10, l. 2: "Recalling equations (4-5) and Figure 9 have:"
Not grammatical. "have" -> "gives" ?
    }\end{textit}
\end{quote}

This has been changed.

\begin{quote}
    \begin{textit}{
        2. p. 10, second last par.: "Note that intuitively..."
        Are the authors able to concisely provide some intuition as to why
        the naive result is not correct?
    }\end{textit}
\end{quote}

We expect that this is due to the hospitals running at full capacity which
implies more overall rejections (the queues are loss queues). We are however
hesitant to include that in the paper itself. We feel that to do so, a full
investigation should be carried out (which we feel is outside of the scope of
this paper).

\begin{quote}
    \begin{textit}{
        3. Just before 3.1: "Kernel"
        Why is kernel capitalized?
    }\end{textit}
\end{quote}

This has been changed.

\begin{quote}
    \begin{textit}{
        4. p. 11, sentence just before equation: This models corresponds to
        the first..."
        Not grammatically correct.
    }\end{textit}
\end{quote}

This has been modified to read:

``This models corresponds to the first
possibility: the patient is lost (from the point of view of this model).''

\begin{quote}
    \begin{textit}{
        5. p. 16, second bullet:
        Believe that "Multi player" is one word.
    }\end{textit}
\end{quote}

This has been fixed.

\subsection{Editor requests}

\begin{quote}
    \begin{textit}{
Referee \#2 finds the notation difficult to follow and suggests the addition of a list of parameters. I think the difficulty is perhaps exaggerated as I find the text that the Referee quotes from p3 relatively easy to follow. However, I would ask the authors to consider whether a list of parameters and key notation would be of benefit to the reader.
    }\end{textit}
\end{quote}

We have considered it and do not feel it would help very much. The problem
parameters are listed in the table, everything else is part of the problem
solution which we feel is clearly described.

\begin{quote}
    \begin{textit}{
        The journal uses a Harvard-style convention for references. Please can the authors modify the citation of references to reflect this.
    }\end{textit}
\end{quote}

This has been changed throughout.

\begin{quote}
    \begin{textit}{
        More informative Figure captions might help with the notation issue. For
        example, "Figure 7: The effect of \(K_{RG}\) on \(\overline{\lambda}\)" would be easier
        to understand if "\(K_{RG}\)" and "\(\overline{\lambda}\)" were explained in words.
    }\end{textit}
\end{quote}

The captions have been changed to be more descriptive.

\begin{quote}
    \begin{textit}{
        The size of text used in images is a potential issue. For example, I am not
        sure that the detailed annotations in Figure 3 will be legible when the figure
        is prepared for inclusion in the journal. Could the two graphs in Figure 7 be
        replaced by a single graph? The only difference between the two graphs seems to
        be a minor change in annotation. Similarly for Figure 8. The authors should try
        to provide images of the highest quality possible as separate files.
    }\end{textit}
\end{quote}

Figure 3 has been made slightly larger but does indeed have quite small print
but in electronic format can be zoomed in on to any level (see later comment
about vector format of images).

We have removed the second plot for Figures 7 and 8 and added an explanation in the caption saying that the same effect holds for the other values of \(\lambda\).

Image file formats are in vector format (converted from svg to pdf) which
ensures lossless quality, this will all be provided as separate files.

\end{document}

### 2016-07-05 Paper/paper.tex
Fixing grammatical sentence.
Y-axis italics.

@@
 that the domain of $f_{\NH}$ is the $x$-axis and the domain of $f_{\RG}$ is the
-y-axis) it is obvious to see that the functions must intersect at some point as
+$y$-axis) it is obvious to see that the functions must intersect at some point as
 shown in Figure \ref{exampleforproof}.
@@
 discharged) to another ward and/or using the post-anesthesia care unit
-as a temporary overflow measure. This models corresponds to the first
+as a temporary overflow measure. This model corresponds to the first
 possibility: the patient is lost (from the point of view of this model).
